### 2019-02-07 Model/simple_model/Paper.tex
Create Model file for ART model pre-capital

\documentclass[12pt, final]{article}
\usepackage{color}
\usepackage{times}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage[paperwidth=8.5in,left=1.0in,right=1.0in,top=1.0in,bottom=1.0in,paperheight=11.0in]{geometry}
\usepackage[labelsep=colon,singlelinecheck=false,footnotesize]{caption}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{booktabs}
\usepackage[sort&compress]{natbib}
\usepackage{subfig}
\usepackage{titlesec}
\usepackage[breaklinks]{hyperref}
\hypersetup{pdfdisplaydoctitle=true,bookmarksnumbered=true,colorlinks=true,citecolor=black,linkcolor=darkblue,urlcolor=darkred,pdfstartview=FitH,pdfpagemode=UseNone}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{accents}
\newcommand{\ubar}[1]{\underaccent{\bar}{#1}}

%Define Color Names
\definecolor{Gray}{rgb}{0.65,0.65,0.65}
\definecolor{darkblue}{rgb}{0,0,0.55}
\definecolor{darkred}{rgb}{0.5,0,0}

%Section Headings
\newcommand\Bheadfont{\fontsize{14pt}{\baselineskip}\selectfont}
\titleformat{\section}[hang]{\normalfont\sc\color{darkblue}\Bheadfont}{\thesection\hskip0.618em}{0em}{}
\titlespacing*{\section}{0pt}{15pt plus 2pt minus 2pt}{9pt plus 2pt minus 2pt}
\titleformat{\subsection}[runin]{\normalfont\sc\color{darkblue}} {\thesubsection\hskip0.618em}{0em}{}
\titlespacing*{\subsection}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
\titleformat{\subsubsection}[runin]{\normalfont\sc\color{darkblue}} {\thesubsubsection\hskip0.618em}{0em}{}
\titlespacing*{\subsubsection}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
\titleformat{\paragraph}[runin]{\bfseries}{\theparagraph\hskip0.618em}{0em}{}
\titlespacing*{\paragraph}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}

\begin{document}

\section{Model} A representative household chooses $\{c_t, n_t, b_t\}_{t=0}^\infty$ to maximize expected lifetime utility, $E_0\textstyle\sum_{t=0}^\infty\beta^t [\log(c_t)-\chi n_t^{1+\eta}/(1+\eta)]$, where $\beta$ is the subjective discount factor, $\chi$ determines the steady state labor supply, $1/\eta$ is the Frisch elasticity of labor supply, $c$ is consumption, $h$ is the degree of external habit persistence, $n$ is labor hours, $b$ is the real value of a privately-issued 1-period nominal bond, and $E_0$ is the mathematical expectation operator conditional on information available in period 0. The household's choices are constrained by $c_t+b_t/(i_ts_t)=w_tn_t+b_{t-1}/\pi_t+d_t$, where $\pi$ is the gross inflation rate, $w$ is the real wage rate, $i$ is the gross nominal interest rate, $d$ is a real dividend from ownership of intermediate firms, and $s$ is a risk premium shock that follows
\begin{gather}
  s_t=(1-\rho_s)\bar{s}+\rho_s s_{t-1} + \sigma_\upsilon\upsilon_t, 0\leq \rho_s < 1, \upsilon \sim \mathbb{N}(0,1).
\end{gather}
An increase in $s_t$ lowers the marginal cost of saving in the risk-free bond (JDM Fisher).  \\
The first order conditions to the household's constrained optimization problems are given by
\begin{gather*}
  \lambda_t = c_t\\
  w_t = \chi n_t^\eta \lambda_t\\
  1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]
  \end{gather*}
where $1/\lambda$ is the marginal utility of wealth (i.e., the Lagrange multiplier on the budget constraint).\\
The production sector consists of a continuum of monopolistically competitive intermediate goods firms and a final goods firm. Intermediate firm $i \in [0,1]$ produces a differentiated good, $y_t^f(i)$, according to $y_t^f = z_tn_t(i)$, where $n(i)$ is the labor hired by firm $i$ and $z_t = g_tz_{t-1}$ is technology, which is common across firms. Deviations from the balanced growth rate, $\bar{g}$, follow
\begin{gather}
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t, \varepsilon \sim \mathbb{N}(0,1).
\end{gather}
An increase in $g_t$ acts just like a typical supply shock, lowering inflation and raising output growth.\\
The final goods firm purchases $y_t^f(i)$ units from each intermediate firm to produce the final good, $y_t^f \equiv [\int_0^1 y_t^f(i)^{\epsilon - 1}di]^{\epsilon/(\epsilon - 1)}$, where $\epsilon > 1$ is the elasticity of substitution. It then maximizes dividends to determine its demand function for intermediate good $i$, $y_t^f(i) = (p_t(i)/p_t)^{-\epsilon}y_t^f$, where $p_t = [\int_0^1p_t(i)^{1-\epsilon}di]^{1/(1-\epsilon)}$ is the price level. Following Rotemberg (1982), each intermediate firm pays a price adjustment cost $adj_t(i) \equiv \varphi(p_t(i)/(\bar{\pi}p_{t-1}(i))-1)^2y_t^f/2$, where $\varphi>0$ scales the cost and $\bar{pi}$ is the gross inflation rate along the balanced growth path. Given the adjustment cost, firm $i$ chooses $n_t(i)$ and $p_t(i)$ to maximize the expected discounted present value of future dividends, $E_t\sum_{k=t}^\infty q_{t,k}d_k(i)$, subject to its production function and the demand for its product, where $q_{t,t} \equiv 1$, $q_{t,t+1} \equiv \beta(\lambda_t/\lambda_{t+1})$ is the pricing kernel between periods $t$ and $t+1$, $q_{t,k} \equiv \Pi_{j=t+1}^{k>t} q_{j-1,j}$, and $d_t(i) = p_t(i)y_t^f(i)/p_t - w_tn_t(i) - adj_t(i)$. In symmetric equilibrium, all firms make identical decisions (i.e., $p_t(i) = p_t$, $n_t(i) = n_t$, and $y_t^f(i) = y_t^f$). Therefore, the optimality conditions imply
    \begin{gather}
      y_t^f = z_tn_t\\
      \varphi(\pi_t/\bar{\pi}-1)(\pi_t/\bar{\pi}) = 1 - \epsilon + \epsilon w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}/\bar{\pi} - 1)(\pi_{t+1}/\bar{\pi}-1)(\pi_{t+1}/\bar{\pi})(y^f_{t+1}/y_t^f)].
      \end{gather}
    Without price adjustment costs (i.e., $\varphi = 0$), the real marginal cost of producing a unit of output ($w_t/z_t$) equals $(\epsilon-1)/\epsilon$, which is the inverse of a firm's markup of price over marginal cost ($\mu$). \\
    The central bank sets the gross nominal interest rate, $i$, according to
    \begin{gather}
      i_t = \max\{1, i_t^n\},\\
      i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t), 0 \leq \rho_i < 1, \varepsilon_i \sim \mathbb{N}(0,1),
    \end{gather}
    where $y$ is output (i.e., final goods, $y^f$, minus the resources lost due to price adjustment costs, $adj$), $i^n$ is the gross notional interest rate, $\bar{i}$ and $\bar{\pi}$ are the steady-state or target values of the inflation and nominal interest rates, and $\phi_\pi$ and $\phi_y$ determine the central bank's responses to deviations of inflation from the target rate and deviations of output growth from the balanced growth rate. When the net notional rate is positive, $i_t = i^n_t$. When it is negative, the ZLB binds and $i_t = 1$. A more negative net notional rate means the central bank is more constrained and hte model is more nonlinear. \\
    The model does not possess a steady-state due to the unit root in technology, $z_t$. Therefore, we redefine the subset of variables with a trend in terms of technology (i.e., $\tilde{x}_t \equiv x_t/z_t$). The detrended equilibrium system includes the two stochastic processes, (1) and (2), the ZLB constraint, (5), and
      \begin{gather}
c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
\lambda_t = c_t \\
w_t = \chi n_t^\eta \lambda_t\\
1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]
      \end{gather}

A competitive equilibrium consists of infinite sequences of quantities, $\{\tilde{c}_t, \tilde{y}_t, \tilde{y}_t^f, y_t^g\}_{t=0}^\infty$, prices $\{\tilde{w}_t, i_t, i^n_t, \pi_t, \tilde{\lambda}_t\}_{t=0}^\infty$, and exogenous variables $\{s_t, g_t\}_{t=0}^\infty$, that satisfy the detrended equilibrium system, given the initial conditions, $\{\tilde{c}_{-1}, i^n_{-1}, s_0, g_0, \varepsilon_{i,0}\}$, and shock sequences, $\{\varepsilon_{g,t}, \varepsilon_{s,t}, \varepsilon_{i,t}\}_{t=1,\infty}$.

\end{document}

### 2019-02-15 src/general/Unused/expvar.m
Add ART-capital as general

@@ -1,88 +1,0 @@
-function [Einvpi,Ec,Er,Erk] = expvar(k,z,beta,i,...
-                                     Palpha,Ppi,Peta,Pvarphi,Pphipi,Pphiy,...  
-                                     Pdelta,Pnu,Pzbar,Prhoz,Pbeta,Prhobeta,...
-                                     Schi,Sr,Sy,...       
-                                     Ge_weight,Ge_nodes,Gu_weight,Gu_nodes,...
-                                     Gk_grid,Gz_grid,Gbeta_grid,...
-                                     pf_n,pf_pi,pf_i)
-
-% Replicate state across the shocks                                 
-nsims = numel(k);
-kArr = k(:,ones(length(Ge_nodes),1),ones(length(Gu_nodes),1));
-zArr = z(:,ones(length(Ge_nodes),1),ones(length(Gu_nodes),1));
-betaArr = beta(:,ones(length(Ge_nodes),1),ones(length(Gu_nodes),1));
-iArr = i(:,ones(length(Ge_nodes),1),ones(length(Gu_nodes),1));
-eNodesArr = permute(Ge_nodes(:,ones(nsims,1),ones(length(Gu_nodes),1)),[2 1 3]);
-uNodesArr = permute(Gu_nodes(:,ones(nsims,1),ones(length(Ge_nodes),1)),[2 3 1]);
-npArr = 0*zArr;
-pipArr = 0*zArr;
-ipArr = 0*zArr;
-%----------------------------------------------------------------------
-% Solve for variables
-%----------------------------------------------------------------------
-% Investment
-kpArr = iArr + (1-Pdelta)*kArr;   
-% Technology
-zpArr = Pzbar*(zArr/Pzbar).^Prhoz.*exp(eNodesArr);
-% Discount factor
-betapArr = Pbeta*(betaArr/Pbeta).^Prhobeta.*exp(uNodesArr); 
-%----------------------------------------------------------------------
-% Linear interpolation of the policy variables 
-%---------------------------------------------------------------------- 
-[npArr(:),pipArr(:),ipArr(:)] = Fallterp33c_F(Gk_grid,Gz_grid,Gbeta_grid,...
[…]

### 2019-02-15 src/general/Unused/plot_IRF.m

@@ -1,180 +1,0 @@
-% IRF comparison of normal and ZLB times
-clear all
-close all
-clc
-
-% Saving 'on' or 'off'
-saving = 'off';
-
-%% ------------------------------------------------------------------------
-% Calculate stochastic steady state
-%--------------------------------------------------------------------------
-% Set random number seed
-mtstream = RandStream('mt19937ar','seed',0);
-RandStream.setGlobalStream(mtstream);
-
-nburn = 10000;
-% Set shocks to zero
-e = zeros(nburn,1);
-u = zeros(nburn,1);
-% Load baseline solution
-if exist('Rules\results.mat','file')
-    load('Rules\results.mat');
-    load([baselinename '.mat']);
-else
-    disp('Please run script_TL_onetime.m first to get baseline solution.')
-    break
-end
-V = variables;
-
-% Production function
-y = G.z_gr.*G.k_gr.^P.alpha.*pf.n.^(1-P.alpha); 
-% Interest rate rule
-r = max(1,S.r*(pf.pi/P.pi).^P.phipi.*(y./S.y).^P.phiy);
-% Fix beta cross-section
-betaCS = find(r(O.k_pts,ceil(O.z_pts/2),:)==1,1,'first');
-beta_zlb = G.beta_grid(betaCS);
-
-% Find stochastic steady state
-paths = simnonlin(pf,O,P,S,G,V,nburn,e,u,1);
-ss = paths(nburn,:);
-
-%% ------------------------------------------------------------------------
-% Impulse Responses
-%--------------------------------------------------------------------------
-% Number of periods
-npers = 21;
-
-% Shocks
-e = zeros(npers,1);
-e(2) = 0.01;
-unorm = zeros(npers,1);
-uZLB = zeros(npers,1);
-u_fixbeta = log((beta_zlb/P.beta)^(1-P.rhobeta));
-uZLB(:) = u_fixbeta;
-
-path = zeros(npers,V.nplotvar,2);
-% Fixed beta shock ss
-path_zlb = simnonlin(pf,O,P,S,G,V,nburn,zeros(nburn,1),u_fixbeta*ones(nburn,1),1,ss);
-ss_zlb = path_zlb(end,:);
-%   Normal Times
[…]

### 2019-02-15 src/general/Unused/plot_pfs3d.m

@@ -1,222 +1,0 @@
-clear all
-close all
-clc
-plotops
-set(0,'DefaultLineColor','black')
-set(0,'DefaultLineLineWidth',2)
-
-% Saving 'on' or 'off'
-saving = 'off';
-
-% Plot type
-%   M: Manuscript
-%   P: Presentation
-plottype = 'M';
-
-%% ------------------------------------------------------------------------
-% Load/calulate decision rules
-%--------------------------------------------------------------------------
-% Load decision rules
-load('Rules\pf_baseline_phiy25_phipi150.mat');
-V = variables;
-
-%   Production function
-y = G.z_gr.*G.k_gr.^P.alpha.*pf.n.^(1-P.alpha); 
-%   Interest rate rule
-r = max(1,S.r*(pf.pi/P.pi).^P.phipi.*(y/S.y).^P.phiy);
-disp(['ZLB bind (% nodes)' num2str(100*sum(r(:)==1)/G.nodes)]) 
-% Tobin's q
-q = 1+P.nu*(pf.i./G.k_gr-P.delta);  
-% Adjusted output
-ytil = y.*(1-(P.varphi*(pf.pi/P.pi-1).^2)/2);
-% Capital adjustment costs
-kac = P.nu*(pf.i./G.k_gr-P.delta).^2/2;
-% Aggregate resource constraint
-c = ytil - pf.i - kac.*G.k_gr;   
-% FOC Labor
-w = S.chi*pf.n.^P.eta.*c.^P.sigma;
-% Firm FOC labor
-psi = w.*pf.n./((1-P.alpha)*y);
-% Firm FOC capital
-rk = (1-P.alpha)*psi.*y./G.k_gr;
-% Expected future variables
-realr = 0*r;
-Ec = 0*r;
-Er = 0*r;
-Erk = 0*r;
-for i = 1:numel(realr)
-    [Einvpi,Ec(i),Er(i),Erk(i)] = expvar(...
-        G.k_gr(i),G.z_gr(i),G.beta_gr(i),pf.i(i),...
-        P.alpha,P.pi,P.eta,P.varphi,P.phipi,P.phiy,...  
-        P.delta,P.nu,P.zbar,P.rhoz,P.beta,P.rhobeta,...
-        S.chi,S.r,S.y,...       
-        G.e_weight,G.e_nodes,G.u_weight,G.u_nodes,...
[…]

### 2019-02-15 src/general/figures/figure_Eduration.m

@@ -1,0 +1,258 @@
+%  Creates a figure of the Expectated duration, actual and estimated
+%  scatter pot
+
+clear
+clc
+close all
+
+savename = 'Eduration';
+
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
+    '../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load actual expected duration from DGP
+Eduration = textread('../../data-artificial/Ezlb_duration/Eduration.txt','%f');
+Eduration = reshape(Eduration,[npers,nsimsall,nZLBpers]);
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+
+Eduration_est = nan(npers,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    %Load state estimate for given specification
+    filename = [specs{ifolder,1},'/states/Eduration.txt'];
+    if exist(filename, 'file') == 2
+        Eduration_temp = textread(filename,'%f');
+        Eduration_temp = reshape(Eduration_temp,[npers,nsims,nZLBpers]);
+        %Global data may be missing, replace zeros with nan
+        %if strcmp(specs{ifolder,2},'global')
+        %   Eduration_temp(Eduration_temp==0) = NaN;
+        %end
+        %Error in global and linear expectation calculation means Eduration
+        %needs to be reduced by 1
+        %if (strcmp(specs{ifolder,2},'global') || strcmp(specs{ifolder,2},'linear'))
+        %    Eduration_temp = Eduration_temp - 1;
[…]

### 2019-02-15 src/general/figures/figure_Eduration_zlb6.m

@@ -1,0 +1,238 @@
+%  Creates a figure of the Expectated duration, actual and estimated
+%  scatter pot
+
+clear
+clc
+close all
+
+savename = 'Eduration_zlb6';
+
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
+    '../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load actual expected duration from DGP
+Eduration = textread('../../data-artificial/Ezlb_duration/Eduration.txt','%f');
+Eduration = reshape(Eduration,[npers,nsimsall,nZLBpers]);
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+
+Eduration_est = nan(npers,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    %Load state estimate for given specification
+    filename = [specs{ifolder,1},'/states/Eduration.txt'];
+    if exist(filename, 'file') == 2
+        Eduration_temp = textread(filename,'%f');
+        Eduration_temp = reshape(Eduration_temp,[npers,nsims,nZLBpers]);
+        %Global data may be missing, replace zeros with nan
+        %if strcmp(specs{ifolder,2},'global')
+        %   Eduration_temp(Eduration_temp==0) = NaN;
+        %end
+        %Error in global and linear expectation calculation means Eduration
+        %needs to be reduced by 1
+        %if (strcmp(specs{ifolder,2},'global') || strcmp(specs{ifolder,2},'linear'))
+        %    Eduration_temp = Eduration_temp - 1;
[…]

### 2019-02-15 src/general/figures/figure_Pzlb6.m

@@ -1,0 +1,232 @@
+%  Creates a figure of the Expectated duration, actual and estimated
+%  scatter pot
+
+clear
+clc
+close all
+
+savename = 'Pzlb6';
+
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';,...  
+    '../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';,...  
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load actual expected duration from DGP
+Pzlb = textread('../../data-artificial/Ezlb_duration/Pzlb.txt','%f');
+Pzlb = reshape(Pzlb,[npers,nsimsall,nZLBpers]);
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
+states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
[…]

### 2019-02-15 src/general/figures/figure_credset_accuracy.m

@@ -1,0 +1,185 @@
+%  Creates a figure of the percent of actuals outside of forecast credible sets
+% from the different model %  specifications from the periods just prior to the ZLB binding.
+
+clear
+clc
+close all
+savename = 'credset_accuracy'; 
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
+    '../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
+    '../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
+    '../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-linear/me0/states/','linear','kf','me0','Lin-KF-$0\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore;
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
[…]

### 2019-02-15 src/general/figures/figure_crps_example.m

@@ -1,0 +1,108 @@
+%  Creates a figure of the percent of actuals outside of forecast credible sets
+% from the different model %  specifications from the periods just prior to the ZLB binding.
+
+clear
+clc
+close all
+plotops
+
+savename = 'crps_example'; 
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore;
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
+%Load forecast distribution
+forecast_dist = textread('../../Estimation-global/me5/states/forecast_dist.txt','%f');
+forecast_dist = 100*(forecast_dist.^4-1);
+actual = 100*(sims(89+8,V.i,2,2)^4-1);
+disp(['mean forecast =    ',num2str(mean(forecast_dist))])
+disp(['true realization = ',num2str(actual)])
+pts = 0:0.01:8;
+%%
+%   Subplot padding
+plotposition = [1 1 6.5 2.75];
+pad.topmarg = .12; % Increase if subplot title is cut off
+pad.leftmarg = .05; % Increase if ylabel is cut off
+pad.vspace = 0.04;
+pad.hspace = .08;
+pad.rightmarg = .025; % Decrease if white-space on RHS
+pad.botmarg = .15; % Increase if xaxis lables are cut off
[…]

### 2019-02-15 src/general/figures/figure_forecast_accuracy.m

@@ -1,0 +1,169 @@
+%  Creates a figure of the RMSE forecasts from the different model
+%  specifications from the periods just prior to the ZLB binding.
+
+clear
+clc
+close all
+savename = 'forecast_accuracy'; 
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
+    '../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
+    '../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
+    '../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-linear/me0/states/','linear','kf','me0','Lin-KF-$0\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore;
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
+%Load in forecasts from the specifications
[…]

### 2019-02-15 src/general/figures/figure_forecast_accuracy2.m

@@ -1,0 +1,168 @@
+%  Creates a figure of the RMSE forecasts from the different model
+%  specifications from the periods just prior to the ZLB binding.
+
+clear
+clc
+close all
+savename = 'forecast_accuracy'; 
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
+    '../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
+    '../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
+    '../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    %'../../Estimation-linear/me0/','linear','kf','me0','Lin-KF-$0\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore;
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
+%Load in forecasts from the specifications
+temp = textread([specs{1,1},'forecast.txt'],'%f');
[…]

### 2019-02-15 src/general/figures/figure_forecast_accuracy_test.m

@@ -1,0 +1,128 @@
+%  Creates a figure of the RMSE forecasts from the different model
+%  specifications from the periods just prior to the ZLB binding.
+
+clear
+clc
+close all
+savename = 'forecast_accuracy'; 
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
+    '../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
+    '../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
+    '../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    %'../../Estimation-linear/me0/','linear','kf','me0','Lin-KF-$0\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+temp = textread([specs{1,1},'forecast.txt'],'%f');
+% forecast_dgp = reshape(temp,[npers,3,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore;
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+forecast = nan(npers,3,Vnstate,nsims,nZLBpers,nspecs);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
[…]

### 2019-02-15 src/general/figures/figure_girf.m

@@ -1,0 +1,151 @@
+% Simulation comparison of normal and ZLB times
+clear
+clc
+close all
+
+% Number of periods and simulations
+nplot = 21;         % i.e., 5 years
+ninitstate = 2;     % Initial state vectors
+
+% Load V from capital model
+load('../options.mat','V','S')
+V.nstate = V.nvar - V.nfore;
+Vcap = V;
+Scap = S;
+
+% Load structures for no capital model
+load('../../Results-nocap/options.mat','V','P','S')
+V.nstate = V.nvar - V.nfore;
+
+%--------------------------------------------------------------------------
+% True GIRF paths
+%--------------------------------------------------------------------------
+initstate = textread('../../data-artificial/girf_initstate_nlpf.txt','%f');
+initstate_nlpf = reshape(initstate,[Vcap.nstate,2]);
+initstate = textread('../../data-artificial/girf_initstate_pwlin.txt','%f');
+initstate_pwif = reshape(initstate,[Vcap.nstate,2]);
+meanpaths_true = textread('../../data-artificial/girf_meanpaths.txt','%f');
+meanpaths_true = reshape(meanpaths_true,[nplot,Vcap.nstate,2,ninitstate,V.nshock]);
+
+%--------------------------------------------------------------------------
+% NL-PF-5% GIRF paths
+%--------------------------------------------------------------------------
+nsimstemp = 100;
+nsims = 50;
+% nsims = 10;
+nZLBpers = 6;
+meanpathstemp = textread('../../Estimation-global/me5/girf_meanpaths.txt','%f');
+meanpathstemp = reshape(meanpathstemp,[nplot,V.nstate,2,ninitstate,V.nshock,nsimstemp,nZLBpers]);
+meanpathstemp(:,:,:,:,:,nsims+1:end,:) = [];
+meanpaths{1} = reshape(meanpathstemp,[nplot,V.nstate,2,ninitstate,V.nshock,nsims*nZLBpers]);
+% meanpaths{1} = reshape(meanpathstemp(:,:,:,:,:,:,[1,2]),[nplot,V.nstate,2,ninitstate,V.nshock,nsims*2]);
+
+%--------------------------------------------------------------------------
+% PW-IF-0% GIRF paths
[…]

### 2019-02-15 src/general/figures/figure_in_accuracy.m

@@ -1,0 +1,247 @@
+%  Creates a figure of the RMSE of RMSE of filtered state estimates across
+%  ZLB bins and specification. Bottom of the code plots various simulations
+
+clear
+clc
+close all
+
+savename = 'in_accuracy';
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
+    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
+states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    %Load state estimate for given specification
+    filename = [specs{ifolder,1},'/states/states.txt'];
+    if exist(filename, 'file') == 2
[…]

### 2019-02-15 src/general/figures/figure_state_accuracy.m

@@ -1,0 +1,194 @@
+%  Creates a figure of the RMSE of RMSE of filtered state estimates across
+%  ZLB bins and specification. Bottom of the code plots various simulations
+
+clear
+clc
+close all
+
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
+    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore;
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
+states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    %Load state estimate for given specification
+    filename = [specs{ifolder,1},'/states/states.txt'];
+    if exist(filename, 'file') == 2
[…]

### 2019-02-15 src/general/figures/global-pwlinear-params/figure_Pzlb.m

@@ -1,0 +1,231 @@
+%  Creates a figure of the Expectated duration, actual and estimated
+%  scatter pot
+
+clear
+clc
+close all
+
+savename = 'Pzlb';
+
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';,...  
+    '../../../global-pwlinear-params/me5/','global','pf','me5','NL-PF using PW-IF estimated parameters';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load actual expected duration from DGP
+Pzlb = textread('../../../data-artificial/Ezlb_duration/Pzlb.txt','%f');
+Pzlb = reshape(Pzlb,[npers,nsimsall,nZLBpers]);
+
+% Load parameter names
+load('../../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
+states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
[…]

### 2019-02-15 src/general/figures/global-pwlinear-params/figure_forecast_accuracy.m

@@ -1,0 +1,170 @@
+%  Creates a figure of the RMSE forecasts from the different model
+%  specifications from the periods just prior to the ZLB binding.
+
+clear
+clc
+close all
+savename = 'forecast_accuracy'; 
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
+    '../../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
+    '../../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
+    '../../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../../Estimation-linear/me0/states/','linear','kf','me0','Lin-KF-$0\%$';...
+    '../../../global-pwlinear-params/me5/states/','global','pf','me5','NL-PF using PW-IF estimated parameters';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore;
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
[…]

### 2019-02-15 src/general/figures/nomiss/figure_simulation_comp.m

@@ -1,0 +1,118 @@
+% Simulation comparison of normal and ZLB times
+clear
+clc
+close all
+
+% Saving 'on' or 'off'
+saving = 'on';
+
+% Simulation ZLB duration: 1SDx4, 1SDx7, 1p5SDx4
+dur = '1p5SDx4';
+
+% Load structures for no capital model
+load('../../../Results-nocap/options.mat','V','P','F')
+V.nstate = V.nvar - V.nfore;
+
+%--------------------------------------------------------------------------
+% True simulation
+%--------------------------------------------------------------------------
+T = 21;
+simstemp = textread(['../../../data-artificial-nocap/simulation_',dur,'.txt'],'%f');
+sims{1} = reshape(simstemp,[T,V.nstate]);
+
+%--------------------------------------------------------------------------
+% NL-PF-5% simulations
+%--------------------------------------------------------------------------
+nsims = 100;
+nZLBpers = 6;
+simstemp = textread(['../../../Estimation-global-nomiss/me5/simulation_',dur,'.txt'],'%f');
+simstemp = reshape(simstemp,[T,V.nstate,nsims,nZLBpers]);
+simstemp(:,:,51:end,:) = [];
+simstemp = reshape(simstemp,[T,V.nstate,(nsims/2)*nZLBpers]);
+sims{2}(:,:,1) = mean(simstemp,3);
+sims{2}(:,:,2:3) = quantile(simstemp,[.05,.95],3);
+
+%--------------------------------------------------------------------------
+% PW-IF-0% simulations
+%--------------------------------------------------------------------------
+simstemp = textread(['../../../Estimation-pwlinear-nomiss/simulation_',dur,'.txt'],'%f');
+simstemp = reshape(simstemp,[T,V.nstate,nsims,nZLBpers]);
+simstemp(:,:,51:end,:) = [];
+simstemp = reshape(simstemp,[T,V.nstate,(nsims/2)*nZLBpers]);
+sims{3}(:,:,1) = mean(simstemp,3);
+sims{3}(:,:,2:3) = quantile(simstemp,[.05,.95],3);
+
+%% ------------------------------------------------------------------------
+% Plot the results
[…]

### 2019-02-15 src/general/figures/pf-me2-me10/figure_Eduration.m

@@ -1,0 +1,240 @@
+%  Creates a figure of the Expectated duration, actual and estimated
+%  scatter pot
+
+clear
+clc
+close all
+
+savename = 'Eduration';
+
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    '../../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  
+    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
+    '../../../Estimation-global/me10/','global','pf','me10','Global, Particle Filter, ME 10$\%$';  
+    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load actual expected duration from DGP
+Eduration = textread('../../../data-artificial/Ezlb_duration/Eduration.txt','%f');
+Eduration = reshape(Eduration,[npers,nsimsall,nZLBpers]);
+
+%Load in V from misspecified model
+load('../../../Results-nocap/options.mat','V','P','F')
+
+Eduration_est = nan(npers,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    %Load state estimate for given specification
+    filename = [specs{ifolder,1},'/states/Eduration.txt'];
+    if exist(filename, 'file') == 2
+        Eduration_temp = textread(filename,'%f');
+        Eduration_temp = reshape(Eduration_temp,[npers,nsims,nZLBpers]);
+        %Global data may be missing, replace zeros with nan
+        %if strcmp(specs{ifolder,2},'global')
+        %   Eduration_temp(Eduration_temp==0) = NaN;
+        %end
[…]

### 2019-02-15 src/general/figures/pf-me2-me10/figure_Pzlb.m

@@ -1,0 +1,187 @@
+%  Creates a figure of the Expectated duration, actual and estimated
+%  scatter pot
+
+clear
+clc
+close all
+
+savename = 'Pzlb';
+
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    '../../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';,...  
+    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';,...  
+    '../../../Estimation-global/me10/','global','pf','me10','Global, Particle Filter, ME 10$\%$';,...  
+    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load actual expected duration from DGP
+Pzlb = textread('../../../data-artificial/Ezlb_duration/Pzlb.txt','%f');
+Pzlb = reshape(Pzlb,[npers,nsimsall,nZLBpers]);
+
+% Load parameter names
+load('../../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
[…]

### 2019-02-15 src/general/figures/pwlinear-stickyw/figure_crps.m

@@ -1,0 +1,183 @@
+%  Creates a figure of the percent of actuals outside of forecast credible sets
+% from the different model %  specifications from the periods just prior to the ZLB binding.
+
+clear
+clc
+close all
+savename = 'crps'; 
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
+    '../../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
+    '../../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
+    '../../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../../Estimation-linear/me0/states/','linear','kf','me0','Lin-KF-$0\%$';...
+    '../../../Estimation-pwlinear-stickyw/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$, Sticky Wages';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore;
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
[…]

### 2019-02-15 src/general/figures/pwlinear-stickyw/figure_in_accuracy_bar.m

@@ -1,0 +1,222 @@
+%  Creates a figure of the RMSE of RMSE of filtered state estimates across
+%  ZLB bins and specification. Bottom of the code plots various simulations
+
+clear
+clc
+close all
+savename = 'in_accuracy_bar'; 
+%Specifications to include: path, method, filter, measurement error,%label
+specs = {...
+    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
+    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
+    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../../Estimation-pwlinear-stickyw/','pwlinear-stickyw','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$, Sticky Wages';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names
+load('../../options.mat','V','P','F')
+
+% Load actual data
+simscap = textread('../../../data-artificial/sims.txt','%f');
+simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+sims = nan(npers,Vnstate,nsims,nZLBpers);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
+    else
+        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
+    end
+end
+
+states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
[…]

### 2019-02-15 src/general/linmodel.m

@@ -1,6 +1,6 @@
-function [T, M, eu] = linmodel(P,S,V)
+function [T,M,eu] = linmodel(P,S,V)
 
-% [T, M, eu] = linmodel(P,S,V)
+% [T,M,eu] = linmodel(P,S,V)
 %   Solves the log-linear model with GENSYS
 % Inputs:
 %     P     :   Structure of parameters
@@ -21,102 +21,216 @@ Pi = zeros(V.nvar,V.nfore);
 CC = zeros(V.nvar,1);
 j = 0;
 %---------------------------------------------
-j=j+1;%	[FOC Labor]
+j = j+1;% [FOC Utilization]
 %---------------------------------------------
-G0(j,V.w) = 1;
-G0(j,V.c) = -P.sigma;
-G0(j,V.n) = -P.eta;
-%---------------------------------------------
-j = j+1;% [Consumption Euler Equation]
-%---------------------------------------------
-G0(j,V.c) = P.sigma;
-G0(j,V.rk) = -(1-P.beta*(1-P.delta));
-G0(j,V.beta) = -1;
-G0(j,V.q) = -P.beta*(1-P.delta);
-G0(j,V.i) = -P.beta*P.nu*P.delta^2;
-G1(j,V.q) = -1;
-G1(j,V.c) = P.sigma;
-G1(j,V.k) = -P.beta*P.nu*P.delta^2;
-Pi(j,V.fec) = P.sigma;
-Pi(j,V.ferk) = -(1-P.beta*(1-P.delta));
-Pi(j,V.febeta) = -1;
-Pi(j,V.feq) = -P.beta*(1-P.delta);
-Pi(j,V.fei) = -P.beta*P.nu*P.delta^2;
-%---------------------------------------------
-j = j+1;% [FOC Bond]
-%---------------------------------------------
-G0(j,V.c) = P.sigma;
-G0(j,V.pi) = 1;
-G0(j,V.beta) = -1;
-G1(j,V.r) = 1;
-G1(j,V.c) = P.sigma;
-Pi(j,V.fec) = P.sigma;
-Pi(j,V.fepi) = 1;
-Pi(j,V.febeta) = -1;
-%---------------------------------------------
-j = j+1;% [ARC]
-%---------------------------------------------
-G0(j,V.c) = S.c;
-G0(j,V.y) = -S.y;
-G0(j,V.i) = S.i;
+G0(j,V.rk) = 1;
+G0(j,V.ups) = -S.rk*P.sigups;
[…]

### 2019-02-15 src/general/postdraws_conditional.m

@@ -1,0 +1,89 @@
+function [draws_all,nzlb,NRMSE,MDD,reject0595,postvar,MSE,bias2,isimdone] = ...
+    postdraws_conditional(V,P,F,nsims,folder,sims,isimdone,inq)
+    % Calculates accuracy statistics for a single dataset
+    % Inputs:
+    %   V:        Structure of variable indexes
+    %   P:        Structure of model parameters
+    %   F:        Structure of estimation information (e.g., priors)
+    %   nsims:    Number of datasets, integer
+    %   folder:   File location of posterior estimate files, string
+    %   sims:     Artificial data
+    %   subset:   Subset of datasets to consider, nsims x 1 logical
+    %   inq:      ZLB duration index in sims
+    %
+    % Outputs:
+    %   draws_all: posterior draws, 1000 x nparam x nsims
+    %   nzlb:      number of zlb events in the datasets, nsims x 1 integer
+    %   NRMSE:     Normalized root mean squared error of the posterior
+    %                draws, nsims x nparam+1
+    %   MDD:       Marginal data density, nsims x 1
+    %   reject0595: Share of datasets that truth is outside of credible
+    %                 set, nparam+1 x 1
+    %   postvar:   Posterior variance, nparam+1 x 1
+    %   MSE:   Mean-squared error, nparam+1 x 1
+    %   bias2:   Square of the bias of the mean, nparam+1 x 1
+
+    % Finished datasets
+    if isimdone == 0
+        isimdone = ones(nsims,1);
+    end
+    draws_all = NaN(1000,F.nparam,nsims);
+    nmodesearchdraws = 5000;
+
+    % True parameters
+    for j = 1:F.nparam
+       eval(['thetatilde(j) = P.' F.priors{j,1} ';']);
+    end
+
+    %Loop through simulations
+    itemp = 1;
+    nzlb = zeros(nsims,1);
+    for isim = 1:nsims
+        % Check if posterior files exist
+        filename = [folder,'zlb',num2str(inq),'/thin/' num2str(isim) '-MHdraws.txt'];
+        if (exist(filename,'file') && isimdone(isim)==1)
+            % Load draws
+            draws = textread(filename,'%f');
+            draws = reshape(draws,[numel(draws)/F.nparam,F.nparam]);
+            draws_all(:,:,isim) = draws;
+            % Load data
+            data = sims(:,:,isim);
+            % Load discarded draws and log likelihoods for MDD
[…]

### 2019-02-15 src/general/script_results_tables2.m

@@ -1,0 +1,150 @@
+%  This file creates a figure with the RMSE of filtered state estimates. 
+%  The output is tbd
+
+clear
+clc
+close all
+
+savename = 'table4b.tex';
+%Specifications to include: path, method, filter, measurement error
+specs = {...
+    '../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';         
+    };
+
+% First load in the simulated date from the true model
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+% Load parameter names - true model
+load('options.mat','V','P','F')
+%Rename V to indicate it is from true model
+Vcap= V;
+Pcap = P;
+Fcap = F;
+
+%Load in V from misspecified model
+load('../Results-nocap/options.mat','V','P','F')
+
+means = nan(F.nparam,nsims,nZLBpers,nspecs);
+
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    % Loop through ZLB durations
+    for inq = 1:numel(nqs)
+        % ZLB duration
+        nq = nqs(inq);
+        disp(['ZLB duration = ' num2str(nq)])
+        for isim = 1:nsims
+            %Load filtered state estimates if they exist, otherwise keep as
+            %NaNs
+            filename = [specs{ifolder,1},'zlb',num2str(inq),'/thin/',num2str(isim),'-MHdraws.txt'];
+            if exist(filename, 'file') == 2
+                draws = textread(filename,'%f');
+                means(:,isim,inq,ifolder) = mean(reshape(draws,[ndraws,F.nparam]),1);
+            end
+        end
+    end
+end   
+
+p50 = squeeze(quantile(means,0.5,2));
+p05 = squeeze(quantile(means,0.05,2));
[…]

### 2019-02-15 src/general/script_simulate.m

@@ -1,115 +1,0 @@
-% Calculate simulation statistics
-clear
-clc
-%--------------------------------------------------------------------------
-% Run simulations
-%--------------------------------------------------------------------------
-if exist('Rules\results.mat','file')
-    load('Rules\results.mat')
-    if exist('tables','var')
-        if ~exist('sims','var')
-            runsims = 'on';
-        else
-            runsims = 'off';
-        end
-    else
-        disp('Run script_tables.m first to get the alternative solutions.')
-        break
-    end
-else
-    disp('Run script_TL_onetime.m first to get the baseline solution.')
-    break
-end
-% Simulation parameters
-nburn = 10000;  % Periods to get stochastic steady state
-nplot = 500000;
-npers = nburn+nplot;
-
-% Set random number seed and draw shocks
-mtstream = RandStream('mt19937ar','seed',2);
-RandStream.setGlobalStream(mtstream);
-shockse = randn(nplot,1);
-shocksu = randn(nplot,1);
-
-if strcmp(runsims,'on')
-    nparams = size(tables,1);
-    % Simulate for each parameterization
-    sims = zeros(nparams,9);
-    if matlabpool('size') == 0
-        matlabpool
-    end
-    parfor iparam = 1:nparams
-        % Load ZLB solution
-        P.phiy = tables(iparam,2);
-        P.phipi = tables(iparam,3);
-        suffix = ['_phiy' num2str(1e3*P.phiy) '_phipi' num2str(1e2*P.phipi)];
-        temp = load([baselinename suffix '.mat'],'pf','O','P','S','G');
-        pf = temp.pf;
-        O = temp.O;
-        P = temp.P;
-        S = temp.S;
-        G = temp.G;
-        % Production function
-        y = G.z_gr.*G.k_gr.^P.alpha.*pf.n.^(1-P.alpha); 
-        %   Interest rate rule     
-        r = max(1,S.r*(pf.pi/P.pi).^P.phipi.*(y./O.ybench).^P.phiy);
-        zlbbinds = length(find(r == 1))/G.nodes;
-        %--------------------------------------------------------------------------
-        % Simulate
-        %--------------------------------------------------------------------------
-        disp(['Simulating: ' suffix]);
-        % Technology shocks
-        e = zeros(npers,1);
-        e(nburn+1:end) = P.sige*shockse;
[…]

### 2019-02-15 src/general/tables/table_globalme.m

@@ -1,0 +1,155 @@
+%  This file creates a table with the median, credible sets and RMSE of
+%  mean posterior estimates for different ZLB bins and specifications.
+
+clear
+clc
+close all
+
+savename = 'table_globalme.tex';
+%Specifications to include: path, method, filter, measurement error, table
+%label
+specs = {...
+    '../../Estimation-global/me2/','global','pf','me2','NL-PF-2$\%$'; ...     
+    '../../Estimation-global/me5/','global','pf','me5','NL-PF-5$\%$';...   
+    '../../Estimation-global/me10/','global','pf','me10','NL-PF-10$\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+
+means = nan(F.nparam,nsims,nZLBpers,nspecs);
+
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    % Loop through ZLB durations
+    for inq = [1,numel(nqs)]
+        % ZLB duration
+        nq = nqs(inq);
+        disp(['ZLB duration = ' num2str(nq)])
+        for isim = 1:nsims
+            %Load posterior distributions they exist, otherwise keep as
+            %NaNs
+            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
+            if exist(filename, 'file') == 2
+                %Calculate mean across posterior distribution
+                means(:,isim,inq,ifolder) = textread(filename,'%f');
+            end
+        end
+    end
+end   
+
+%Median and credible sets across datasets (dim 2)
+pmean = squeeze(mean(means,2));
+p05 = squeeze(quantile(means,0.05,2));
+p95 = squeeze(quantile(means,0.95,2));
[…]

### 2019-02-15 src/general/tables/table_me5_nomiss.m

@@ -1,0 +1,154 @@
+%  This file creates a table with the median, credible sets and RMSE of
+%  mean posterior estimates for different ZLB bins and specifications.
+
+clear
+clc
+close all
+
+savename = 'table_me5_nomiss.tex';
+%Specifications to include: path, method, filter, measurement error, table
+%label
+specs = {...
+    '../../Estimation-global-nomiss/me5/','global','pf','me5','NL-PF-5$\%$'; ...   
+    '../../Estimation-pwlinear-nomiss/','pwlinear','if','me0','PW-IF-0$\%$';...  
+    '../../Estimation-linear-nomiss/me5/','linear','kf','me5','Lin-KF-5$\%$';...   
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+
+means = nan(F.nparam,nsims,nZLBpers,nspecs);
+
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    % Loop through ZLB durations
+    for inq = [1,numel(nqs)]
+        % ZLB duration
+        nq = nqs(inq);
+        disp(['ZLB duration = ' num2str(nq)])
+        for isim = 1:nsims
+            %Load posterior distributions they exist, otherwise keep as
+            %NaNs
+            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
+            if exist(filename, 'file') == 2
+                %Calculate mean across posterior distribution
+                means(:,isim,inq,ifolder) = textread(filename,'%f');
+            end
+        end
+    end
+end   
+
+%Median and credible sets across datasets (dim 2)
+pmean = squeeze(mean(means,2));
+p05 = squeeze(quantile(means,0.05,2));
[…]

### 2019-02-15 src/general/tables/table_moments.m

@@ -1,0 +1,261 @@
+%  This file creates a table with the median, credible sets and RMSE of
+%  mean posterior estimates for different ZLB bins and specifications.
+
+clear
+clc
+close all
+
+savename = 'table_moments.tex';
+%Specifications to include: path, method, filter, measurement error, table
+%label
+specs = {...
+    '../../Estimation-global/me5/','NL_PF_5','pf','me5','NL-PF-5$\%$';  
+    '../../Estimation-pwlinear/','PW_IF_0','if','me0','PW-IF-0$\%$';...  
+    '../../Estimation-linear/me0/','Lin_KF_0','kf','me2','Lin-KF-0$\%$';... 
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+nmoments = 4;
+
+% Load parameter names
+load('../options.mat','V','P','F')
+
+% Load actual data
+momentscap = textread('../../data-artificial/Ezlb_duration/moments.txt','%f');
+momentscap = reshape(momentscap,[nmoments,V.nvar-V.nfore]);
+
+Vcap= V;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+Vnstate = V.nvar-V.nfore
+
+%Create artificial data matrix (true model) that aligns with variable order
+%from the true model. Note that yg is named cg in misspec model
+moments = nan(nmoments,Vnstate);
+for ivar = 1:(Vnstate)
+    if strcmp(V.names{ivar},'cg')
+        moments(:,ivar) = momentscap(:,Vcap.yg);
+    else
+        eval(['moments(:,ivar) = momentscap(:,Vcap.',V.names{ivar},');']);
+    end
+end
+
+moments_est = nan(nmoments,Vnstate,nsims,nZLBpers,nspecs);
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    %Load state estimate for given specification
+    filename = [specs{ifolder,1},'/states/moments.txt'];
[…]

### 2019-02-15 src/general/tables/table_param_linkfme0nm_linkfme5nm.m

@@ -1,0 +1,152 @@
+%  This file creates a table with the median, credible sets and RMSE of
+%  mean posterior estimates for different ZLB bins and specifications.
+
+clear
+clc
+close all
+
+savename = 'table_param_linkfme0nm_linkfme5nm.tex';
+%Specifications to include: path, method, filter, measurement error, table
+%label
+specs = {...
+    %'../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    %'../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
+    %'../../Estimation-global-nomiss/me5/','global','pf','me5','No misspecification, Global, Particle Filter, ME 5$\%$';    
+    %'../../Estimation-pwlinear-nomiss/','pwlinear','if','me0','No misspecification, Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-linear-nomiss/me0/','linear','kf','me0','No misspecification, Level Linear, Kalman Filter, ME 0$\%$';...
+    '../../Estimation-linear-nomiss/me5/','linear','kf','me5','No misspecification, Level Linear, Kalman Filter, ME 5$\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+
+means = nan(F.nparam,nsims,nZLBpers,nspecs);
+
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    % Loop through ZLB durations
+    for inq = 1:numel(nqs)
+        % ZLB duration
+        nq = nqs(inq);
+        disp(['ZLB duration = ' num2str(nq)])
+        for isim = 1:nsims
+            %Load posterior distributions they exist, otherwise keep as
+            %NaNs
[…]

### 2019-02-15 src/general/tables/table_param_linkfme5_stickyw.m

@@ -1,0 +1,147 @@
+%  This file creates a table with the median, credible sets and RMSE of
+%  mean posterior estimates for different ZLB bins and specifications.
+
+clear
+clc
+close all
+
+savename = 'table_param_linkfme5_stickyw.tex';
+
+%Specifications to include: path, method, filter, measurement error, table
+%label
+specs = {...
+    '../../Estimation-linear/me5/','linear','kf','me0','Linear, Kalman Filter, ME 5$\%$';...
+    '../../Estimation-linear-stickyw/me5/','linear','kf','me0','Linear, Kalman Filter, ME 5$\%$, Sticky Wages';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+
+means = nan(F.nparam,nsims,nZLBpers,nspecs);
+
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    % Loop through ZLB durations
+    for inq = 1:numel(nqs)
+        % ZLB duration
+        nq = nqs(inq);
+        disp(['ZLB duration = ' num2str(nq)])
+        for isim = 1:nsims
+            %Load posterior distributions they exist, otherwise keep as
+            %NaNs
+            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
+            if exist(filename, 'file') == 2
+                %Calculate mean across posterior distribution
+                means(:,isim,inq,ifolder) = textread(filename,'%f');
+            end
+        end
+    end
+end   
+
+%Median and credible sets across datasets (dim 2)
+p50 = squeeze(quantile(means,0.5,2));
+p05 = squeeze(quantile(means,0.05,2));
+p95 = squeeze(quantile(means,0.95,2));
+%RMSE across datasets (dim 2), ignore nans
[…]

### 2019-02-15 src/general/tables/table_param_me5nm_pwnm.m

@@ -1,0 +1,151 @@
+%  This file creates a table with the median, credible sets and RMSE of
+%  mean posterior estimates for different ZLB bins and specifications.
+
+clear
+clc
+close all
+
+savename = 'table_param_me5nm_pwnm.tex';
+%Specifications to include: path, method, filter, measurement error, table
+%label
+specs = {...
+    %'../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    %'../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
+    '../../Estimation-global-nomiss/me5/','global','pf','me5','No misspecification, Global, Particle Filter, ME 5$\%$';    
+    '../../Estimation-pwlinear-nomiss/','pwlinear','if','me0','No misspecification, Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    %'../../Estimation-linear-nomiss/me0/','linear','kf','me0','No misspecification, Level Linear, Kalman Filter, ME 0$\%$';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+
+means = nan(F.nparam,nsims,nZLBpers,nspecs);
+
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    % Loop through ZLB durations
+    for inq = 1:numel(nqs)
+        % ZLB duration
+        nq = nqs(inq);
+        disp(['ZLB duration = ' num2str(nq)])
+        for isim = 1:nsims
+            %Load posterior distributions they exist, otherwise keep as
+            %NaNs
+            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
+            if exist(filename, 'file') == 2
[…]

### 2019-02-15 src/general/tables/table_param_stickyw.m

@@ -1,0 +1,147 @@
+%  This file creates a table with the median, credible sets and RMSE of
+%  mean posterior estimates for different ZLB bins and specifications.
+
+clear
+clc
+close all
+
+savename = 'table_param_stickyw.tex';
+
+%Specifications to include: path, method, filter, measurement error, table
+%label
+specs = {...
+    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
+    '../../Estimation-pwlinear-stickyw/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$, Sticky Wages';...
+    };
+
+npers = 120;
+nsimsall = 100;
+nsims = 50;
+nZLBpers = 6;
+nqs = [0,6,12,18,24,30];
+nspecs = size(specs,1);
+ndraws = 1000;
+
+%Load in V from misspecified model
+load('../../Results-nocap/options.mat','V','P','F')
+
+means = nan(F.nparam,nsims,nZLBpers,nspecs);
+
+%Loop through specifications
+for ifolder = 1:size(specs,1)
+    disp(['Specification: ' specs{ifolder,1}])
+    % Loop through ZLB durations
+    for inq = 1:numel(nqs)
+        % ZLB duration
+        nq = nqs(inq);
+        disp(['ZLB duration = ' num2str(nq)])
+        for isim = 1:nsims
+            %Load posterior distributions they exist, otherwise keep as
+            %NaNs
+            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
+            if exist(filename, 'file') == 2
+                %Calculate mean across posterior distribution
+                means(:,isim,inq,ifolder) = textread(filename,'%f');
+            end
+        end
+    end
+end   
+
+%Median and credible sets across datasets (dim 2)
+p50 = squeeze(quantile(means,0.5,2));
+p05 = squeeze(quantile(means,0.05,2));
+p95 = squeeze(quantile(means,0.95,2));
[…]

### 2019-03-02 src/general/eqm_fp.m
Get solution for fp ARTgs!

@@ -101,7 +101,7 @@ Eppc = sum(EppcArr3(:));
 %Res(5,icol) = P.varphiw*(wg-1)*wg-((1-P.thetaw)*wp+P.thetaw*wf)*n/yf-P.varphiw*Ewpc;
 
 %pigap,n,q,mc
-x_up(3) = Ecap; %pf.q
+x_up(3) = Ecap; %pf.q %all policy functions at time t
 pf_lam = 1/(s*i*Ebond/(P.pi*lam));
 c_pf = pf_lam + P.h*c/g;
 var = (1-P.g*Einv)/x_up(3); %just q?
@@ -109,9 +109,11 @@ xg_pf = 1/3*(sqrt(7-6*var)+2);
 x_pf = xg_pf*P.g*x/g;
 y_pf = c_pf + x_pf;
 x_up(2) = (y_pf/(k/g)^P.alpha)^(1/(1-P.alpha)); %pf.n
-RHS_firm = 1 - P.theta + P.theta*mc + P.varphi*Eppc;
+RHS_firm = 1 - P.theta + P.theta*mc + P.varphi*Eppc;%/y*y_pf;
 x_up(1) = (1+sqrt((P.varphi+4*RHS_firm)/P.varphi))/2;
+w = (1-P.alpha)*mc*y/n;
+x_up(4) = (w*x_up(2))/((1-P.alpha)*y_pf);
 %LHS_firm = P.varphi*(x_up(1)-1)*x_up(1)-(1-P.theta) - P.varphi*Eppc;
-LHS_firm = P.varphi*(pigap-1)*pigap-(1-P.theta) - P.varphi*Eppc;
-x_up(4) = LHS_firm/P.theta;
+%LHS_firm = P.varphi*(pigap-1)*pigap-(1-P.theta) - P.varphi*Eppc;
+%x_up(4) = LHS_firm/P.theta;
 end

### 2019-03-07 src/general/Fallterp743_exogfirst.f90
Create new branch to make fp with RT-capital

@@ -1,266 +1,0 @@
-#include "fintrf.h"
-subroutine mexFunction(nlhs, plhs, nrhs, prhs)
-    ! Declarations
-	implicit none
-
-    ! mexFunction argument
-    mwPointer plhs(*), prhs(*)    
-    integer*4 nlhs, nrhs
-    
-    ! Function declarations
-    mwSize mxGetM,mxGetN  
-    mwpointer mxGetPr, mxCreateNumericArray, mxGetDimensions 
-    double precision mxGetScalar  
-    integer*4 mxClassIDFromClassName 
-    
-    ! Pointers to input/output mxArrays
-    mwpointer x1_pr,x2_pr,x3_pr,x4_pr,x5_pr,x6_pr,x7_pr
-    mwpointer x1i_pr,x2i_pr,x3i_pr
-    mwpointer pf1_pr,pf2_pr,pf3_pr,pf4_pr
-    mwpointer o1_pr,o2_pr,o3_pr,o4_pr
-    
-    ! Array information
-	mwSize nx1,nx2,nx3,nx4,nx5,nx6,nx7,nodes,e1,e2,e3
-	integer*4 myclassid
-	double precision, allocatable, dimension(:) :: x1,x2,x3,x4,x5,x6,x7,x1i,x2i,x3i
-	double precision x4i,x5i,x6i,x7i
-	double precision, allocatable, dimension(:,:,:,:,:,:,:) :: pf1,pf2,pf3,pf4
-	double precision, allocatable, dimension(:,:,:) :: o1,o2,o3,o4
-    
-    ! Load Inputs
-    ! Grids
-    nx1 = mxGetN(prhs(1))  
-    nx2 = mxGetN(prhs(2))  
-    nx3 = mxGetN(prhs(3))
-    nx4 = mxGetN(prhs(4))
-    nx5 = mxGetN(prhs(5))
-    nx6 = mxGetN(prhs(6))
-    nx7 = mxGetN(prhs(7))
-    nodes = nx1*nx2*nx3*nx4*nx5*nx6*nx7
-    allocate(x1(nx1))
-    allocate(x2(nx2))
-    allocate(x3(nx3))
-    allocate(x4(nx4))
-    allocate(x5(nx5))
-    allocate(x6(nx6))
-    allocate(x7(nx7))
-    x1_pr = mxGetPr(prhs(1))
[…]

### 2019-03-07 src/general/Fallterp853_R.f90

@@ -1,205 +1,0 @@
-#include "fintrf.h"
-subroutine mexFunction(nlhs, plhs, nrhs, prhs)
-    ! Declarations
-	implicit none
-
-    ! mexFunction argument
-    mwPointer plhs(*), prhs(*)    
-    integer*4 nlhs, nrhs
-    
-    ! Function declarations
-    mwSize mxGetN  
-    mwpointer mxGetPr, mxCreateNumericArray, mxGetDimensions 
-    double precision mxGetScalar  
-    integer*4 mxClassIDFromClassName 
-    
-    ! Pointers to input/output mxArrays
-    mwpointer x4_pr,x5_pr,x6_pr,x7_pr,x8_pr
-    mwpointer pf1_pr,pf2_pr,pf3_pr,pf4_pr,pf5_pr
-    mwpointer o1_pr,o2_pr,o3_pr,o4_pr,o5_pr
-    
-    ! Array information
-	mwSize nx1,nx2,nx3,nx4,nx5,nx6,nx7,nx8,nodes
-	integer*4 myclassid
-	double precision, allocatable, dimension(:) :: x4,x5,x6,x7,x8
-	double precision x4i,x5i,x6i,x7i,x8i
-	double precision, allocatable, dimension(:,:,:,:,:,:,:,:) :: pf1,pf2,pf3,pf4,pf5
-	double precision, allocatable, dimension(:,:,:) :: o1,o2,o3,o4,o5
-	  
-    ! Load Inputs
-    nx1 = mxGetScalar(prhs(1))
-    nx2 = mxGetScalar(prhs(2))
-    nx3 = mxGetScalar(prhs(3))
-    nx4 = mxGetScalar(prhs(4))
-    nx5 = mxGetScalar(prhs(5))
-    nx6 = mxGetScalar(prhs(6))
-    nx7 = mxGetScalar(prhs(7))
-    nx8 = mxGetScalar(prhs(8))
-    nodes = nx1*nx2*nx3*nx4*nx5*nx6*nx7*nx8
-    allocate(x4(nx4))
-    allocate(x5(nx5))
-    allocate(x6(nx6))
-    allocate(x7(nx7))
-    allocate(x8(nx8))
[…]

### 2019-03-07 src/general/RT-Capital/Results/eqm.m

@@ -1,0 +1,93 @@
+function R = eqm(x,state,P,S,G,pf,...
+                 gpArr,betapArr,weightArr)
+
+% Preallocate function output
+R = zeros(size(x));
+Rdim = size(R,2);
+
+% State Values
+c = state(1);   	%Consumption last period
+k = state(2);  	    %Capital last period
+i = state(3);       %Investment last period   
+rn = state(4);  	%Notional interest rate last period
+g = state(5);       %Growth state current period
+mp = state(6);      %Interest rate shock current period 
+
+for j = 1:Rdim   
+    % Policy Function Guesses
+    n = x(1,j);     %Labor policy current period 
+    q = x(2,j);     %Tobin's q current period
+    pie = x(3,j);   %Inflation current period  
+    psi = x(4,j);   %Marginal cost current period
+    %----------------------------------------------------------------------
+    % Solve for variables
+    %----------------------------------------------------------------------
+    % Production function
+    y = (k/g)^P.alpha*n^(1-P.alpha);
+    % Real GDP
+    rgdp = c+i;
+    rgdpp = (1-(P.varphi*(pie/P.pi-1)^2)/2)*y;
+    % Interest rate rule
+    rnp = rn^P.rhor*(S.r*(pie/P.pi)^P.phipi*...
+          (g*rgdpp/(P.g*rgdp))^P.phiy)^(1-P.rhor)*exp(mp);   
+    r = max(P.zlb,rnp);
+    % Firm FOC labor
+    w = (1-P.alpha)*psi*y/n;
+    % FOC labor
+    cp = w/(S.chi*n^P.eta)+P.h*c/g;
+    % Aggregate resource constraint
+    ip = rgdpp - cp;  
+    % Investment adjustment costs
+    iac = ip*g/(i*P.g);
+    % Law of motion for capital
+    kp = (1-P.delta)*(k/g)+ip*(1-P.nu*(iac-1)^2/2);         
+    %----------------------------------------------------------------------
+    % Linear interpolation of the policy variables 
+    %---------------------------------------------------------------------- 
+    [npArr,qpArr,pipArr,psipArr] = Fallterp743(...
+       G.c_grid,G.k_grid,G.i_grid,G.rn_grid,...
+       G.g_grid,G.beta_grid,G.mp_grid,...
[…]

### 2019-03-07 src/general/RT-Capital/Results/linmodel.m

@@ -1,0 +1,163 @@
+function [T,M,eu] = linmodel(P,S,V)
+
+% [T,M,eu] = linmodel(P,S,V)
+%   Solves the log-linear model with GENSYS
+% Inputs:
+%     P     :   Structure of parameters
+%     S     :   Structure of steady state values
+%     V     :   Structure of variable locations and names
+% Output:
+%     T     :   Transition matrix
+%     M     :   Impact matrix
+%     eu    :   [existence, uniqueness]
+
+%---------------------------------------------
+%   Initialize GENSYS components
+%---------------------------------------------
+G0 = zeros(V.nvar);
+G1 = zeros(V.nvar);
+Psi = zeros(V.nvar,V.nshock);
+Pi = zeros(V.nvar,V.nfore);
+CC = zeros(V.nvar,1);
+j = 0;
+%---------------------------------------------
+j=j+1;%	[FOC Labor]
+%---------------------------------------------
+G0(j,V.w) = 1;
+G0(j,V.n) = -P.eta;
+G0(j,V.c) = -1/(1-P.htilde);
+G0(j,V.g) = -P.htilde/(1-P.htilde);
+G1(j,V.c) = -P.htilde/(1-P.htilde);
+%---------------------------------------------
+j = j+1;% [FOC Bond]
+%---------------------------------------------
+G0(j,V.c) = 1/(1-P.htilde);
+G0(j,V.pi) = 1;
+G0(j,V.beta) = -1;
+G0(j,V.g) = 1/(1-P.htilde);
+G1(j,V.r) = 1;
+G1(j,V.c) = (1+P.htilde)/(1-P.htilde);
+G1(j,V.g) = P.htilde/(1-P.htilde);
+G1(j,V.clag) = -P.htilde/(1-P.htilde);
+Pi(j,V.fec) = 1/(1-P.htilde);
+Pi(j,V.fepi) = 1;
+Pi(j,V.febeta) = -1;
+Pi(j,V.feg) = 1/(1-P.htilde);
+%---------------------------------------------
+j = j+1;% [FOC Capital]
+%---------------------------------------------
+G0(j,V.q) = P.beta*(1-P.delta)/P.g;
+G0(j,V.beta) = 1;
+G0(j,V.rk) = 1-P.beta*(1-P.delta)/P.g;
+G0(j,V.g) = -1/(1-P.htilde);
+G0(j,V.c) = -1/(1-P.htilde);
+G1(j,V.q) = 1;
[…]

### 2019-03-07 src/general/RT-Capital/Results/variables.m

@@ -1,0 +1,72 @@
+function V = variables
+
+% Variables: Names variables and assigns locations
+% Inputs:
+%     model
+% Output:
+%     V     :   Structure of variable locations and names
+
+% Variables names
+V.names =      {'n'          %1  Labor hours
+                'w'          %2  Real wage rate
+                'c'          %3  Consumption
+                'y'          %4  Output                
+                'k'          %5  Capital
+                'i'          %6  Investment
+                'q'          %7  Tobin's q 
+                'rk'         %8  Rental rate
+                'psi'        %9  Marginal cost 
+                'r'          %10 Nominal interest rate
+                'pi'         %11 Gross inflation
+                'rn'         %12 Notional interest rate 
+                'beta'       %13 Discount factor
+                'g'          %14 Growth rate            
+                'rgdp'       %15 Real GDP
+                'clag'       %16 Lagged consumption
+                'ilag'       %17 Lagged investment                
+               };
+
+% Variables titles        
+V.desc =      { 'Labor Hours'
+                'Real Wage Rate'
+                'Consumption'
+                'Output'
+                'Capital'
+                'Investment'
+                'Tobin''s q'
+                'Rental Rate'
+                'Marginal Cost'
+                'Nominal Interest Rate'
+                'Inflation Rate'
+                'Notional Interest Rate'
+                'Discount Factor'               
+                'Growth Rate'
+                'Real GDP'
+                'Lagged Consumption'
+                'Lagged Investment'            
+            };
+
+%Shocktypes: 
+V.shocktypes = {'g','beta','mp'};  
+% Forecast errors
+V.foretypes = {'c','beta','g','rk','q','i','pi'}; 
+
+% Number of variables
+V.nvar = length(V.names);
+% Number of shocks
+V.nshock = length(V.shocktypes);
+% Number of forecast errors
+V.nfore = length(V.foretypes);
+
+% Establish variable index
+for j = 1:V.nvar
+   eval(['V.' V.names{j} ' = j;']);      
+end
+% Establish shock index
+for j = 1:V.nshock
+    eval(['V.eps' V.shocktypes{j} ' = j;'])
+end
+% Establish forecast error index
+for j = 1:V.nfore
+    eval(['V.fe' V.foretypes{j} ' = j;'])
+end

### 2019-03-07 src/general/eqm_fp.m

@@ -1,119 +1,0 @@
-function x_up = eqm_fp(pf0,state,O,P,S,G,pf,gpArr3,weightArr3)
-
-% State Values
-g = state(1);           %Growth state current period
-s = state(2);           %Risk premium state current period
-mp = state(3);          %Monetary policy shock current period
-in = state(4);          %Notional interest rate last period
-c = state(5);           %Consumption last period
-k = state(6);           %Capital last period
-x = state(7);           %Investment last period   
-%w = state(8);           %Real wage last period
-
-% Policy Function Guesses
-%cp = pf0(1,icol);      %Consumption current period
-pigap = pf0(1);   %Inflation gap current period  
-n = pf0(2);       %Labor current period 
-q = pf0(3);       %Tobin's q current period
-%ups = pf0(5,icol);     %Utilization current period
-mc = pf0(4);      %Marginal cost current period    
-%----------------------------------------------------------------------
-% Current period
-%----------------------------------------------------------------------
-% Production function (2)
-yf = (k/g)^P.alpha*n^(1-P.alpha); 
-% Real gdp
-y = c + x;
-yp = (1-P.varphi*(pigap-1)^2/2)*yf;
-% Output growth
-yg = g*yp/(P.g*y);    
-% Notional Interest Rate (9)
-inp = in^P.rhoi*(S.i*pigap^P.phipi*yg^P.phiy)^(1-P.rhoi)*exp(mp); 
-% Nominal Interest Rate (10)
-i = inp;    
-% Firm FOC labor (5)
-w = (1-P.alpha)*mc*yf/n;
-% FOC labor
-cp = w/(S.chi*n^P.eta)+P.h*c/g;
-% Aggregate resource constraint
-xp = yp - cp;
-% Investment growth gap (14)
-xg = g*xp/(P.g*x);    
-% Law of motion for capital (15)
-kp = (1-P.delta)*(k/g)+xp*(1-P.nu*(xg-1)^2/2);       
-% Inverse MUC (11)
-lam = cp-P.h*c/g;
[…]

### 2019-03-07 src/general/eqm_fp_gustetal.m

@@ -1,155 +1,0 @@
-function x_up = eqm_fp_gustetal(pf0,state,O,P,S,G,pf,gpArr3,mpArr3,weightArr3)
-
-% State Values
-g = state(1);           %Growth state current period
-s = state(2);           %Risk premium state current period
-mp = state(3);          %Monetary policy shock current period
-in = state(4);          %Notional interest rate last period
-c = state(5);           %Consumption last period
-k = state(6);           %Capital last period
-x = state(7);           %Investment last period   
-%w = state(8);           %Real wage last period
-
-% Policy Function Guesses
-%cp = pf0(1,icol);      %Consumption current period
-pigap = pf0(1);   %Inflation gap current period  
-n = pf0(2);       %Labor current period 
-n_zlb = pf0(3);
-q = pf0(4);       %Tobin's q current period
-%ups = pf0(5,icol);     %Utilization current period
-mc = pf0(5);      %Marginal cost current period    
-%----------------------------------------------------------------------
-% Current period
-%----------------------------------------------------------------------
-% Production function (2)
-yf = (k/g)^P.alpha*n^(1-P.alpha); %should also be recalculated? CHECK
-% Real gdp
-y = c + x;
-yp = (1-P.varphi*(pigap-1)^2/2)*yf;
-% Output growth
-yg = g*yp/(P.g*y);    
-% Notional Interest Rate (9)
-inp = in^P.rhoi*(S.i*pigap^P.phipi*yg^P.phiy)^(1-P.rhoi)*exp(mp); 
-% Nominal Interest Rate (10)
-i = inp; 
-if inp > 1
-    % Firm FOC labor (5)
-    w = (1-P.alpha)*mc*yf/n;
-    % FOC labor
-    cp = w/(S.chi*n^P.eta)+P.h*c/g;
-    % Aggregate resource constraint
-else
-%   % Production function (2)
[…]

### 2019-03-07 src/general/figures/figure_Eduration_zlb6.m

@@ -1,238 +1,0 @@
-%  Creates a figure of the Expectated duration, actual and estimated
-%  scatter pot
-
-clear
-clc
-close all
-
-savename = 'Eduration_zlb6';
-
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
-    '../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load actual expected duration from DGP
-Eduration = textread('../../data-artificial/Ezlb_duration/Eduration.txt','%f');
-Eduration = reshape(Eduration,[npers,nsimsall,nZLBpers]);
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-Eduration_est = nan(npers,nsims,nZLBpers,nspecs);
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    %Load state estimate for given specification
-    filename = [specs{ifolder,1},'/states/Eduration.txt'];
-    if exist(filename, 'file') == 2
-        Eduration_temp = textread(filename,'%f');
-        Eduration_temp = reshape(Eduration_temp,[npers,nsims,nZLBpers]);
-        %Global data may be missing, replace zeros with nan
-        %if strcmp(specs{ifolder,2},'global')
-        %   Eduration_temp(Eduration_temp==0) = NaN;
-        %end
-        %Error in global and linear expectation calculation means Eduration
-        %needs to be reduced by 1
-        %if (strcmp(specs{ifolder,2},'global') || strcmp(specs{ifolder,2},'linear'))
-        %    Eduration_temp = Eduration_temp - 1;
[…]

### 2019-03-07 src/general/figures/figure_crps_example.m

@@ -1,108 +1,0 @@
-%  Creates a figure of the percent of actuals outside of forecast credible sets
-% from the different model %  specifications from the periods just prior to the ZLB binding.
-
-clear
-clc
-close all
-plotops
-
-savename = 'crps_example'; 
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-
-% Load parameter names
-load('../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore;
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
-%Load forecast distribution
-forecast_dist = textread('../../Estimation-global/me5/states/forecast_dist.txt','%f');
-forecast_dist = 100*(forecast_dist.^4-1);
-actual = 100*(sims(89+8,V.i,2,2)^4-1);
-disp(['mean forecast =    ',num2str(mean(forecast_dist))])
-disp(['true realization = ',num2str(actual)])
-pts = 0:0.01:8;
-%%
-%   Subplot padding
-plotposition = [1 1 6.5 2.75];
-pad.topmarg = .12; % Increase if subplot title is cut off
-pad.leftmarg = .05; % Increase if ylabel is cut off
-pad.vspace = 0.04;
-pad.hspace = .08;
-pad.rightmarg = .025; % Decrease if white-space on RHS
-pad.botmarg = .15; % Increase if xaxis lables are cut off
[…]

### 2019-03-07 src/general/figures/figure_forecast_accuracy2.m

@@ -1,168 +1,0 @@
-%  Creates a figure of the RMSE forecasts from the different model
-%  specifications from the periods just prior to the ZLB binding.
-
-clear
-clc
-close all
-savename = 'forecast_accuracy'; 
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
-    '../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
-    '../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
-    '../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    %'../../Estimation-linear/me0/','linear','kf','me0','Lin-KF-$0\%$';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load parameter names
-load('../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore;
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
-%Load in forecasts from the specifications
-temp = textread([specs{1,1},'forecast.txt'],'%f');
[…]

### 2019-03-07 src/general/figures/figure_in_accuracy_bar.m

@@ -1,174 +1,0 @@
-%  Creates a figure of the RMSE of RMSE of filtered state estimates across
-%  ZLB bins and specification. Bottom of the code plots various simulations
-
-clear
-clc
-close all
-savename = 'in_accuracy_bar'; 
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    '../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
-    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
-    '../../Estimation-global/me10/','global','pf','me10','Global, Particle Filter, ME 10$\%$';  ...
-    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load parameter names
-load('../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore;
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
-states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    %Load state estimate for given specification
-    filename = [specs{ifolder,1},'/states/states.txt'];
-    if exist(filename, 'file') == 2
[…]

### 2019-03-07 src/general/figures/figure_simulation_comp.m

@@ -1,125 +1,0 @@
-% Simulation comparison of normal and ZLB times
-clear
-clc
-close all
-
-% Saving 'on' or 'off'
-saving = 'on';
-
-% Simulation ZLB duration: 1SDx4, 1SDx7, 1p5SDx4
-dur = '1p5SDx4';
-
-% Load V from capital model
-load('../options.mat','V')
-V.nstate = V.nvar - V.nfore;
-Vcap = V;
-
-% Load structures for no capital model
-load('../../Results-nocap/options.mat','V','P','F')
-V.nstate = V.nvar - V.nfore;
-
-%--------------------------------------------------------------------------
-% True simulation
-%--------------------------------------------------------------------------
-T = 21;
-simstemp = textread(['../../data-artificial/simulation_',dur,'.txt'],'%f');
-simstemp = reshape(simstemp,[T,Vcap.nstate]);
-sims{1} = simstemp(:,[Vcap.c,Vcap.n,Vcap.y,Vcap.yf,Vcap.yg,Vcap.w,...
-    Vcap.pi,Vcap.i,Vcap.in,Vcap.lam,Vcap.g,Vcap.s,Vcap.mp]);
-
-%--------------------------------------------------------------------------
-% NL-PF-5% simulations
-%--------------------------------------------------------------------------
-nsims = 100;
-nZLBpers = 6;
-simstemp = textread(['../../Estimation-global/me5/simulation_',dur,'.txt'],'%f');
-simstemp = reshape(simstemp,[T,V.nstate,nsims,nZLBpers]);
-simstemp(:,:,51:end,:) = [];
-simstemp = reshape(simstemp,[T,V.nstate,(nsims/2)*nZLBpers]);
-sims{2}(:,:,1) = mean(simstemp,3);
-sims{2}(:,:,2:3) = quantile(simstemp,[.05,.95],3);
-
-%--------------------------------------------------------------------------
-% PW-IF-0% simulations
-%--------------------------------------------------------------------------
-simstemp = textread(['../../Estimation-pwlinear/simulation_',dur,'.txt'],'%f');
-simstemp = reshape(simstemp,[T,V.nstate,nsims,nZLBpers]);
-simstemp(:,:,51:end,:) = [];
-simstemp = reshape(simstemp,[T,V.nstate,(nsims/2)*nZLBpers]);
[…]

### 2019-03-07 src/general/figures/figure_state_accuracy.m

@@ -1,194 +1,0 @@
-%  Creates a figure of the RMSE of RMSE of filtered state estimates across
-%  ZLB bins and specification. Bottom of the code plots various simulations
-
-clear
-clc
-close all
-
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
-    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load parameter names
-load('../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore;
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
-states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    %Load state estimate for given specification
-    filename = [specs{ifolder,1},'/states/states.txt'];
-    if exist(filename, 'file') == 2
[…]

### 2019-03-07 src/general/figures/global-pwlinear-params/figure_Pzlb.m

@@ -1,231 +1,0 @@
-%  Creates a figure of the Expectated duration, actual and estimated
-%  scatter pot
-
-clear
-clc
-close all
-
-savename = 'Pzlb';
-
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';,...  
-    '../../../global-pwlinear-params/me5/','global','pf','me5','NL-PF using PW-IF estimated parameters';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load actual expected duration from DGP
-Pzlb = textread('../../../data-artificial/Ezlb_duration/Pzlb.txt','%f');
-Pzlb = reshape(Pzlb,[npers,nsimsall,nZLBpers]);
-
-% Load parameter names
-load('../../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
-states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
[…]

### 2019-03-07 src/general/figures/global-pwlinear-params/figure_forecast_accuracy.m

@@ -1,170 +1,0 @@
-%  Creates a figure of the RMSE forecasts from the different model
-%  specifications from the periods just prior to the ZLB binding.
-
-clear
-clc
-close all
-savename = 'forecast_accuracy'; 
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
-    '../../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
-    '../../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
-    '../../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../../Estimation-linear/me0/states/','linear','kf','me0','Lin-KF-$0\%$';...
-    '../../../global-pwlinear-params/me5/states/','global','pf','me5','NL-PF using PW-IF estimated parameters';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load parameter names
-load('../../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore;
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
[…]

### 2019-03-07 src/general/guess.m

@@ -1,50 +1,0 @@
-function pf = guess(V,P,S,G)
-
-% pf = guess(V,P,S,G) 
-%   Sets the initial policy functions
-% Inputs:
-%   V : structure of variable indices
-%   P : structure of parameters
-%   S : structure of steady state values 
-%   G : structure of grids
-% Outputs:
-%  pf : structure of policy functions
-
-%----------------------------------------------------------------------
-% log-linear solution - ZLB not imposed
-%----------------------------------------------------------------------
-[T,~,eu] = linmodel(P,S,V);
-disp(['Linear Solution: eu=' mat2str(eu)])
-
-% Transform discretized state space to level deviation from steady state
-g_gr_per = G.g_gr - P.g;
-s_gr_per = G.s_gr - P.s;
-mp_gr_per = G.mp_gr;
-in_gr_per = G.in_gr - S.i;
-c_gr_per = G.c_gr - S.c;
-k_gr_per = G.k_gr - S.k;
-x_gr_per = G.x_gr - S.x;
-%w_gr_per = G.w_gr - S.w;
-
-% Calculate linear policy functions on discretized state space 
-%linpf_c = zeros(G.griddim);
-linpf_pi = zeros(G.griddim);
-linpf_n = zeros(G.griddim);
-linpf_q = zeros(G.griddim);
-linpf_mc = zeros(G.griddim);
-%linpf_ups = zeros(G.griddim);
-state = [g_gr_per(:),s_gr_per(:),mp_gr_per(:),in_gr_per(:),c_gr_per(:),k_gr_per(:),x_gr_per(:)]';
-%linpf_c(:) = T(V.c,[V.g,V.s,V.mp,V.in,V.c,V.k,V.x])*state;
-linpf_pi(:) = T(V.pi,[V.g,V.s,V.mp,V.in,V.c,V.k,V.x])*state;
-linpf_n(:) = T(V.n,[V.g,V.s,V.mp,V.in,V.c,V.k,V.x])*state;
-linpf_q(:) = T(V.q,[V.g,V.s,V.mp,V.in,V.c,V.k,V.x])*state;
-%linpf_ups(:) = T(V.ups,[V.g,V.s,V.mp,V.in,V.c,V.k,V.x])*state;
-linpf_mc(:) = T(V.mc,[V.g,V.s,V.mp,V.in,V.c,V.k,V.x])*state;
-
[…]

### 2019-03-07 src/general/simulation.m

@@ -1,91 +1,0 @@
-function sims = simulation(pf,P,S,G,V,epsg,epss,epsmp,varargin)
-
-%----------------------------------------------------------------------
-% Initialize Simulation
-%----------------------------------------------------------------------
-% Containers for simulated variables
-[npers,nsims] = size(epsg);
-sims = zeros(npers,V.nplotvar,nsims);
-
-if isempty(varargin)
-    % Initialize state variables at deterministic steady state
-    sims(1,V.g,:) = P.g;
-    sims(1,V.s,:) = P.s;
-    sims(1,V.in,:) = S.in;
-    sims(1,V.c,:) = S.c;
-    sims(1,V.k,:) = S.k;
-    sims(1,V.x,:) = S.x;
-    sims(1,V.w,:) = S.w;
-    sims(1,V.y,:) = sims(1,V.c,:) + sims(1,V.x,:);
-else
-    if size(varargin{1},2) == 1
-        % Initialize state variables at stochastic steady state
-        sims(1,:,:) = repmat(varargin{1},[1 1 nsims]);
-    elseif size(varargin{1},2) > 1
-        % Initialize state variables at draw from ergodic distribution
-        sims(1,:,:) = varargin{1};
-    end
-end
-
-% Create 3rd dimension to match path
-epsgTemp = permute(epsg,[1,3,2]);
-epssTemp = permute(epss,[1,3,2]);
-epsmpTemp = permute(epsmp,[1,3,2]);
-
-%----------------------------------------------------------------------
-% Simulate time series
-%----------------------------------------------------------------------
-for t = 2:npers
-    % Growth shock
-    sims(t,V.g,:) = P.g + P.sigg*epsgTemp(t,1,:);
-    % Risk Premium shock
-    sims(t,V.s,:) = (1-P.rhos)*P.s + P.rhos*sims(t-1,V.s,:) + P.sigs*epssTemp(t,1,:);
-    % Monetary policy shock
-    sims(t,V.mp,:) = P.sigmp.*epsmpTemp(t,1,:);
-    % Evaluate policy functions
[…]

### 2019-03-07 src/general/tables/table_linkfme5_nomiss.m

@@ -1,155 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_linkfme5_nomiss.tex';
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-global-nomiss/me5/','global','pf','me5','NL-PF-5$\%$'; ... 
-    '../../Estimation-linear-nomiss/me0/','linear','kf','me0','Lin-KF-0$\%$';... 
-    '../../Estimation-linear-nomiss/me5/','linear','kf','me5','Lin-KF-5$\%$';...   
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = [1,numel(nqs)]
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
-                %Calculate mean across posterior distribution
-                means(:,isim,inq,ifolder) = textread(filename,'%f');
-            end
-        end
-    end
-end   
-
-%Median and credible sets across datasets (dim 2)
-p50 = squeeze(quantile(means,0.5,2));
-p05 = squeeze(quantile(means,0.05,2));
[…]

### 2019-03-07 src/general/tables/table_ols_rhos.m

@@ -1,48 +1,0 @@
-%  Creates a figure of the percent of actuals outside of forecast credible sets
-% from the different model %  specifications from the periods just prior to the ZLB binding.
-
-clear
-clc
-close all
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-ndraws = 1000;
-
-% Load parameter names
-load('../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore;
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
-s = squeeze(sims(2:120,V.s,:,:));
-lags = squeeze(sims(1:119,V.s,:,:));
-
-for izlb = 1:6
-    for itask = 1:50
-        b = regress(s(:,itask,izlb),[ones(119,1),lags(:,itask,izlb)]);
-        rhos(itask,izlb) = b(2);
-    end
-end
-median(rhos,1)

### 2019-03-07 src/general/tables/table_param_pw_pfme5.m

@@ -1,147 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_param_pw_pfme5.tex';
-
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';         
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = 1:numel(nqs)
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
-                %Calculate mean across posterior distribution
-                means(:,isim,inq,ifolder) = textread(filename,'%f');
-            end
-        end
-    end
-end   
-
-%Median and credible sets across datasets (dim 2)
-p50 = squeeze(quantile(means,0.5,2));
-p05 = squeeze(quantile(means,0.05,2));
-p95 = squeeze(quantile(means,0.95,2));
-%RMSE across datasets (dim 2), ignore nans
[…]

### 2019-03-07 src/general/tables/table_param_sum_neg_in.m

@@ -1,197 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_param_sum_neg_in.tex';
-
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';...         
-    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load parameter names
-load('../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
-in = squeeze(sims(:,V.in,:,:));
-neg_in = in;
-neg_in(in>1) = NaN;
-sumin = squeeze(sum(1-neg_in,1,'omitnan'));
-
-Qsumin = reshape(discretize(sumin(:),[min(sumin(:)),quantile(sumin(:),5),max(sumin(:))]),nsims,nZLBpers);
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
[…]

### 2019-03-07 src/general/tables/table_stickyw.m

@@ -1,153 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_stickyw.tex';
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-global/me5/','global','pf','me5','NL-PF-5$\%$'; ...   
-    '../../Estimation-pwlinear/','pwlinear','if','me0','PW-IF-0$\%$';...   
-    '../../Estimation-pwlinear-stickyw/','pwlinear','if','me0','PW-IF-0$\%$-Sticky Wages';...    
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = [1,numel(nqs)]
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
-                %Calculate mean across posterior distribution
-                means(:,isim,inq,ifolder) = textread(filename,'%f');
-            end
-        end
-    end
-end   
-
-%Median and credible sets across datasets (dim 2)
-pmean = squeeze(mean(means,2));
-p05 = squeeze(quantile(means,0.05,2));
-p95 = squeeze(quantile(means,0.95,2));
[…]

### 2019-03-07 src/general/tables/table_zlb7.m

@@ -1,147 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_zlb7.tex';
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-global/me5/','global','pf','me5','NL-PF-5$\%$'; ...   
-    '../../Estimation-pwlinear/','pwlinear','if','me0','PW-IF-0$\%$';...   
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 7;
-nqs = [0,6,12,18,24,30,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = [1:numel(nqs)]
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
-                %Calculate mean across posterior distribution
-                means(:,isim,inq,ifolder) = textread(filename,'%f');
-            end
-        end
-    end
-end   
-
-%Median and credible sets across datasets (dim 2)
-p50 = squeeze(quantile(means,0.5,2));
-p05 = squeeze(quantile(means,0.05,2));
-p95 = squeeze(quantile(means,0.95,2));
-%RMSE across datasets (dim 2), ignore nans
[…]

### 2019-03-08 src/general/figures/figure_credset_accuracy.m
Fix issue in fp with P.nu; eqm_fp_gustetal still won't converge

@@ -1,185 +1,0 @@
-%  Creates a figure of the percent of actuals outside of forecast credible sets
-% from the different model %  specifications from the periods just prior to the ZLB binding.
-
-clear
-clc
-close all
-savename = 'credset_accuracy'; 
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    %'../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  ...
-    '../../data-artificial/Ezlb_duration/','dgp','na','na','DGP';  ...
-    '../../Estimation-global/me5/states/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  ...
-    '../../Estimation-pwlinear/states/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../Estimation-linear/me0/states/','linear','kf','me0','Lin-KF-$0\%$';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load parameter names
-load('../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore;
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
[…]

### 2019-03-08 src/general/figures/global-pwlinear-params/figure_Eduration.m

@@ -1,239 +1,0 @@
-%  Creates a figure of the Expectated duration, actual and estimated
-%  scatter pot
-
-clear
-clc
-close all
-
-savename = 'Eduration';
-
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
-    '../../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
-    '../../../global-pwlinear-params/me5/','global','pf','me5','NL-PF using PW-IF estimated parameters';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load actual expected duration from DGP
-Eduration = textread('../../../data-artificial/Ezlb_duration/Eduration.txt','%f');
-Eduration = reshape(Eduration,[npers,nsimsall,nZLBpers]);
-
-%Load in V from misspecified model
-load('../../../Results-nocap/options.mat','V','P','F')
-
-Eduration_est = nan(npers,nsims,nZLBpers,nspecs);
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    %Load state estimate for given specification
-    filename = [specs{ifolder,1},'/states/Eduration.txt'];
-    if exist(filename, 'file') == 2
-        Eduration_temp = textread(filename,'%f');
-        Eduration_temp = reshape(Eduration_temp,[npers,nsims,nZLBpers]);
-        %Global data may be missing, replace zeros with nan
-        %if strcmp(specs{ifolder,2},'global')
-        %   Eduration_temp(Eduration_temp==0) = NaN;
-        %end
-        %Error in global and linear expectation calculation means Eduration
-        %needs to be reduced by 1
[…]

### 2019-03-08 src/general/figures/pf-me2-me10/figure_Eduration.m

@@ -1,240 +1,0 @@
-%  Creates a figure of the Expectated duration, actual and estimated
-%  scatter pot
-
-clear
-clc
-close all
-
-savename = 'Eduration';
-
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    '../../../Estimation-global/me2/','global','pf','me2','Global, Particle Filter, ME 2$\%$';  
-    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
-    '../../../Estimation-global/me10/','global','pf','me10','Global, Particle Filter, ME 10$\%$';  
-    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load actual expected duration from DGP
-Eduration = textread('../../../data-artificial/Ezlb_duration/Eduration.txt','%f');
-Eduration = reshape(Eduration,[npers,nsimsall,nZLBpers]);
-
-%Load in V from misspecified model
-load('../../../Results-nocap/options.mat','V','P','F')
-
-Eduration_est = nan(npers,nsims,nZLBpers,nspecs);
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    %Load state estimate for given specification
-    filename = [specs{ifolder,1},'/states/Eduration.txt'];
-    if exist(filename, 'file') == 2
-        Eduration_temp = textread(filename,'%f');
-        Eduration_temp = reshape(Eduration_temp,[npers,nsims,nZLBpers]);
-        %Global data may be missing, replace zeros with nan
-        %if strcmp(specs{ifolder,2},'global')
-        %   Eduration_temp(Eduration_temp==0) = NaN;
-        %end
[…]

### 2019-03-08 src/general/figures/pwlinear-stickyw/figure_Eduration.m

@@ -1,239 +1,0 @@
-%  Creates a figure of the Expectated duration, actual and estimated
-%  scatter pot
-
-clear
-clc
-close all
-
-savename = 'Eduration';
-
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';  
-    '../../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
-    '../../../Estimation-pwlinear-stickyw/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$, Sticky Wages';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load actual expected duration from DGP
-Eduration = textread('../../../data-artificial/Ezlb_duration/Eduration.txt','%f');
-Eduration = reshape(Eduration,[npers,nsimsall,nZLBpers]);
-
-%Load in V from misspecified model
-load('../../../Results-nocap/options.mat','V','P','F')
-
-Eduration_est = nan(npers,nsims,nZLBpers,nspecs);
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    %Load state estimate for given specification
-    filename = [specs{ifolder,1},'/states/Eduration.txt'];
-    if exist(filename, 'file') == 2
-        Eduration_temp = textread(filename,'%f');
-        Eduration_temp = reshape(Eduration_temp,[npers,nsims,nZLBpers]);
-        %Global data may be missing, replace zeros with nan
-        %if strcmp(specs{ifolder,2},'global')
-        %   Eduration_temp(Eduration_temp==0) = NaN;
-        %end
-        %Error in global and linear expectation calculation means Eduration
[…]

### 2019-03-08 src/general/figures/pwlinear-stickyw/figure_Pzlb.m

@@ -1,236 +1,0 @@
-%  Creates a figure of the Expectated duration, actual and estimated
-%  scatter pot
-
-clear
-clc
-close all
-
-savename = 'Pzlb';
-
-%Specifications to include: path, method, filter, measurement error,%label
-specs = {...
-    '../../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    '../../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';,...  
-    '../../../Estimation-pwlinear-stickyw/','pwlinear-stickyw','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$, Sticky Wages';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-% Load actual expected duration from DGP
-Pzlb = textread('../../../data-artificial/Ezlb_duration/Pzlb.txt','%f');
-Pzlb = reshape(Pzlb,[npers,nsimsall,nZLBpers]);
-
-% Load parameter names
-load('../../options.mat','V','P','F')
-
-% Load actual data
-simscap = textread('../../../data-artificial/sims.txt','%f');
-simscap = reshape(simscap,[npers,V.nvar-V.nfore,nsimsall,nZLBpers]);
-
-Vcap= V;
-
-%Load in V from misspecified model
-load('../../../Results-nocap/options.mat','V','P','F')
-Vnstate = V.nvar-V.nfore
-
-%Create artificial data matrix (true model) that aligns with variable order
-%from the true model. Note that yg is named cg in misspec model
-sims = nan(npers,Vnstate,nsims,nZLBpers);
-for ivar = 1:(Vnstate)
-    if strcmp(V.names{ivar},'cg')
-        sims(:,ivar,:,:) = simscap(:,Vcap.yg,1:nsims,:);
-    else
-        eval(['sims(:,ivar,:,:) = simscap(:,Vcap.',V.names{ivar},',1:nsims,:);']);
-    end
-end
-
-states = nan(npers,Vnstate,nsims,nZLBpers,nspecs);
-%Loop through specifications
-for ifolder = 1:size(specs,1)
[…]

### 2019-03-08 src/general/tables/table_linkfme5.m

@@ -1,153 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_linkfme5.tex';
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-global/me5/','global','pf','me5','NL-PF-5$\%$'; ... 
-    '../../Estimation-linear/me5/','linear','kf','me5','Lin-KF-5$\%$';... 
-    '../../Estimation-linear/me0/','linear','kf','me0','Lin-KF-0$\%$';...   
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = [1,numel(nqs)]
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
-                %Calculate mean across posterior distribution
-                means(:,isim,inq,ifolder) = textread(filename,'%f');
-            end
-        end
-    end
-end   
-
-%Median and credible sets across datasets (dim 2)
-p50 = squeeze(quantile(means,0.5,2));
-p05 = squeeze(quantile(means,0.05,2));
-p95 = squeeze(quantile(means,0.95,2));
[…]

### 2019-03-08 src/general/tables/table_param_linkfme0_stickyw.m

@@ -1,147 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_param_linkfme0_stickyw.tex';
-
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-linear/me0/','linear','kf','me0','Linear, Kalman Filter, ME 0$\%$';...
-    '../../Estimation-linear-stickyw/me0/','linear','kf','me0','Linear, Kalman Filter, ME 0$\%$, Sticky Wages';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = 1:numel(nqs)
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
-                %Calculate mean across posterior distribution
-                means(:,isim,inq,ifolder) = textread(filename,'%f');
-            end
-        end
-    end
-end   
-
-%Median and credible sets across datasets (dim 2)
-p50 = squeeze(quantile(means,0.5,2));
-p05 = squeeze(quantile(means,0.05,2));
-p95 = squeeze(quantile(means,0.95,2));
-%RMSE across datasets (dim 2), ignore nans
[…]

### 2019-03-08 src/general/tables/table_param_linkfme5_stickyw.m

@@ -1,147 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_param_linkfme5_stickyw.tex';
-
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-linear/me5/','linear','kf','me0','Linear, Kalman Filter, ME 5$\%$';...
-    '../../Estimation-linear-stickyw/me5/','linear','kf','me0','Linear, Kalman Filter, ME 5$\%$, Sticky Wages';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = 1:numel(nqs)
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
-                %Calculate mean across posterior distribution
-                means(:,isim,inq,ifolder) = textread(filename,'%f');
-            end
-        end
-    end
-end   
-
-%Median and credible sets across datasets (dim 2)
-p50 = squeeze(quantile(means,0.5,2));
-p05 = squeeze(quantile(means,0.05,2));
-p95 = squeeze(quantile(means,0.95,2));
-%RMSE across datasets (dim 2), ignore nans
[…]

### 2019-03-08 src/general/tables/table_param_linme5_pfme5.m

@@ -1,146 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_param_linme5_pfme5.tex';
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-linear/me5/','linear','kf','me5','Level Linear, Kalman Filter, ME 5$\%$';...
-    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$';         
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = 1:numel(nqs)
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
-                %Calculate mean across posterior distribution
-                means(:,isim,inq,ifolder) = textread(filename,'%f');
-            end
-        end
-    end
-end   
-
-%Median and credible sets across datasets (dim 2)
-p50 = squeeze(quantile(means,0.5,2));
-p05 = squeeze(quantile(means,0.05,2));
-p95 = squeeze(quantile(means,0.95,2));
-%RMSE across datasets (dim 2), ignore nans
[…]

### 2019-03-08 src/general/tables/table_param_me5nm_pwnm.m

@@ -1,151 +1,0 @@
-%  This file creates a table with the median, credible sets and RMSE of
-%  mean posterior estimates for different ZLB bins and specifications.
-
-clear
-clc
-close all
-
-savename = 'table_param_me5nm_pwnm.tex';
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    %'../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    %'../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$';...
-    '../../Estimation-global-nomiss/me5/','global','pf','me5','No misspecification, Global, Particle Filter, ME 5$\%$';    
-    '../../Estimation-pwlinear-nomiss/','pwlinear','if','me0','No misspecification, Piecewise Linear, Inversion Filter, ME 0$\%$';...
-    %'../../Estimation-linear-nomiss/me0/','linear','kf','me0','No misspecification, Level Linear, Kalman Filter, ME 0$\%$';...
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-means = nan(F.nparam,nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    for inq = 1:numel(nqs)
-        % ZLB duration
-        nq = nqs(inq);
-        disp(['ZLB duration = ' num2str(nq)])
-        for isim = 1:nsims
-            %Load posterior distributions they exist, otherwise keep as
-            %NaNs
-            filename = [specs{ifolder,1},'zlb',num2str(inq),'/mean/',num2str(isim),'-postmean.txt'];
-            if exist(filename, 'file') == 2
[…]

### 2019-03-08 src/general/tables/table_speeds.m

@@ -1,104 +1,0 @@
-%  This file creates a table with the median, credible sets of estimation speed.
-
-clear
-clc
-close all
-
-savename = 'table_speeds.tex';
-%Specifications to include: path, method, filter, measurement error, table
-%label
-specs = {...
-    '../../Estimation-linear/me0/','linear','kf','me0','Level Linear, Kalman Filter, ME 0$\%$ (1 core)';...
-    '../../Estimation-pwlinear/','pwlinear','if','me0','Piecewise Linear, Inversion Filter, ME 0$\%$ (1 core)';...
-    '../../Estimation-global/me5/','global','pf','me5','Global, Particle Filter, ME 5$\%$ (16 cores)';         
-    };
-
-npers = 120;
-nsimsall = 100;
-nsims = 50;
-nZLBpers = 6;
-nqs = [0,6,12,18,24,30];
-nspecs = size(specs,1);
-ndraws = 1000;
-
-%Load in V from misspecified model
-load('../../Results-nocap/options.mat','V','P','F')
-
-speed = nan(nsims,nZLBpers,nspecs);
-
-%Loop through specifications
-for ifolder = 1:size(specs,1)
-    disp(['Specification: ' specs{ifolder,1}])
-    % Loop through ZLB durations
-    filename = [specs{ifolder,1},'states/speed.txt'];
-    speed(:,:,ifolder) = reshape(textread(filename,'%f'),[nsims,nZLBpers]);
-end   
-s = speed;
-h = s*80000/(60^2);
-%Median and credible sets across datasets (dim 2)
-s_m = squeeze(mean(s,1));
-s_p05 = squeeze(quantile(s,0.05,1));
-s_p95 = squeeze(quantile(s,0.95,1));
-h_m = squeeze(mean(h,1));
-h_p05 = squeeze(quantile(h,0.05,1));
-h_p95 = squeeze(quantile(h,0.95,1));
-
-%number format (# of decimals) for parameter estimates and true value
-nformat = {'%.3f','%.3f','%.1f'};
-
-%Header of table
-Tc = cell(5,7);
-Tc{1,1} = '\begin{table}[!htb]\footnotesize';
[…]

### 2019-03-31 Paper/Paper.tex
Add paper through solution times

\documentclass[12pt, final]{article}
\usepackage{color}
\usepackage{times}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{comment}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage[paperwidth=8.5in,left=1.0in,right=1.0in,top=1.0in,bottom=1.0in,paperheight=11.0in]{geometry}
\usepackage[labelsep=colon,singlelinecheck=false,footnotesize]{caption}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{booktabs}
\usepackage[sort&compress]{natbib}
\usepackage{subfig}
\usepackage{titlesec}
\usepackage[breaklinks]{hyperref}
\hypersetup{pdfdisplaydoctitle=true,bookmarksnumbered=true,colorlinks=true,citecolor=black,linkcolor=darkblue,urlcolor=darkred,pdfstartview=FitH,pdfpagemode=UseNone}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{accents}
\newcommand{\ubar}[1]{\underaccent{\bar}{#1}}

%Define Color Names
\definecolor{Gray}{rgb}{0.65,0.65,0.65}
\definecolor{darkblue}{rgb}{0,0,0.55}
\definecolor{darkred}{rgb}{0.5,0,0}

%Section Headings
\newcommand\Bheadfont{\fontsize{14pt}{\baselineskip}\selectfont}
\titleformat{\section}[hang]{\normalfont\sc\color{darkblue}\Bheadfont}{\thesection\hskip0.618em}{0em}{}
\titlespacing*{\section}{0pt}{15pt plus 2pt minus 2pt}{9pt plus 2pt minus 2pt}
\titleformat{\subsection}[runin]{\normalfont\sc\color{darkblue}} {\thesubsection\hskip0.618em}{0em}{}
\titlespacing*{\subsection}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
\titleformat{\subsubsection}[runin]{\normalfont\sc\color{darkblue}} {\thesubsubsection\hskip0.618em}{0em}{}
\titlespacing*{\subsubsection}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
\titleformat{\paragraph}[runin]{\bfseries}{\theparagraph\hskip0.618em}{0em}{}
\titlespacing*{\paragraph}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}

\begin{document}

\section{Model}
\subsection{Firms} The production sector consists of a continuum of monopolistically competitive intermediate goods firms and a final goods firm. Intermediate firm $f \in [0,1]$ produces a differentiated good, $y(f)$, according to $y_t(f) = (k_{t-1}(f))^\alpha(z_tn_t(f))^{1-\alpha}$, where $n(f)$ is the labor hired by firm $f$ and $k(f)$ is the capital rented by firm $f$. $z_t = g_tz_{t-1}$ is technology, which is common across firms. Deviations from the steady-state growth rate, $\bar{g}$, follow
\begin{gather}
  \label{eq:1}
  g_t = \bar{g} + \sigma_g\varepsilon_{g,t},\; \varepsilon_g \sim \mathds{N}(0,1). 
\end{gather}

The final goods firm purchases output from each intermediate firm to produce the final good, $y_t \equiv [\int_{0}^1 y_t(f)^{(\theta-1)/\theta}df]^{\theta/(\theta-1)}$, where $\theta > 1$ is the elasticity of substitution. Dividend maximization determines the demand for intermediate good $f$, $y_t(f) = (p_t(f)/p_t)^{-\theta}y_t$, where $p_t = [\int_{0}^{1} p_t(f)^{1-\theta}df]^{1/(1-\theta)}$ is the price level. Following Rotemberg (1982), intermediate firms pay a price adjustment cost, $adj_t^p(f) \equiv \varphi(p_t(f)/(\bar{\pi}p_{t-1}(f))-1)^2)y_t/2$, where $\varphi > 0$ scales the cost and $\bar{\pi}$ is the steady-state gross inflation rate. Given this cost, firm $f$ chooses $n_t(f)$, $k_{t-1}(f)$, and $p_t(f)$ to maximize the expected discounted present value of future dividends, $E_t\sum_{k=t}^\infty q_{t,k}d_k(f)$, subject to its production function and the demand for its product, where $q_{t,t} \equiv 1$, $q_{t,t+1} \equiv \beta(\lambda_t/\lambda_{t+1})$ is the pricing kernel between periods $t$ and $t+1$, $q_{t,k} \equiv \prod_{j=t+1}^{k>t} q_{j-1,j}$, and $d_t(f) = p_t(f)y_t(f)/p_t - w_tn_t(f) - adj_t^p(f)$. In symmetric equilibrium, the optimality conditions reduce to
\begin{gather}
  y_t = (k_{t-1})^\alpha(z_tn_t)^{1-\alpha},\\
  w_t = (1-\alpha)mc_ty_t/n_t,\\
  r_t^k = \alpha mc_t y_t/k_{t-1},\\
  \varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)],
\end{gather}
where $\pi^{gap}_t = \pi_t/\bar{\pi}_t$ and $\pi_t = p_t/p_{t-1}$ is the gross inflation rate. If $\varphi = 0$, the real marginal cost of producing a unit of output ($mc_t$) equals $(\theta-1)/\theta$, which is the inverse of the markup of price over marginal cost.
\subsection{Households} The households choose $\{c_t, n_t, b_t, x_t, k_t\}_{t=0}^\infty$ to maximize expected lifetime utility given by $E_0\sum_{t=0}^\infty\beta[\log(c_t-hc^a_{t-1}) - \chi n_t^{1+\eta}/(1+\eta)]$, where $\beta$ is the discount factor, $\chi > 0$ determines steady-state labor, $1/\eta$ is the Frisch elasticity of labor supply, $c$ is consumption, $c^a$ is aggregate consumption, $h$ is the degree of external habit persistence, $b$ is the real value of a privately-issued 1-period nominal bond, $x$ is investment, and $E_0$ is an expectation operator conditional on information available in period 0. The household's budget constraint is given by
\begin{gather*}
    c_t+x_t+b_t/(i_ts_t)=w_tn_t+r_t^kk_{t-1}+b_{t-1}/\pi_t+d_t
  \end{gather*}
where $i$ is the gross nominal interest rate, $r^k$ is the capital rental rate, and $d$ is a real dividend from ownership of intermediate firms. The nominal bond, $b$ is subject to a risk premium, $s$, that follows
\begin{gather}
  \label{eq:6}
  s_t = (1-\rho_s)\bar{s} + \rho_ss_{t-1} + \sigma_s\varepsilon_{s,t},\; 0 \leq \rho_s < 1,\; \varepsilon_s \sim \mathds{N}(0,1),
\end{gather}
where $\bar{s}$ is the steady-state value. An increase in $s_t$ boosts saving, which lowers period-$t$ demand.

Households also face an investment adjustment cost, so the law of motion for capital is given by
\begin{gather}
  k_t = (1-\delta)k_{t-1} + x_t(1-\nu(x^g_t - 1)^2/2),\; 0 \leq \delta \leq 1,
  \end{gather}
where $x_t^g = x_t/(\bar{g}x_{t-1})$ is investment growth relative to its steady-state and $\nu \geq 0$ scales the cost.

The first order conditions to each household's constrained optimization problem are given by
\begin{gather}
  \lambda_t = c_t - hc^a_{t-1}, \\
  w_t = \chi n_t^\eta \lambda_t,\\
  1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}))],\\
  q_t = \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})],\\
  1 = q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] + \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)],\\
  \varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)],
\end{gather}
where $1/\lambda$ is the marginal utility of consumption and $q$ is Tobin's q.\\

\noindent
\textbf{Monetary Policy} The central bank sets the gross nominal interest rate, $i$, according to
\begin{gather}
    \label{eq:15}
    i_t=\max\{1,i_t^n\}\\
      \label{eq:16}
  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{g}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}), 0 \leq \rho_i < 1, \varepsilon_i \sim \mathds{N}(0,1),
  \end{gather}
where $y^{gdp}$ is real GDP (i.e., output, $y$, minus the resources lost due to adjustment costs, $adj^p$), $i^n$ is the gross notional interest rate, $\bar i$ and $\bar{\pi}$ are the target values of the inflation and nominal interest rates, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps. A more negative net notional rate indicates that the central bank is more constrained.\\

\noindent
\textbf{Competitive Equilibrium} The aggregate resource constraint and real GDP definition are given by
\begin{gather}
  c_t + x_t = y_t^{gdp}\\
  y_t^{gdp} = [1 - \varphi(\pi_t^{gap}-1)^2/2]y_t
\end{gather}
The model does not have a steady-state due to the unit root in technology, $z_t$. Therefore, we define the variables with a trend in terms of technology (i.e., $\tilde{x}_t \equiv x_t/z_t$). The detrended equilibrium system is provided in \hyperlink{Appendix A}{Appendix A}. A competitive equilibrium consists of sequences of quantities, $\{\tilde{c}_t, \tilde{y}_t, \tilde{y}_t^{gdp}, x^g_t, y^g_t, n_t, \tilde{k}_t, \tilde{x}_t\}_{t=0}^\infty$, prices, $\{\tilde{w}_t, i_t, i^n_t, \pi_t, \tilde{\lambda}_t, q_t, r^k_t, mc_t\}_{t=0}^\infty$, and exogenous variables, $\{s_t,g_t\}_{t=0}^\infty$, that satisfy the detrended equilibrium system, given the initial conditions, $\{\tilde{c}_{-1}, i^n_{-1}, \tilde{k}_{-1}, \tilde{x}_{-1}, \tilde{w}_{-1}, s_0, g_0, \varepsilon_{i,0}\}$, and three sequences of shocks, $\{\varepsilon_{g,t}, \varepsilon_{s,t}, \varepsilon_{i,t}\}_{t=1}^\infty$.

\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the true model parameters. The parameters were chosen so our data generating process is characteristic of U.S. data. The steady-state growth rate ($\bar{g}$), inflation rate ($\bar{\pi}$), risk-premium ($\bar{s}$), and capital share of income ($\alpha$) are equal to the time averages of per capital real GDP growth, the percent change in the GDP implicit price deflator, the Baa corporate bond yield relative to the yield on the 10-Year Treasury, and the Fernald (2012) utilization-adjusted quarterly-TFP estimates of the capital share of income from 1988Q1-2017Q4.

The subjective discount factor, $\beta$, is set to $0.9949$, which is the time average of the values implied by the steady-state consumption Euler equation and the federal funds rate. The corresponding annualized steady-state nominal interest rate is $3.3\%$ which is consistent with the sample average and current long-run estimates of the federal funds rate. The leisure preference parameter, $\chi$, is set to steady-state labor equals $1/3$ of the available time. The elasticities of substitution between intermediate goods $\theta$, is set to $6$, which corresponds to a $20\%$ average markup and match the values used in Gust et al. (2017). The Frisch elasticity of labor supply, $1/\eta$, is set to $3$ to match the macro estimate in Peterman (2016). The remainin parameters are set to round numbers that are in line with the posterior estimates from similar models in the literature.

\begin{table}
  \hypertarget{Table 1}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c l c c}
    \hline
  Subjective Discount Factor & $\beta$ & $0.9949$ & Rotemberg Price Adjustment Cost & $\varphi$ & $100$ \\
   Frisch Labor Supply Elasticity & $1/\eta$ & $3$ & Inflation Gap Response & $\phi_\pi$ & $2.0$ \\
  Price Elasticity of Substitution & $\theta$ & $6$ & Output Growth Gap Response & $\phi_y$ & $0.5$ \\
  Steady-State Labor Hours & $\bar{n}$ & $1/3$ & Habit Persistence & $h$ & $0.80$ \\
  Steady-State Risk Premium & $\bar{s}$ & $1.0058$ & Risk Premium Persistence & $\rho_s$ & $0.80$ \\
  Steady-State Growth Rate & $\bar{g}$ & $1.0034$ & Notional Rate Persistence & $\rho_i$ & $0.80$ \\
  Steady-State Inflation Rate & $\bar{\pi}$ & $1.0053$ & Technology Growth Shock SD & $\sigma_g$ & $0.005$ \\
  Capital Share of Income & $\alpha$ & $0.35$ & Risk Premium Shock SD & $\sigma_s$ & $0.005$ \\
  Capital Depreciation Rate & $\delta$ & $0.025$ & Notional Interest Rate Shock SD & $\sigma_i$ & $0.0035$ \\
  Investment Adjustment Cost & $\nu$ & $4$ & & &\\
  \hline
  \end{tabular}
  \caption{Parameter values}
  \label{Tab:1}
\end{table}

\section{Solution Methods}
\subsection{Richter et al. (2014)}
We consider the solution methods of Richter et al. (2014) and Gust et al. (2017). The Richter et al. (2014) solution method is policy function iteration with time iteration and linear interpolation, which is based on the theoretical work on monotone operators in Coleman (1991). We discretize the endogenous state variables and approximate the exogenous states $s_t$, $g_t$, and $\varepsilon_{i,t}$ using the N-state Markov chain in Rouwenhorst (1995). We use the Rowenhorst method so that we only have to interpolate along the dimensions of the endogenous state variables, allowing the solution to be faster and more accurate than quadrature methods. To obtain initial conjectures for the nonlinear policy functions, we solve the level-linear version of our model with Sims's (2002) gensys algorithm. Next, we update the policy functions on each node using a fixed point iteration scheme and compute the maximum distance between the updated policy functions and the inital conjectures. Finally, we replace the initial conjectures with the updated policy functions and iterate until the maximum distance is below the tolerance level. \hyperlink{Appendix B}{Appendix B} provides a more detailed discussion of the solution method. %PLEASE REWRITE THIS SO YOU ARE NOT COPYING
%Add Gust et al solution method
\subsection{Gust et al. (2017)}
The Gust et al. (2017) solution method similarly uses time iteration on a fixed point solution with linear interpolations. Following this solution method, instead of directly computing the policy functions, we estimate smoother functions at and away from the ZLB following Gust, L{\o g}pez-Salido, and Smith (2012) which builds on Christiano and Fisher (2000). Since the policy functions depend directly on the nominal interetst rate, they have a kink or non-differentiability associated with the ZLB.  On the other hand, the regime-indexed policy functions do not depend on the current indicator function and are thus more likely to be smooth. The smoother functions are approximated by specifying:
\begin{gather}
  \textbf{pf}_t(d) = \textbf{pf}_{t,1}(d)\mathds{I}_t(d) + \textbf{pf}_{t,2}(d)(1-\mathds{I}_t(d))
\end{gather}
where $\mathds{I}_t(d)$ is defined by
\begin{gather}
  \mathds{I}_t(d) = 
\begin{cases}
     1 &\text{ if } i_t > 1\\
     0 &\text{ otherwise}
\end{cases}
\end{gather}
The variable $i_t=\max\{1,i_t^n\}$ represents the value of the notional rate derived from evaluating the functions $\textbf{pf}_{t,j}(d)$ for $j \in \{1,2\}$ and using equation (\ref{eq:16}). (For each variable, $j=1$ denotes the function associated with the regime with a positive nominal rate and $j=2$ denotes the function associated with the ZLB regime.) %In calculating the fixed point, we use $i=1$ when the model is in the ZLB regime. 
The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for and $l \in \{1,2,3,4\}$ which correspond to the household FOC bond, FOC capital, FOC investment, and the price Phillips curve, respectively, and $j = 1,2$.
\begin{gather}
  R_{t,1,1} = 1 - s_ti_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))]\\
  R_{t,1,2} = 1 - s_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))]\\
  R_{t,2,j} = q_t - \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})]\\
  R_{t,3,j} = 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] - \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)]\\
  R_{t,4,j} = \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t - \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]
  \end{gather}

  \subsection{Euler Equation Errors}
Richter et al. (2014) use Euler equation errors to measure the accuracy of their solutions. To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method to allow exogenous variables to be off the grid. The Euler equation errors are reported in absolute value of the errors in base 10 logarithms. A consumption Euler equation error of -3 means the household makes an error equal to one out of every 1,000 consumption goods.

\section{Results}

\subsection{Solution Times}
\hyperlink{Table 2}{Table 2} reports the solution times for the Richter et al. (2013) and Gust et al. (2017) solution methods for the models with and without capital. %Say something about the solution times% %Say something about the machine the solution times were computed on

\begin{table}[H]
  \centering
  \hypertarget{Table 2}
  \small
    \setlength{\tabcolsep}{10pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Iterations & Total Time & Iterations & Total time\\
    \hline
  Richter et al. (2013) & 67 & 17.9s & 65 & 0h 15m 37.1s\\    
  Gust et al. (2017) & 66 & 46s & 1170 &  5h 32m 48.6s\\
  \hline
\end{tabular}
  \caption{Solution times}
  \label{Tab:2}
\end{table}

\subsection{Policy Functions}

\subsection{Euler Equation Errors}

\appendix
  \section{Detrended Equilibrium System} \hypertarget{Appendix A}
  \noindent
  \textbf{Medium-Scale Model} The detrended system includes (\ref{eq:1}),(\ref{eq:6}),(\ref{eq:15}),(\ref{eq:16}) and 
\begin{gather}
\tilde{y}_t= (\tilde{k}_{t-1}/g_t)^\alpha n_t^{1-\alpha},\\
r^k_t = \alpha mc_t g_t \tilde{y}_t/\tilde{k}_{t-1},\\
\tilde{w}_t = (1-\alpha)mc_t\tilde{y}_t/n_t,\\
\tilde{y}^{gdp}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t,\\
y^g_t = g_t\tilde{y}^{gdp}_t/(\bar{g}\tilde{y}^{gdp}_{t-1}),\\
\tilde{\lambda}_t = \tilde{c}_t\ - h\tilde{c}_{t-1}/g_t,\\
\label{eq:m1}
\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t,\\
\tilde{c}_t + \tilde{x}_t = \tilde{y}^{gdp}_t,\\
x^g_t = g_t\tilde{x}_t/(\bar{g}\tilde{x}_{t-1}),\\
\tilde{k}_t = (1-\delta)(\tilde{k}_{t-1}/g_t) + \tilde{x}_t(1-\nu(x^g_t-1)^2/2),\\%%%
\label{eq:m2}
  1 = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))],\\
q_t = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(r^k_{t+1} + (1-\delta)q_{t+1})/g_{t+1}],\\
1 = q_t[1 - \nu(x^g_t-1)^2/2 - \nu(x^g_t-1)x^g_t] + \nu\beta\bar{g}E_t[q_{t+1}(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)/g_{t+1}],\\
\label{eq:m3}
  \varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1}) (\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(\tilde{y}_{t+1}/\tilde{y}_t)].
\end{gather}
The variables are $\tilde{c},\tilde{n},\tilde{x},\tilde{k},\tilde{y^{gdp}},\tilde{y},x^g,y^g,\tilde{w},r^k,\pi,i,i^n,q,mc,\tilde{\lambda},g,$ and $s$.\\

\noindent \textbf{Small-Scale Model} The detrended system includes (\ref{eq:1}),(\ref{eq:6}),(\ref{eq:15}),(\ref{eq:16})(\ref{eq:m1}),(\ref{eq:m2}),(\ref{eq:m3}), and 
\begin{gather}
\tilde{\lambda}_t = \tilde{c}_t,\\ %%%
\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t,\\ %%%
  \tilde{y}_t= n_t.  %%% 
\end{gather}
The variables are $\tilde{c},i^n,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{y},n,g,$ and $s$.\\

\section{Nonlinear Solution Method}\hypertarget{Appendix B}
We begin by compactly writing the detrended nonlinear system as
\begin{gather*}
  E[f(\textbf{s}_{t+1},\textbf{s}_t,\varepsilon_{t+1})|\textbf{z}_t,\vartheta] = 0,
\end{gather*}
where $f$ is a vector-valued function, $\textbf{s}_t$ is a vector of variables, $\varepsilon_t \equiv [\varepsilon_{s,t}, \varepsilon_{g,t},\varepsilon_{i,t}]'$ is a vector of shocks, $\textbf{z}_t$ is a vector of states ($\textbf{z}_t \equiv [\tilde{c}_{-1}, i^n_{t-1},\tilde{k}_{t-1},\tilde{x}_{t-1},s_t,g_t,\varepsilon_{i,t}]'$ for the model with capital and $\textbf{z}_t \equiv [\tilde{c}_{t-1},i^n_{t-1},s_t,g_t,\varepsilon_{i,t}]'$ for the model without capital), and $\vartheta$ is a vector of parameters.

We use the Markov chain method in Rouwenhorst (1995) to discretize the endogenous state variables, $s_t$, $g_t$, and $\varepsilon_{i,t}$. Kopecky and Suen (2010) show the Rouwenhorst method outperforms other methods for approximating autoregressive processes. The bounds on $\tilde{c}_{t-1}, i^n_{t-1}, \tilde{k}_{t-1},$ and $\tilde{x}_{t-1}$ are set to $\pm 2.5\%, \pm 6\%, \pm 8\%, \pm 15\%$, respectively. Richter and Throckmorton chose these bounds so the grids contain 99.9\% of the simulated values for each state variable and during ZLB duration. We discretize the states into 5 evenly-spaced points for the model with capital and 7 evenly-spaced points for the model without capital. The product of the points in each dimension, D, represents the total nodes in the state space ($D = 78125$ for the model with capital and $D = 2401$ for the model without capital). The realization of $\textbf{z}_t$ on node $d$ is denoted $\textbf{z}_t(d)$. The Rouwenhorst method provides integration nodes, $[s_{t+1}(m), g_{t+1}(m), \varepsilon_{i,t+1}(m)]$, with weights, $\phi(m)$, for $m \in \{1, \dots, M\}$. Since the exogenous variables evolve according to a Markov chain, the number of future realizations is the same as the state variables.

The vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$ ($\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), n_t(\textbf{z}_t), q_t(\textbf{z}_t), mc_t(\textbf{z}_t)]$ for the model with capital and $\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), \tilde{c}_t(\textbf{z}_t)]$. Our choice of policy functions is not unique, but it helps solving for the other variables in the nonlinear system of equations given $\textbf{z}_t$.

The following steps outline our global policy function iteration algorithm:

\begin{enumerate}
  \item Use Sims's (2002) \texttt{gensys} algorithm to solve the level-linear model without the ZLB constraint. Then map the solution to the discretized state space to initialize the policy functions. 
  \item On each node $d \in \{1,\dots,D\}$, use fixed point iteration to find $\textbf{pf}_t(d)$ to satisfy $E[f(\cdot)|\textbf{z}_t(d), \vartheta] \approx 0$. Guess $\textbf{pf}_t(d) = \textbf{pf}_{j-1}(d)$ Then apply the following: 
    \begin{enumerate}
    \item Solve for all variables dated at time $t$, given $\textbf{pf}_t(d)$ and $\textbf{z}_t(d)$.
    \item Linearly interpolate the policy functions $\textbf{pf}_{j-1}$, at the updated state variables $\textbf{z}_{t+1}(m)$, to obtain $\textbf{pf}_{t+1}(m)$ on every integration node, $m \in \{1,\dots,M\}$.
    \item Given $\{\textbf{pf}_{t+1}(m)\}_{m=1}^M$, solve for the other elements of $\textbf{s}_{t+1}(m)$ and compute%and back out the updated \textbf{pf}$_t(d)$.
      \begin{gather*}
        E[f(\textbf{s}_{t+1},\textbf{s}_t(d),\varepsilon_{t+1})|\textbf{z}_t(d),\vartheta] \approx \sum_{m=1}^M \phi(m)f(\textbf{s}_{t+1}(m),\textbf{s}_t(d),\varepsilon_{t+1}(m)).
      \end{gather*}
      \item Back out $\textbf{pf}_t(d)$ from the expectation operators and updated state.
    \end{enumerate}
       \item Repeat step 2 until $\text{maxdist}_j < 10^{-6}$, where $\text{maxdist}_j \equiv \text{max}\{|\textbf{pf}_j - \textbf{pf}_{j-1}|\}$. When that criterion is satisfied, the algorithm has converged to an approximate nonlinear solution.
\end{enumerate}

\begin{comment}
\subsection{ART Model with capital}
\noindent Preferences:
\begin{gather*}
  E_0\textstyle\sum_{t=0}^\infty\beta^t [\log(c_t-hc^a_{t-1})-\chi n_t^{1+\eta}/(1+\eta)]
\end{gather*}

\noindent Budget Constraint:
\begin{gather*}
  c_t+x_t+b_t/(i_ts_t)=w_tn_t+r_t^kk_{t-1}+b_{t-1}/\pi_t+d_t\\
  k_t = (1-\delta)k_{t-1} + x_t(1 - \nu(x^g_t-1)^2/2)
\end{gather*}

\setcounter{equation}{0}
\noindent Equilibrium system:
\small\begin{gather}
y_t = k_{t-1}^\alpha(z_t n_t)^{1-\alpha}\\ %%%
r_t^k = \alpha mc_ty_t/k_{t-1}\\
w_t = (1-\alpha)mc_ty_t/n_t\\
%w_t^g = \pi_tw_t(\bar{\pi}gw_{t-1})\\
y_t^{gdp} = [1 - \varphi(\pi_t^{gap}-1)^2/2]y_t \\
y^g_t = y^{gdp}_t/(\bar{g}y^{gdp}_{t-1})\\
i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{g}_{t})^{\phi_y})^{1-\rho_i}\exp(mp_t)\\
i_t=\max\{1,i_t^n\}\\
\lambda_t = c_t - hc^a_{t-1} \\
w_t = \chi n_t^\eta \lambda_t\\
c_t + x_t = y_t^{gdp}\\
x_t^g = x_t/(\bar{g}x_{t-1})\\
k_t = (1-\delta)k_{t-1}+x_t(1-\nu(x_t^g-1)^2/2) \\%%%
1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}))]\\
q_t = \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})]\\
1 = q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] + \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)]\\
\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
g_t = \bar{g} + \sigma_g\varepsilon_{g,t}\\
s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_s\varepsilon_{s,t}\\
mp_t = \sigma_i\varepsilon_{i,t}\\
  z_t=g_tz_{t-1}
\end{gather}\normalsize
Variables: $\{c,n,x,k,y^{gdp},y,x^g,y^g,w,r^k,\pi,i,i^n,q,mc,\lambda,g,s,mp,z\}$\\

\setcounter{equation}{0}
\noindent De-trended Equilibrium System:
\small\begin{gather}
\tilde{y}_t= (\tilde{k}_{t-1}/g_t)^\alpha n_t^{1-\alpha}\\
r^k_t = \alpha mc_t g_t \tilde{y}_t/\tilde{k}_{t-1}\\
\tilde{w}_t = (1-\alpha)mc_t\tilde{y}_t/n_t\\
\tilde{y}^{gdp}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
y^g_t = g_t\tilde{y}^{gdp}_t/(\bar{g}\tilde{y}^{gdp}_{t-1})\\
i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi}(y^g_t)^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t})\\
i_t=\max\{1,i_t^n\}\\
\tilde{\lambda}_t = \tilde{c}_t\ - h\tilde{c}_{t-1}/g_t\\
\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
\tilde{c}_t + \tilde{x}_t = \tilde{y}^{gdp}_t\\
x^g_t = g_t\tilde{x}_t/(\bar{g}\tilde{x}_{t-1})\\
\tilde{k}_t = (1-\delta)(\tilde{k}_{t-1}/g_t) + \tilde{x}_t(1-\nu(x^g_t-1)^2/2)\\%%%
  1 = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
q_t = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(r^k_{t+1} + (1-\delta)q_{t+1})/g_{t+1}]\\
1 = q_t[1 - \nu(x^g_t-1)^2/2 - \nu(x^g_t-1)x^g_t] + \nu\beta\bar{g}E_t[q_{t+1}(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)/g_{t+1}]\\
  \varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1}) (\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
  g_t= \bar{g} + \sigma_g\varepsilon_{g,t} \\
  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_s\varepsilon_{s,t}\\
  mp_t = \sigma_i\varepsilon_{i,t}
\end{gather}
Variables:$\{\tilde{c},\tilde{n},\tilde{x},\tilde{k},\tilde{y^{gdp}},\tilde{y},x^g,y^g,\tilde{w},r^k,\pi,i,i^n,q,mc,\tilde{\lambda},g,s,mp\}$\\

\setcounter{equation}{0}
\noindent Log-linear Equilibrium System:
\begin{gather}
  \hat{y}_t/\bar{y} = \alpha(\hat{k}_{t-1}/\bar{k} - \hat{g}_t/\bar{g}) + (1-\alpha)\hat{n}_t/\bar{n}\\
\hat{r}^k_t/\bar{r}^k = \hat{mc}_t/\bar{mc} + \hat{g}_t/\bar{g} + \hat{y}_t/\bar{y} - \hat{k}_{t-1}/\bar{k}\\
\hat{w}_t/\bar{w} = \hat{mc}_t/\bar{mc} + \hat{y}_t/\bar{y} - \hat{n}_t/\bar{n}\\
\hat{y}_t^{gdp} = \hat{y}_t\\
\hat{y}^g_t = \hat{g}_t/\bar{g} + \hat{y}^{gdp}_t/\bar{y}^{gdp} - \hat{y}^{gdp}_{t-1}/\bar{y}^{gdp}\\
  \hat{i}_t/\bar{i} = \rho_i\hat{i}_{t-1}/\bar{i} + (1-\rho_i)(\phi_\pi\hat{\pi}^{gap}_t+ \phi_y\hat{y}^g_t)+\hat{mp}_t \\
  \hat{\imath}_t = \hat{\imath}_t^n\\
  \hat{\lambda}_t = \hat{c}_t - (h/\bar{g})\hat{c}_{t-1} + (h\bar{c}/\bar{g}^2)\hat{g}_t\\
  \hat{c}_t + \hat{x}_t = \hat{y}^{gdp}_t\\
  \hat{x}^g_t = \hat{g}_t/\bar{g} + \hat{x}_t/\bar{x} - \hat{x}_{t-1}/\bar{x}\\
  \hat{k}_t = ((1-\delta)/\bar{g})[\hat{k}_{t-1}-(\bar{k}/\bar{g})\hat{g}_t] + \hat{x}_t\\
  \hat{\lambda}_t/\bar{\lambda} + \hat{\imath}_t/\bar{i} + \hat{s}_t/\bar{s}  = E_t\hat{\lambda}_{t+1}/\bar{\lambda}+E_t\hat{g}_{t+1}/\bar{g}+E_t\hat{\pi}_{t+1}/\bar{\pi} \\
  \hat{q}_t = \hat{\lambda}_t/\bar{\lambda} - E_t\hat{\lambda}_{t+1}/\bar{\lambda} + (\beta/\bar{g})[E_t\hat{r}^k_{t+1} + (1-\delta)E_t\hat{q}_{t+1}] - E_t\hat{g}_{t+1}/\bar{g}\\
  \hat{x}^g_t = \hat{q}_t + \beta E_t\hat{x}^g_{t+1}\\
  \varphi\hat{\pi}^{gap}_t = \theta\hat{mc}_t+\beta\varphi E_t\hat{\pi}^{gap}_{t+1}\\
  \hat{g}_t = \sigma_g\varepsilon_{g,t}\\
  \hat{s}_t = \rho_s\hat{s}_{t-1} + \sigma_s\varepsilon_{s,t}\\
  \hat{mp}_t = \sigma_i\varepsilon_{i,t}
\end{gather}
Variables:$\{\hat{c},\hat{n},\hat{x},\hat{k},\hat{y^{gdp}},\hat{y},\hat{x^g},\hat{y^g},\hat{w},\hat{r^k},\hat{\pi},\hat{i},\hat{i^n},\hat{q},\hat{\lambda},\hat{g},\hat{s},\hat{mp}\}$\\
\begin{comment}
\pagebreak

\subsection{ART Model pre-capital}
\noindent Preferences:
\begin{gather*}
  E_0\textstyle\sum_{t=0}^\infty\beta^t [\log(c_t-hc^a_{t-1})-\chi n_t^{1+\eta}/(1+\eta)]
\end{gather*}

\noindent Budget Constraint:
\begin{gather*}
  c_t+b_t/(i_ts_t)=w_tn_t+b_{t-1}/\pi_t+d_t
\end{gather*}

\setcounter{equation}{0}
\noindent Equilibrium system (11 equations):
\small\begin{gather}
c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(c_t/(\bar{g}c_{t-1}))^{\phi_c})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
i_t=\max\{1,i_t^n\}\\
\lambda_t = c_t - hc^a_{t-1} \\
w_t = \chi n_t^\eta \lambda_t\\
1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}))]\\
\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
  y_t=z_t n_t\\  
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
  s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t\\
  z_t=g_tz_{t-1}
\end{gather}\normalsize
Variables: $\{c,i^n,i,\lambda,w,\pi^{gap},y,n,g,s,z\}$\\

\setcounter{equation}{0}
\noindent De-trended Equilibrium System (10 equations):
\small\begin{gather}
\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi}(g_t\tilde{c}_t/(\bar{g}\tilde{c}_{t-1})^{\phi_c})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
i_t=\max\{1,i_t^n\}\\
\tilde{\lambda}_t = \tilde{c}_t\ - h\tilde{c}_{t-1}/g_t\\
\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
  1 = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
  \varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1-\theta + \theta\tilde{w}_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1}) (\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
  \tilde{y}_t= n_t\\  
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t
\end{gather}
Variables: $\{\tilde{c},i^n,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{y},n,k,g,s\}$\\

\setcounter{equation}{0}
\noindent Log-linear Equilibrium System:
\begin{gather}
  \hat{c}_t = \hat{y}_t\\
  \hat{\imath}_t^n = \rho_i\hat{\imath}^n_{t-1} + (1-\rho_i)\phi_\pi\hat{\pi}_t+ (1-\rho_i)\phi_c(\hat{g}+\hat{c}-\hat{c}_{t-1})+\sigma_\nu\nu_t \\
  \hat{\imath}_t = \hat{\imath}_t^n\\
  (1-h/g)\hat{\lambda}_t = \hat{c}_t + (h/g)(\hat{g} - \hat{c}_{t-1})\\
  \hat{w}_t =  \eta\hat{n}_t + \hat{\lambda}_t\\
  \hat{\lambda}_t + \hat{\imath}_t + s_t  = E_t\hat{\lambda}_{t+1}+E_t\hat{\pi}_{t+1} \\
  \varphi\hat{\pi}_t = (\theta-1)\hat{w}_t+\beta\varphi E_t\hat{\pi}_{t+1}\\
  \hat{y}_t = \hat{n}_t 
\end{gather}
\pagebreak
\setcounter{equation}{0}
\subsection{Gust Et Al Model}
\noindent Equilibrium system (13 equations):
\small\begin{gather}
\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
i_t=\max\{1,i_t^n\}\\
1/\lambda_t =  \beta E_t[(1/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
\lambda_t = c_t \\
c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
w_t = \chi n_t^\eta \lambda_t\\
  y_t=z_t n_t\\  
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
  s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t\\
  z_t=g_tz_{t-1}
\end{gather}\normalsize
Variables: $\{c,i^n,i,\lambda,w,\pi^{gap},V_{\lambda},y,V_{\pi},n,g,s,z\}$\\

\setcounter{equation}{0}
\noindent De-trended Equilibrium System (12 equations):
\small\begin{gather}
\varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1 - \theta + \theta\tilde{w}_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(\pi^{gap}_{t+1}-1)\pi^{gap}_{t+1}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
i_t=\max\{1,i_t^n\}\\
1/\tilde{\lambda}_t = \beta E_t[(1/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi^{gap}_{t+1}g_{t+1}))]\\%
\tilde{\lambda}_t = \tilde{c}_t\\
\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
  \tilde{y}_t= n_t\\  
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t
\end{gather}
Variables: $\{\tilde{c},i^n,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{V}_{\lambda},\tilde{y},\tilde{V}_{\pi},n,g,s\}$\\

\setcounter{equation}{0}
\noindent Log-linear Equilibrium System:
\begin{gather}
  \varphi\hat{\pi}_t = (\theta-1)\hat{w}_t+\beta\varphi E_t\hat{\pi}_{t+1}\\
  \hat{\imath}_t^n = \rho_i\hat{\imath}^n_{t-1} + (1-\rho_i)\phi_\pi\hat{\pi}_t+\sigma_\nu\nu_t \\
  \hat{\imath}_t = \hat{\imath}_t^n\\
    -\hat{\lambda}_t = \hat{\imath}_t + s_t - E_t\hat{\lambda}_{t+1} - E_t\hat{\pi}_{t+1} \\
  \hat{\lambda}_t = \hat{c}_t \\
  \hat{c}_t = \hat{y}_t\\
  \hat{w}_t =  \eta\hat{n}_t + \hat{\lambda}_t\\
  \hat{y}_t = \hat{n}_t
\end{gather}

\setcounter{equation}{0}
\noindent Gust et al Indicator Functions\\
\begin{gather}
  c_{t+1,1} = \beta E_t[\lambda_t(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
  c_{t+1,2} = \beta E_t[\lambda_t(s_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\  
\end{gather}
for $k=1,2$ where $k=1$ corresponds to the non-ZLB regime and $k=2$ corresponds to the ZLB regime.
\begin{gather}
c_{t} = c_{t,1}I + c_{t,2}(1-I) 
\end{gather}
for $j=1,2$ and where $I$ is defined by:
$$
\begin{cases}
  I = 1 & \text{ if } i > 1\\
  I = 0 & \text{ otherwise.}
\end{cases}
$$
%We use the functions, $V_l$, to determine the decisions rule though we do not approximate $V_l$ directly, because they inherit a kink associated with the ZLB constraint. Instead, we approximate functions, $V_{l,i}$, that are smoother and easier to approximate by specifying:
%\begin{gather}
%V_l = V_{l,1}I + V_{l,2}(1-I) 
%\end{gather}
%for $l \in \{\lambda, \pi\}$ and $j=1,2$ and where $I$ is defined by:
%\begin{gather}
%  I = 1 \text{ if } i > 1\\
%  \text{  } = 0 \text{ otherwise}
%\end{gather}
%In the above, $i = \max(1,i^n)$ where $i^n$ denotes the value of the notional rate derived from evaluating the functions $V_{l,1}$ and using (2). (For each variable, we use $j=1$ to denote the function associated with the regime with a positive nominal interest rate and $j=2$ to denote the function associated with the ZLB regime. \\
%Because the functions, $V_l$ depend directly on the nominal interest rate, we expect then to have a kink or non-differentiability. By contrast, the counterpart functions, $V_{l,j}$, that are indexed by the interest-rate regime do not depend on the current indicator function and thus are more likely to be smooth. \\
%Specifically, $V_{\pi,1}$ and $V_{\pi,2}$ are both described by (8) because the nominal interest rate does not appear in that equation. $V_{\lambda,1}$ is described by (6), but for the ZLB regime:
%\begin{gather}
%V_{\lambda,t,2} =  \beta E_t[(1/\lambda_{t+1})(s_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\  
%\end{gather}
%where $i_t$ is replaced by 1.
\end{comment}
\end{document}

\documentclass[12pt, final]{article}
\usepackage{color}
\usepackage{times}
\usepackage{amssymb,amsmath,amsthm}
\usepackage{dsfont}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{enumitem}
\usepackage[paperwidth=8.5in,left=1.0in,right=1.0in,top=1.0in,bottom=1.0in,paperheight=11.0in]{geometry}
\usepackage[labelsep=colon,singlelinecheck=false,footnotesize]{caption}
\usepackage{fancyhdr}
\usepackage{float}
\usepackage{booktabs}
\usepackage[sort&compress]{natbib}
\usepackage{subfig}
\usepackage{titlesec}
\usepackage[breaklinks]{hyperref}
\hypersetup{pdfdisplaydoctitle=true,bookmarksnumbered=true,colorlinks=true,citecolor=black,linkcolor=darkblue,urlcolor=darkred,pdfstartview=FitH,pdfpagemode=UseNone}
\usepackage[hyphenbreaks]{breakurl}
\usepackage{accents}
\newcommand{\ubar}[1]{\underaccent{\bar}{#1}}

%Define Color Names
\definecolor{Gray}{rgb}{0.65,0.65,0.65}
\definecolor{darkblue}{rgb}{0,0,0.55}
\definecolor{darkred}{rgb}{0.5,0,0}

%Section Headings
\newcommand\Bheadfont{\fontsize{14pt}{\baselineskip}\selectfont}
\titleformat{\section}[hang]{\normalfont\sc\color{darkblue}\Bheadfont}{\thesection\hskip0.618em}{0em}{}
\titlespacing*{\section}{0pt}{15pt plus 2pt minus 2pt}{9pt plus 2pt minus 2pt}
\titleformat{\subsection}[runin]{\normalfont\sc\color{darkblue}} {\thesubsection\hskip0.618em}{0em}{}
\titlespacing*{\subsection}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
\titleformat{\subsubsection}[runin]{\normalfont\sc\color{darkblue}} {\thesubsubsection\hskip0.618em}{0em}{}
\titlespacing*{\subsubsection}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
\titleformat{\paragraph}[runin]{\bfseries}{\theparagraph\hskip0.618em}{0em}{}
\titlespacing*{\paragraph}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}

\begin{document}

\section{Equilibrium System}

\noindent Preferences:
\begin{gather*}
  E_0\textstyle\sum_{t=0}^\infty\beta^t [\log(c_t)-\chi n_t^{1+\eta}/(1+\eta)]
\end{gather*}

\noindent Budget Constraint:
\begin{gather*}
  c_t+b_t/(i_ts_t)=w_tn_t+b_{t-1}/\pi_t+d_t
\end{gather*}

\setcounter{equation}{0}
\subsection{ART Model}
\noindent Equilibrium system (11 equations):
\small\begin{gather}
c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
i_t=\max\{1,i_t^*\}\\
\lambda_t = c_t \\
w_t = \chi n_t^\eta \lambda_t\\
1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
  y_t=z_t n_t\\  
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
  s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t\\
  z_t=g_tz_{t-1}
\end{gather}\normalsize
Variables: $\{c,i^*,i,\lambda,w,\pi^{gap},y,n,g,s,z\}$\\

\setcounter{equation}{0}
\noindent De-trended Equilibrium System (10 equations):
\small\begin{gather}
\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
i_t=\max\{1,i_t^*\}\\
\tilde{\lambda}_t = \tilde{c}_t\\
\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
  1 = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
  \varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1-\theta + \theta\tilde{w}_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1}) (\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
  \tilde{y}_t= n_t\\  
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t
\end{gather}
Variables: $\{\tilde{c},i^*,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{y},n,g,s\}$\\

\setcounter{equation}{0}
\noindent Log-linear Equilibrium System:
\begin{gather}
  \hat{c}_t = \hat{y}_t\\
  \hat{\imath}_t^n = \rho_i\hat{\imath}^n_{t-1} + (1-\rho_i)\phi_\pi\hat{\pi}_t+\sigma_\nu\nu_t \\
  \hat{\imath}_t = \hat{\imath}_t^n\\
  \hat{\lambda}_t = \hat{c}_t \\
  \hat{w}_t =  \eta\hat{n}_t + \hat{\lambda}_t\\
  \hat{\lambda}_t + \hat{\imath}_t + s_t  = E_t\hat{\lambda}_{t+1}+E_t\hat{\pi}_{t+1} \\
  \varphi\hat{\pi}_t = (\theta-1)\hat{w}_t+\beta\varphi E_t\hat{\pi}_{t+1}\\
  \hat{y}_t = \hat{n}_t 
\end{gather}
\pagebreak
\setcounter{equation}{0}
\subsection{Gust Et Al Model}
\noindent Equilibrium system (13 equations):
\small\begin{gather}
\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
i_t=\max\{1,i_t^*\}\\
1/\lambda_t =  \beta E_t[(1/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
\lambda_t = c_t \\
c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
w_t = \chi n_t^\eta \lambda_t\\
  y_t=z_t n_t\\  
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
  s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t\\
  z_t=g_tz_{t-1}
\end{gather}\normalsize
Variables: $\{c,i^*,i,\lambda,w,\pi^{gap},V_{\lambda},y,V_{\pi},n,g,s,z\}$\\

\setcounter{equation}{0}
\noindent De-trended Equilibrium System (12 equations):
\small\begin{gather}
\varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1 - \theta + \theta\tilde{w}_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(\pi^{gap}_{t+1}-1)\pi^{gap}_{t+1}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
i_t=\max\{1,i_t^*\}\\
1/\tilde{\lambda}_t = \beta E_t[(1/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi^{gap}_{t+1}g_{t+1}))]\\%
\tilde{\lambda}_t = \tilde{c}_t\\
\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
  \tilde{y}_t= n_t\\  
  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t
\end{gather}
Variables: $\{\tilde{c},i^*,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{V}_{\lambda},\tilde{y},\tilde{V}_{\pi},n,g,s\}$\\

\setcounter{equation}{0}
\noindent Log-linear Equilibrium System:
\begin{gather}
  \varphi\hat{\pi}_t = (\theta-1)\hat{w}_t+\beta\varphi E_t\hat{\pi}_{t+1}\\
  \hat{\imath}_t^n = \rho_i\hat{\imath}^n_{t-1} + (1-\rho_i)\phi_\pi\hat{\pi}_t+\sigma_\nu\nu_t \\
  \hat{\imath}_t = \hat{\imath}_t^n\\
    -\hat{\lambda}_t = \hat{\imath}_t + s_t - E_t\hat{\lambda}_{t+1} - E_t\hat{\pi}_{t+1} \\
  \hat{\lambda}_t = \hat{c}_t \\
  \hat{c}_t = \hat{y}_t\\
  \hat{w}_t =  \eta\hat{n}_t + \hat{\lambda}_t\\
  \hat{y}_t = \hat{n}_t
\end{gather}

\setcounter{equation}{0}
\noindent Gust et al Indicator Functions\\
\begin{gather}
  c_{t+1,1} = \beta E_t[\lambda_t(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
  c_{t+1,2} = \beta E_t[\lambda_t(s_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\  
\end{gather}
for $k=1,2$ where $k=1$ corresponds to the non-ZLB regime and $k=2$ corresponds to the ZLB regime.
\begin{gather}
c_{t} = c_{t,1}I + c_{t,2}(1-I) 
\end{gather}
for $j=1,2$ and where $I$ is defined by:
$$
\begin{cases}
  I = 1 & \text{ if } i > 1\\
  I = 0 & \text{ otherwise.}
\end{cases}
$$
%We use the functions, $V_l$, to determine the decisions rule though we do not approximate $V_l$ directly, because they inherit a kink associated with the ZLB constraint. Instead, we approximate functions, $V_{l,i}$, that are smoother and easier to approximate by specifying:
%\begin{gather}
%V_l = V_{l,1}I + V_{l,2}(1-I) 
%\end{gather}
%for $l \in \{\lambda, \pi\}$ and $j=1,2$ and where $I$ is defined by:
%\begin{gather}
%  I = 1 \text{ if } i > 1\\
%  \text{  } = 0 \text{ otherwise}
%\end{gather}
%In the above, $i = \max(1,i^*)$ where $i^*$ denotes the value of the notional rate derived from evaluating the functions $V_{l,1}$ and using (2). (For each variable, we use $j=1$ to denote the function associated with the regime with a positive nominal interest rate and $j=2$ to denote the function associated with the ZLB regime. \\
%Because the functions, $V_l$ depend directly on the nominal interest rate, we expect then to have a kink or non-differentiability. By contrast, the counterpart functions, $V_{l,j}$, that are indexed by the interest-rate regime do not depend on the current indicator function and thus are more likely to be smooth. \\
%Specifically, $V_{\pi,1}$ and $V_{\pi,2}$ are both described by (8) because the nominal interest rate does not appear in that equation. $V_{\lambda,1}$ is described by (6), but for the ZLB regime:
%\begin{gather}
%V_{\lambda,t,2} =  \beta E_t[(1/\lambda_{t+1})(s_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\  
%\end{gather}
%where $i_t$ is replaced by 1.
\end{comment}
\end{document}

### 2019-03-31 src/general/parameters.m

@@ -18,7 +18,7 @@ P.rhos     = 0.80;      % Persistence
 P.rhoi     = 0.80; 	    % Persistence
 P.sigg     = 0.005;     % Standard deviation
 P.sigs     = 0.005;     % Standard deviation
-P.sigmp    = 0.005;     % Standard deviation
+P.sigmp    = 0.0035;     % Standard deviation
 P.phipi    = 2.0;       % Inflation responsiveness
 P.phiy     = 0.5;       % Output responsiveness
 P.nu       = 4;         % Investment adjustment cost

### 2019-03-31 Paper/Paper.tex
Write paper through results (bullet points)

@@
 (2017) solution methods for the models with and without capital.
-%Say something about the solution times% %Say something about the machine the solution times were computed on
-
+The solution times were computed with multi-core processing using the Parallel Computing Toolbox and integrate Fortran in the interpolation steps of our algorithm through MATLAB executable functions.
+The solution times represent one run of each algorithm.
+The machine used to compute solution times has two CPUs (at 2.30GHz), each with 16 cores.
+%Say something about the solution times%
+\begin{itemize}
+\item Gust et al. method slower, particularly on the model with capital. The differential blows up for the model with capital.
+\item The speed and speed differential is influenced by the parameterization, and appears to take more time on the boundary of convergence for each algorithm.
+\end{itemize}
 \begin{table}[H]
@@
   \caption{Solution times}
-  \label{Tab:2}
 \end{table}
 
-\subsection{Policy Functions}
+\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital.
+\hyperlink{Table 3}{Table 3} reports the RMSE and mean \% error from linear policy functions.
+The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.
 
-\subsection{Euler Equation Errors}
+\begin{itemize}
+\item ART is visually a lot smoother; matched with statistics
+  \item the Gust Et Al combined policy function si very similar to the non-ZLB policy function. All Gust Et Al policy functions have a kink corresponding to the ZLB. 
+  \item Percent error and RMSE error wise though, this is not too big of a difference?
+    \item say something about what the mean \% error and RMSE is
+  \end{itemize}
+
+\begin{figure}[H]
+\hypertarget{Figure 1}  
+    \centering
+    \includegraphics[scale=.6]{pfs3D_CAPITAL-eps-converted-to.pdf}%{pfs3D_CAPITAL.eps}
+  \caption{Labor policy function for model with capital}    
+  \label{Fig:1}
+  \end{figure}
+
+\begin{table}[H]
+  \centering
+  \hypertarget{Table 3}
+  \small
+    \setlength{\tabcolsep}{10pt}      
+  \begin{tabular}{l c c c c}
+    \hline
+    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
+    & Mean \% Error & RMSE & Mean \% Error & RMSE\\
+    \hline
+    Richter et al. policy & 0.46545\% &0.0020137 consumption units & 0.19585\% & .0029035 labor units \\    
+  Gust et al. policy & 0.45556\% & 0.0019792 consumption units & 0.56142\% & 0.0076665 labor units \\
+  \hline
+\end{tabular}
+  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). Gust et al. combined policy functions are reported.}
+\end{table}
+
+\subsection{Euler Equation Errors} \hyperlink{Figure 2}{Figure 2} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the household FOC bond, FOC capital, FOC investment, and price Phillips curve in the model with capital.
+We also report the mean and maximum error.
+The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.
+
+\begin{itemize}
+\item Euler equations very comparable between algorithms
+\item Gust et al does slightly worse. Means are similar but max is higher.
+  \end{itemize}
+
+\begin{figure}[H]
+\hypertarget{Figure 2}  
+    \centering
+    \includegraphics[scale=1.5]{eeerrors_C.eps}%{pfs3D_CAPITAL.eps}
+  \caption{Euler equation errors for model with capital}    
+  \end{figure}
 
@@
 \end{enumerate}
+
+\section{Results for model without capital} \hypertarget{Appendix C}
+The following reports the corresponding results for the model wtihout capital.
+\hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and risk premium.
+\hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the consumption euler Equation and the price Phillips curve.
+
+\begin{figure}[H]
+\hypertarget{Figure 3}  
+    \centering
+    \includegraphics[scale=.6]{pfs3D.eps}
+  \caption{Consumption policy function for model without capital}    
+  \end{figure}
+
+\begin{itemize}
+\item Smoother in general
+\item Very close between ART and GustEtAl
+  \end{itemize}
+
+\begin{figure}[H]
+\hypertarget{Figure 4}  
+    \centering
+    \includegraphics[scale=1.5]{eeerrors.eps}
+  \caption{Euler equation errors for model without capital}    
+  \end{figure}
+
+\begin{itemize}
+\item Bimodality more distinct in Gust et al policy functions
+\item Very similar with regards to mean and max; Gust et al does slightly better in consumption Euler
+\end{itemize}
 

### 2019-03-31 Paper/Paper.tex
Reword sections

@@
 
-\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the true model parameters.
-The parameters were chosen so our data generating process is characteristic of U.S.
-data.
-The steady-state growth rate ($\bar{g}$), inflation rate ($\bar{\pi}$), risk-premium ($\bar{s}$), and capital share of income ($\alpha$) are equal to the time averages of per capital real GDP growth, the percent change in the GDP implicit price deflator, the Baa corporate bond yield relative to the yield on the 10-Year Treasury, and the Fernald (2012) utilization-adjusted quarterly-TFP estimates of the capital share of income from 1988Q1-2017Q4.
-
-The subjective discount factor, $\beta$, is set to $0.9949$, which is the time average of the values implied by the steady-state consumption Euler equation and the federal funds rate.
-The corresponding annualized steady-state nominal interest rate is $3.3\%$ which is consistent with the sample average and current long-run estimates of the federal funds rate.
-The leisure preference parameter, $\chi$, is set to steady-state labor equals $1/3$ of the available time.
-The elasticities of substitution between intermediate goods $\theta$, is set to $6$, which corresponds to a $20\%$ average markup and match the values used in Gust et al.
-(2017).
-The Frisch elasticity of labor supply, $1/\eta$, is set to $3$ to match the macro estimate in Peterman (2016).
-The remainin parameters are set to round numbers that are in line with the posterior estimates from similar models in the literature.
+\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters. Parameters are from Atkinson et al. (2019), and were chosen to be characteristic of U.S. data.
 
@@
 \subsection{Richter et al. (2014)}
-We consider the solution methods of Richter et al.
-(2014) and Gust et al.
-(2017).
 The Richter et al.
-(2014) solution method is policy function iteration with time iteration and linear interpolation, which is based on the theoretical work on monotone operators in Coleman (1991).
-We discretize the endogenous state variables and approximate the exogenous states $s_t$, $g_t$, and $\varepsilon_{i,t}$ using the N-state Markov chain in Rouwenhorst (1995).
-We use the Rowenhorst method so that we only have to interpolate along the dimensions of the endogenous state variables, allowing the solution to be faster and more accurate than quadrature methods.
-To obtain initial conjectures for the nonlinear policy functions, we solve the level-linear version of our model with Sims's (2002) gensys algorithm.
-Next, we update the policy functions on each node using a fixed point iteration scheme and compute the maximum distance between the updated policy functions and the inital conjectures.
-Finally, we replace the initial conjectures with the updated policy functions and iterate until the maximum distance is below the tolerance level.
+(2014) solution method is policy function iteration with time iteration and linear interpolation.
+We first construct an evely-spaced state space by discretizing the endogenous state variables and using the Rouwenhorst (1995) method to approximate the exogenous state variables $s_t$, $g_t$, and $\varepsilon_{i,t}$.
+As in Richter et al.
+(2014), we use the Rouwenhorst method so that we do not have to interpolate along the dimensions of the exogenous state variables, providing a faster and more accurate than quadrature methods.
+To construct the initial policy functions, we solve the log-linear analog of our model with the ZLB not imposed using Sims's (2002) gensys algorithms.
+We update the policy functions using a fixed point iteration scheme on each node in the discretized state space and calculate the maximum distance between the updated policy functions and the previous guess.
+Finally, we update the policy functions with our new guess and iterate until the maximum distance is below a convergence criterion.
 \hyperlink{Appendix B}{Appendix B} provides a more detailed discussion of the solution method.
-%PLEASE REWRITE THIS SO YOU ARE NOT COPYING
+The baseline code for this algorithm is provided as a companion to Richter et al (2014).
 %Add Gust et al solution method
-\subsection{Gust et al. (2017)}
+\subsection{Gust et al. (2014)}
 The Gust et al.
-(2017) solution method similarly uses time iteration on a fixed point solution with linear interpolations.
+(2014) solution method similarly uses time iteration on a fixed point solution with linear interpolations.
 Following this solution method, instead of directly computing the policy functions, we estimate smoother functions at and away from the ZLB following Gust, L{\o g}pez-Salido, and Smith (2012) which builds on Christiano and Fisher (2000).
@@
   \subsection{Euler Equation Errors}
+We use Euler equation errors to measure the accuracy of our solutions.
+To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method following Richter et al.
+(2014) to allow exogenous variables to have realizations between grid points.
+The Euler equation errors are represented in absolute value of the errors in base 10 logarithms.
+An Euler equation error of -3 means the household makes an error equivalent to one per 1,000 consumption goods.
+
   Richter et al.
@@
 (2017) solution methods for the models with and without capital.
-The solution times were computed with multi-core processing using the Parallel Computing Toolbox and integrate Fortran in the interpolation steps of our algorithm through MATLAB executable functions.
+The solution times were computed with multi-core processing using the Parallel Computing Toolbox.
+With MATLAB executable functions (MEX) provided by the companion Toolbox to Richter et al.
+(2013), we integrate Fortran in the interpolation steps of the algorithm.
 The solution times represent one run of each algorithm.
-The machine used to compute solution times has two CPUs (at 2.30GHz), each with 16 cores.
+The machine used to compute the solutions has two CPUs (at 2.30GHz), each with 16 cores.
 %Say something about the solution times%
@@
 
+\section{Conclusion}
+% summarize results
+Opportunities for future work
+\begin{itemize}
+\item Chebyshev polynomials
+\item Smolyak grids
+  \item This might make solution method faster, so we could potentially increase the number of grid points and make it better than Richter et al
+  \end{itemize}
+
 \appendix
@@
 \section{Nonlinear Solution Method}\hypertarget{Appendix B}
-We begin by compactly writing the detrended nonlinear system as
+The following discussion is based on Atkinson et al. (2019) and Richter and Throckmorton (2014). We express the detrended nonlinear system compactly as
 \begin{gather*}
@@
 
-We use the Markov chain method in Rouwenhorst (1995) to discretize the endogenous state variables, $s_t$, $g_t$, and $\varepsilon_{i,t}$.
-Kopecky and Suen (2010) show the Rouwenhorst method outperforms other methods for approximating autoregressive processes.
-The bounds on $\tilde{c}_{t-1}, i^n_{t-1}, \tilde{k}_{t-1},$ and $\tilde{x}_{t-1}$ are set to $\pm 2.5\%, \pm 6\%, \pm 8\%, \pm 15\%$, respectively.
-Richter and Throckmorton chose these bounds so the grids contain 99.9\% of the simulated values for each state variable and during ZLB duration.
+We use the Markov chain method in Rouwenhorst (1995) to discretize the endogenous state variables, $s_t$, $g_t$, and $\varepsilon_{i,t}$ follwing Richter et al (2014).
+The bounds on $\tilde{c}_{t-1}, i^n_{t-1}, \tilde{k}_{t-1},$ and $\tilde{x}_{t-1}$ are set to $\pm 2.5\%, \pm 6\%, \pm 8\%, \pm 15\%$, respectively, following Atkinson et al.
+(2019).
 We discretize the states into 5 evenly-spaced points for the model with capital and 7 evenly-spaced points for the model without capital.
@@
 The Rouwenhorst method provides integration nodes, $[s_{t+1}(m), g_{t+1}(m), \varepsilon_{i,t+1}(m)]$, with weights, $\phi(m)$, for $m \in \{1, \dots, M\}$.
-Since the exogenous variables evolve according to a Markov chain, the number of future realizations is the same as the state variables.
 
 The vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$ ($\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), n_t(\textbf{z}_t), q_t(\textbf{z}_t), mc_t(\textbf{z}_t)]$ for the model with capital and $\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), \tilde{c}_t(\textbf{z}_t)]$.
-Our choice of policy functions is not unique, but it helps solving for the other variables in the nonlinear system of equations given $\textbf{z}_t$.
+The policy functions are selected so that solving fr other variables in the nonlinear system is straightforwards.
 
-The following steps outline our global policy function iteration algorithm:
+The following steps outline the global policy function iteration algorithm:
 
 \begin{enumerate}
-  \item Use Sims's (2002) \texttt{gensys} algorithm to solve the level-linear model without the ZLB constraint.
-Then map the solution to the discretized state space to initialize the policy functions.
-  \item On each node $d \in \{1,\dots,D\}$, use fixed point iteration to find $\textbf{pf}_t(d)$ to satisfy $E[f(\cdot)|\textbf{z}_t(d), \vartheta] \approx 0$.
-Guess $\textbf{pf}_t(d) = \textbf{pf}_{j-1}(d)$ Then apply the following:
+  \item Use Sims's (2002) \texttt{gensys} algorithm to solve the log-linear model without the ZLB constraint and obtain conjectures for the policy functions $\textbf{pf}_0$.  
+  \item On each node $d \in \{1,\dots,D\}$,% use fixed point iteration to find $\textbf{pf}_t(d)$ to satisfy $E[f(\cdot)|\textbf{z}_t(d), \vartheta] \approx 0$.
+Guess $\textbf{pf}_j(d) = \textbf{pf}_{j-1}(d)$ Then:
     \begin{enumerate}
@@
     \item Linearly interpolate the policy functions $\textbf{pf}_{j-1}$, at the updated state variables $\textbf{z}_{t+1}(m)$, to obtain $\textbf{pf}_{t+1}(m)$ on every integration node, $m \in \{1,\dots,M\}$.
-    \item Given $\{\textbf{pf}_{t+1}(m)\}_{m=1}^M$, solve for the other elements of $\textbf{s}_{t+1}(m)$ and compute%and back out the updated \textbf{pf}$_t(d)$.
+    \item Given $\{\textbf{pf}_{t+1}(m)\}_{m=1}^M$, solve for the other elements of $\textbf{s}_{t+1}(m)$ and approximate the expectation operators %and back out the updated \textbf{pf}$_t(d)$.
       \begin{gather*}
@@
       \end{gather*}
-      \item Back out $\textbf{pf}_t(d)$ from the expectation operators and updated state.
+      \item Solve for $\textbf{pf}_t(d)$ from the expectation operators and $\textbf{s}_{t+1}(m)$. Set $\textbf{pf}_j(d) = \textbf{pf}_t(d)$.
     \end{enumerate}

### 2019-04-01 Paper/Paper.tex
Work on paper through fleshing out future research

@@
 \begin{document}
+
+\section{Introduction}
+As a result of the financial crisis of 2007-9 and the subsequent recession, central banks lowered their policy rate to its zero lower bound (ZLB).
+Although the ZLB constraint has always existed, for most of the data prior to the recession, policy rates were well above zero.
+In the wake of this unprecedented lowering of policy rates, the ZLB holds for a considerable portion of historic data for three major economies – the US, Japan, and Great Britain.
+The ZLB creates a kink in the policy rule and calls into question linear estimation methods.
+Researchers have responded to this inherent nonlinearity in different ways.
+Some have failed to incorporate the ZLB period data.
+Others have chosen to estimate linear models on the entire data set; however, this provides inaccurate estimates of model parameters and model predictions.
+A few have estimated nonlinear models that treats the ZLB as an occasionally binding constraint.
+As incorporating the ZLB constraint makes traditional solution methods intractable, researchers have turned to fully nonlinear models, including those described in Richter et al (2013) and Gust et al (2017).
+However, not much work has been done in comparing the accuracy and speed of different global nonlinear solution methods.
+We will examine the performance of Richter et al (2013) and Gust et al (2017) in terms of accuracy and speed.
 
@@
 
-\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters. Parameters are from Atkinson et al. (2019), and were chosen to be characteristic of U.S. data.
-
-\begin{table}
+\begin{table}[H]
   \hypertarget{Table 1}
+  \centering
+    \captionsetup{justification=centering}
   \small
@@
 \end{table}
+
+\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters. Parameters are from Atkinson et al. (2019), and were chosen to be characteristic of U.S. data.
 
@@
 
+Another contribution of Gust et al (2017) is to solve their model using Smolyak discretization methods with Chebyshev polynomials.
+The Smolyak method, proposed by Smolyak (1963) and improved by Judd et al.
+(2014) is a sparse-grid method and thus avoids the curse of dimensionality associated with grid-based methods.
+However, we do not explore this difference in this paper.
+
   \subsection{Euler Equation Errors}
@@
 
-  Richter et al.
-(2014) use Euler equation errors to measure the accuracy of their solutions.
-To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method to allow exogenous variables to be off the grid.
-The Euler equation errors are reported in absolute value of the errors in base 10 logarithms.
-A consumption Euler equation error of -3 means the household makes an error equal to one out of every 1,000 consumption goods.
+  We simulate 10,000 periods of the model at the nonlinear solution with random shocks.
+For each period, we follow one iteration of step 2 of the algorithm outlined in \hyperlink{Appendix B}{Appendix B} and then transform the residuals to Euler equation errors.
+
+We considered adding a second measure of accuracy, a statistical measure from Den Haan and Marcet (1994) based on a transformation of the Euler equation residuals to a chi-square distribution.
+However, it proved uninformative, as several runs of the test statistic were all in the extreme tails of the distribution.
 
 \section{Results}
+
+\begin{table}[H]
+  \centering
+    \captionsetup{justification=centering}
+  \hypertarget{Table 2}
+  \small
+    \setlength{\tabcolsep}{10pt}      
+  \begin{tabular}{l c c c c}
+    \hline
+    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
+    & Iterations & Total Time & Iterations & Total time\\
+    \hline
+  Richter et al. (2013) & 67 & 17.9s & 65 & 0h 15m 37.1s\\    
+  Gust et al. (2017) & 66 & 46s & 1170 &  5h 32m 48.6s\\
+  \hline
+\end{tabular}
+  \caption{Solution times}
+\end{table}
 
@@
 \end{itemize}
-\begin{table}[H]
-  \centering
-  \hypertarget{Table 2}
-  \small
-    \setlength{\tabcolsep}{10pt}      
-  \begin{tabular}{l c c c c}
-    \hline
-    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
-    & Iterations & Total Time & Iterations & Total time\\
-    \hline
-  Richter et al. (2013) & 67 & 17.9s & 65 & 0h 15m 37.1s\\    
-  Gust et al. (2017) & 66 & 46s & 1170 &  5h 32m 48.6s\\
-  \hline
-\end{tabular}
-  \caption{Solution times}
-\end{table}
-
-\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital.
-\hyperlink{Table 3}{Table 3} reports the RMSE and mean \% error from linear policy functions.
-The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.
-
-\begin{itemize}
-\item ART is visually a lot smoother; matched with statistics
-  \item the Gust Et Al combined policy function si very similar to the non-ZLB policy function. All Gust Et Al policy functions have a kink corresponding to the ZLB. 
-  \item Percent error and RMSE error wise though, this is not too big of a difference?
-    \item say something about what the mean \% error and RMSE is
-  \end{itemize}
 
@@
   \centering
-    \includegraphics[scale=.6]{pfs3D_CAPITAL-eps-converted-to.pdf}%{pfs3D_CAPITAL.eps}
+    \captionsetup{justification=centering}
+    \includegraphics[scale=1.05]{pfs3DCAP.eps}
   \caption{Labor policy function for model with capital}    
-  \label{Fig:1}
   \end{figure}
+
+\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital.
+The black dots on the nodes of the graph represent labor values corresponding to the ZLB.
 
@@
   \centering
+  \captionsetup{justification=centering}
   \hypertarget{Table 3}
@@
 
+\hyperlink{Table 3}{Table 3} reports the RMSE (root mean square error) and mean percent error from linear policy functions.
+The mean percent error is calculated as $1/N\sum_i^N |\textbf{pf.n}(i) - \hat{\textbf{n}}(i)|/\bar{n}$ where $N$ is the number of periods, $\textbf{pf.n}$ is the labor policy function, $\hat{\textbf{n}}$ is the linear regression model of $\textbf{pf.n}$ fit to the state variables, and $\bar{n}$ is steady state labor.
+The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.
+
+\begin{itemize}
+\item ART is visually a lot smoother; matched with statistics
+  \item the Gust Et Al combined policy function si very similar to the non-ZLB policy function. All Gust Et Al policy functions have a kink corresponding to the ZLB. 
+  \item Percent error and RMSE error wise though, this is not too big of a difference?
+    \item say something about what the mean \% error and RMSE is
+  \end{itemize}
+
+\begin{figure}[H]
+\hypertarget{Figure 2}  
+\centering
+  \captionsetup{justification=centering}
+    \includegraphics[scale=1]{eeerrorsCAP.eps}%{pfs3_CAPITAL.eps}
+  \caption{Euler equation errors for model with capital}    
+  \end{figure}
+
 \subsection{Euler Equation Errors} \hyperlink{Figure 2}{Figure 2} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the household FOC bond, FOC capital, FOC investment, and price Phillips curve in the model with capital.
@@
 
-\begin{figure}[H]
-\hypertarget{Figure 2}  
-    \centering
-    \includegraphics[scale=1.5]{eeerrors_C.eps}%{pfs3D_CAPITAL.eps}
-  \caption{Euler equation errors for model with capital}    
-  \end{figure}
-
 \section{Conclusion}
 % summarize results
-Opportunities for future work
-\begin{itemize}
-\item Chebyshev polynomials
-\item Smolyak grids
-  \item This might make solution method faster, so we could potentially increase the number of grid points and make it better than Richter et al
-  \end{itemize}
+Future work includes solving the Gust et al (2017) solution method using Smolyak discretization methods with Chebyshev polynomials.
+This would likely speed up the solution algorithm.
+We could increase the number of grid points to improve the accuracy of the solution with the regained time and compare this to the Richter et al (2013) solution method.
 
@@
 \section{Results for model without capital} \hypertarget{Appendix C}
-The following reports the corresponding results for the model wtihout capital.
-\hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and risk premium.
-\hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the consumption euler Equation and the price Phillips curve.
+The following reports the corresponding results for the model without capital.
 
@@
 \centering
-    \includegraphics[scale=.6]{pfs3D.eps}
+  \captionsetup{justification=centering}
+    \includegraphics[scale=1]{pfs3D.eps}
   \caption{Consumption policy function for model without capital}    
   \end{figure}
+
+\hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and risk premium.
+
+\begin{figure}[H]
+  \hypertarget{Figure 4}
+  \centering
+    \captionsetup{justification=centering}
+    \includegraphics[scale=.75]{eeerrors.eps}
+  \caption{Euler equation errors for model without capital}    
+  \end{figure}
+
+\hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the consumption euler Equation and the price Phillips curve.
 
@@
   \end{itemize}
-
-\begin{figure}[H]
-\hypertarget{Figure 4}  
-    \centering
-    \includegraphics[scale=1.5]{eeerrors.eps}
-  \caption{Euler equation errors for model without capital}    
-  \end{figure}
 

### 2019-04-01 src/general/figs/figeeerrors_bothalgs.m

@@ -64,13 +64,13 @@ if strcmp(plottype,'M')
 elseif strcmp(plottype,'P')
     savename = [figname '_pres'];
     set(0,'DefaultAxesFontSize',8)
-    figbox = [1,1,4.5,2.5];
-    subpad.bot = .175; % Increase if xaxis lables are cut off
-    subpad.top = .125; % Increase if subplot title is cut off
-    subpad.left = .15; % Increase if ylabel is cut off
+    figbox = [1,1,7,2.5];
+    subpad.bot = .325; % Increase if xaxis lables are cut off
+    subpad.top = .15; % Increase if subplot title is cut off
+    subpad.left = .25; % Increase if ylabel is cut off
     subpad.right = .05; % Decrease if white-space on RHS
     subpad.legend = 0; % Increase if legend overlaps subplot titles
-    fontsize = 8;
+    fontsize = 9;
 end
 
 plotdim = [2,4];
@@ -92,16 +92,16 @@ for isubplot = 1:prod(plotdim)
     if isubplot < 5
         N1 = hist(EE_ART(:,iEE1),bins{iEE1}); %ART
         bar(bins{iEE1},100*N1/length(EE_ART(:,iEE1)),'grouped')
-        text(-7.5,16.5,['Mean: ', num2str(RMeanEEART(iEE1))],'Fontsize',8);
-        text(-7.5,13.5,['Max: ', num2str(RMaxEEART(iEE1))],'Fontsize',8);
+        text(-7.80,16.5,['Mean: ', num2str(RMeanEEART(iEE1))],'Fontsize',8);
+        text(-7.8,13.5,['Max: ', num2str(RMaxEEART(iEE1))],'Fontsize',8);
         iEE1 = iEE1 + 1;    
         ylabel('ART','interpreter','latex','fontsize',fontsize)
         ylim([0, 20])
     else
         N2 = hist(EE_Gust(:,iEE2),bins{iEE2}); %GustEtAl
         bar(bins{iEE2},100*N2/length(EE_Gust(:,iEE2)),'grouped')
-        text(-7.5,11,['Mean: ', num2str(RMeanEEGust(iEE2))],'Fontsize',8);        
-        text(-7.5,8.5,['Max: ', num2str(RMaxEEGust(iEE2))],'Fontsize',8);
+        text(-7.8,11,['Mean: ', num2str(RMeanEEGust(iEE2))],'Fontsize',8);        
[…]

### 2019-04-01 src/general/solutions/smoothness_test.m

@@ -113,7 +113,9 @@ disp(['Gust, n: ',num2str(meanperc_err{2}), '%'])
 disp(['Gust, n_zlb: ', num2str(meanperc_err{3}), '%'])
 disp(['Gust, n_agg: ', num2str(meanperc_err{4}), '%'])
 
-figure('Renderer', 'painters', 'Position', [100 100 825 525])
+figbox = [1,1,7,3.5];
+figure;%('Renderer', 'painters', 'Position', [100 100 825 525])
+set(gcf,'position',figbox);
 
 in_vec = squeeze(G.in_gr(2,:,2,:,3,3,3));
 in_vec = in_vec(:);
@@ -141,16 +143,16 @@ hold on
 scatter3(in_vec,s_vec, z_zlb{i}(:),15,'MarkerEdgeColor','k',...
         'MarkerFaceColor','k')
 hold off
-xlabel('Interest rate')
-ylabel('Risk premium')
-zlabel('Labor')
-title(label{i})
+xlabel('Interest rate','Fontsize',9)
+ylabel('Risk premium','Fontsize',9)
+zlabel('Labor','Fontsize',9)
+title(label{i},'Fontsize',10)
 [az, el] = view;
 view(az+90-25,el-20)
 % view(az-90,el-10)
 %view(-37.5-90,30-10)
-text(0.999,1.01,.365,['mean \% err: ',num2str(meanperc_err{i},'%.6f'),'\%'])
-text(0.999,1.01,.36,'Black dots: ZLB')
+text(0.999,1.01,.365,['mean \% err: ',num2str(meanperc_err{i},'%.6f'),'\%'],'Fontsize',8)
+text(0.999,1.01,.36,'Black dots: ZLB','Fontsize',8)
 end
 
 saving = 'on';

### 2019-04-01 src/simple/figs/figeeerrors_bothalgs.m

@@ -30,8 +30,8 @@ EE_Gust(:,2) = R.EE2(:);
 RMeanEEGust(:,1) = R.meanEE;
 RMaxEEGust(:,1) = R.maxEE;
 
-bins{1} = -6:.0833:-2.25;
-bins{2} = -7.25:.0833:-1.5;
+bins{1} = -6:.1:-2.25;
+bins{2} = -7.25:.1:-1.5;
 
 nEE = size(EE_ART,1);
 
@@ -40,7 +40,7 @@ titles = {'Consumption Euler','Firm Pricing','Consumption Euler','Firm Pricing'}
 % Plot options
 if strcmp(plottype,'M')
     savename = ['Figs/' figname];
-    figbox = [1,1,6.5,2.5];
+    figbox = [1,1,7,4];
     subpad.bot = .175; % Increase if xaxis lables are cut off
     subpad.top = .125; % Increase if subplot title is cut off
     subpad.left = .075; % Increase if ylabel is cut off
@@ -50,7 +50,7 @@ if strcmp(plottype,'M')
 elseif strcmp(plottype,'P')
     savename = ['Figs/' figname '_pres'];
     set(0,'DefaultAxesFontSize',8)
-    figbox = [1,1,4.5,2.5];
+    figbox = [1,1,7,5];
     subpad.bot = .175; % Increase if xaxis lables are cut off
     subpad.top = .125; % Increase if subplot title is cut off
     subpad.left = .15; % Increase if ylabel is cut off
@@ -78,24 +78,24 @@ for isubplot = 1:prod(plotdim)
     if isubplot < 3
         N1 = hist(EE_ART(:,iEE1),bins{iEE1}); %ART
         bar(bins{iEE1},100*N1/length(EE_ART(:,iEE1)),'grouped')
-        text(-7.5,11,['Mean: ', num2str(RMeanEEART(iEE1))],'Fontsize',8);
-        text(-7.5,8.5,['Max: ', num2str(RMaxEEART(iEE1))],'Fontsize',8);
+        text(-7.5,11,['Mean: ', num2str(RMeanEEART(iEE1))],'Fontsize',10);
+        text(-7.5,8.5,['Max: ', num2str(RMaxEEART(iEE1))],'Fontsize',10);
         iEE1 = iEE1 + 1;    
-        ylabel('ART','interpreter','latex','fontsize',fontsize)
+        ylabel('ART','interpreter','latex','FontSize',10)
         ylim([0, 15])
     else
[…]

### 2019-04-01 src/simple/solutions/smoothness_test.m

@@ -87,7 +87,9 @@ disp(['Gust, c: ',num2str(meanperc_err{2}), '%'])
 disp(['Gust, c_zlb: ', num2str(meanperc_err{3}), '%'])
 disp(['Gust, c_agg: ', num2str(meanperc_err{4}), '%'])
 
-figure('Renderer', 'painters', 'Position', [100 100 825 525])
+figbox = [1,1,7,4.5];
+figure;%('Renderer', 'painters', 'Position', [100 100 825 525])
+set(gcf,'position',figbox);
 
 in_vec = squeeze(G.in_gr(4,:,4,:));
 in_vec = in_vec(:);
@@ -111,14 +113,14 @@ hold on
 scatter3(in_vec,s_vec, z_zlb{i}(:),15,'MarkerEdgeColor','k',...
         'MarkerFaceColor','k')
 hold off
-xlabel('Interest rate')
-ylabel('Risk premium')
-zlabel('Consumption')
-title(label{i})
+xlabel('Interest rate','FontSize',9)
+ylabel('Risk premium','FontSize',9)
+zlabel('Consumption','FontSize',9)
+title(label{i},'FontSize',10)
 [az, el] = view;
 view(az-90,el-10)
-text(1.013,1.04,.37,['avg % err: ',num2str(meanperc_err{i})])
-text(1.013,1.04,.36,'Black dots: ZLB')
+text(1.013,1.04,.37,['avg \% err: ',num2str(meanperc_err{i})],'FontSize',9)
+text(1.013,1.04,.36,'Black dots: ZLB','FontSize',9)
 end
 
 % % Linear regressions using regress

### 2019-04-11 Paper/Paper.tex
Sync Paper to school computers work

--- 2019-03-31 Paper/Paper.tex
@@
 \newcommand{\ubar}[1]{\underaccent{\bar}{#1}}
+\usepackage{epstopdf}
+\epstopdfsetup{outdir=./}
+\usepackage{xcolor}
+\usepackage{setspace}
+\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
+\let\endchangemargin=\endlist 
+\newcommand{\forceindent}{\leavevmode{\parindent=15pt\indent}}
 
@@
 
+\title{Comparison of Global Solution Methods to a Zero Lower Bound Model}
+\date{\small First Draft: \today}
+\author{Emily Martell\thanks{Thank you to Professor Throckmorton for advising and providing materials for this project.
+Thank you to Professor Campbell, Professor Han, Professor Rolek, and Professor Throckmorton for serving on my committee.}}
 \begin{document}
+\maketitle
+\bigskip
+\begin{center}
+\fontsize{14pt}{\baselineskip}\sc Abstract%\normalfont
+\end{center}
 
-\section{Model}
+\onehalfspacing
+\begin{changemargin}{1cm}{1cm}
+
+{\small \forceindent During the Great Recession, the U.S.
+Federal Reserve lowered policy rates to zero, creating a kink in its policy rule, and calling into question traditional solution methods.
+Recent work has explored fully nonlinear models to represent the ZLB, but not much work has compared the performance of different solution methods.
+Two suggested solution methods are linear interpolation This paper examines the effect of making the policy functions conditional on whether the ZLB binds.
+We consider a fully nonlinear New Keynesian model with capital, and a solution algorithm with policy function iteration and linear interpolation.
+We find no evidence that the regime-indexed policy functions are smoother.
+In addition, the solution algorithms perform similarly with respect to accuracy, but the solution containing the regime-indexed policy functions is much slower, all else equal.}
+\end{changemargin}
+\vfill
+\pagebreak
+
+\section{Introduction}
+
+As a result of the global financial crisis of 2007-9 and the subsequent recession, central banks lowered
+their policy rate to its zero lower bound (ZLB). Although the ZLB constraint has always existed,
+for most of the data prior to the recession, policy rates were well above zero. In the wake of this
+unprecedented lowering of policy rates, the ZLB holds for a considerable portion of historic data
+for three major economies --- the US, Japan, and the Euro Area. The ZLB creates a kink in the policy
+rule and calls into question linear estimation methods.
+
+Researchers have responded to this inherent
+nonlinearity in different ways. Some have failed to incorporate the ZLB period data. Others have
+chosen to estimate linear models on the entire data set; however, this could lead to inaccurate estimates
+of model parameters and model predictions.
+Some have estimated a piecewise linear version of the nonlinear model (e.g., \hyperlink{Guerrieri}{\color{black}{Guerrieri and Iacoviello, 2017}}).
+A few have estimated fully nonlinear models that treats the
+	ZLB as an occasionally binding constraint (e.g., \hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}; \hyperlink{Plante}{\color{black}{Plante et al.,\ 2018}}; \hyperlink{RT}{\color{black}{Richter and Throckmorton, 2016}}).
+These papers solve the nonlinear model using projection methods, which is explored in several other papers (e.g.
+\hyperlink{Aruoba}{\color{black}{Aruoba et al.,\ 2018}}; \hyperlink{Fernandez}{\color{black}{Ferna\'ndez-Villaverde et al.,\ 2015)}}.
+Solving a nonlinear model using projection methods provides the most comprehensive treatment of the ZLB but is computationally intensive.
+
+As it is important to incorporate all historical data and yield accurate parameter values and predictions, the path forward seems to be in fully nonlinear models.
+Among those that use projection methods to solve a nonlinear model, some use policy function iteration with linear interpolation (e.g., \hyperlink{Plante}{\color{black}{Plante et al.,\ 2018}}; \hyperlink{RT}{\color{black}{Richter and Throckmorton, 2016}}).
+In terms of the approximating function, others estimate alternative functions like regime-indexed policy functions (\hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}) or piecewise smooth policy functions (\hyperlink{Aruoba}{\color{black}{Aruoba et al.\ 2018}}) to avoid the kink introduced by the ZLB.
+With respect to the grid construction, some use the Smolyak collocation method developed by \hyperlink{Judd}{\color{black}{Judd et al.\ (2010)}} to reduce the burden of dimensionality (e.g., \hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}; \hyperlink{Fernandez}{\color{black}{Ferna\'ndez-Villaverde et al.\, 2015}}; \hyperlink{Aruoba}{\color{black}{Aruoba et al.,\ 2018}}).
+Not much work has been done in comparing the accuracy and speed of different global nonlinear solution methods.
+We will  examine the performance of \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} and \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} in terms of accuracy and speed as examples of different ways to solve nonlinear models.
+
+The \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} solution method is policy function iteration with linear interpolation to approximate future variables.
+The state space features evenly-spaced nodes and exogenous state variables  approximated with the Markov chain from \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}}.
+The Rouwenhorst approximation is useful because it only requires interpolation along the dimensions of the endogenous state variables.
+This yields a faster and more accurate solution than quadrature methods.They update the policy functions with linear interpolation to accurately capture the kink experienced at the ZLB.
+
+The \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method approximates policy functions underlying the model's decision rule using an antistropic Smolyak method with Chebyshev polynomials.
+(See \hyperlink{Judd2}{\color{black}{Judd et al.\ (2014)}} for a discussion of antistropic Smolyak methods).
+They approximate the exogenous state variables using Gauss-Hermite quadrature.
+Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, which builds on \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}}.
+The idea is that the policy functions feature a kink or non-differentiability at the ZLB and regime-indexing the policy functions will yield smoother functions.
+
+In this paper, we consider the effect of making the policy functions conditional on whether the ZLB binds.
+To isolate the effect of splitting the policy functions, we use policy function iteration on a fixed point with linear interpolation following \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}.
+This solution method also provides the motivation for a single policy function, and the \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution provides the motivation for a regime-indexed policy function.
+Henceforth, the solution method based on the \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} solution algorithm will be denoted ART and the solution algorithm that estimates smoother functions based on \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} will be denoted GHLS.
+It is important to note that we do not consider the effect of a Smolyak basis with Chebyshev polynomials, so this is a modified \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method.
+The key point in this paper is to explore how splitting up the policy functions conditional on the ZLB impacts the speed and accuracy of the solution of a nonlinear model.
+
+First, we construct the state space with evenly-spaced nodes and approximate the exogenous state variables with \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}}.
+After obtaining initial conjectures for a set of policy functions from the log-linear solution, we iterate on the policy functions, linearly interpolating and numerically integrating the policy functions each step, using a fixed point iteration scheme.
+The algorithm converges once the maximum distance between successive guesses of policy functions falls below a convergence criterion.
+For the ART portion, we update a single policy function.
+For the GHLS portion, we update regime-indexed policy functions.
+
+%In a NK model instead???
+The standard representation of the Euler equation is
+\begin{gather*}
+u'(c_t)  = \beta u'(c_{t+1})[f'(k_{t+1}) + 1 - \delta],
+\end{gather*}
+where $u(\cdot)$ is the instantaneuous utility function, $0<\beta<1$ is the discount factor, $c_t$ is consumption at period $t$, $k_t$ is the capital stock at the beginning of the period, $0 < \delta \leq 1$ is the rate of depreciation, and $f(\cdot)$ is the production function.
+$u(\cdot)$ and $f(\cdot)$ are differentated according to the choice variables.
+The Euler equation is the fundamental dynamic equation in intertemporal optimization problems that include dynamic constraints.
+It states that the marginal cost of forgoing consumption today must equal the discounted marginal benefit of investing in capital for one period.
+%Cite Dr Richter's notes?
+
+%Here make a better segway
+The interest rate appears in the household's budget constraint in models where the household has the choice of owning a nomimal bond.
+The household must choose a combination of consumption, labor, and bond holdings to maximize expected lifetime utility.
+Thus, the household's choice of consumption depends on the interest rate and whether the economy is at the ZLB.
+To approximate regime-indexed consumption policy functions $c_t^{ZLB}$ and $c_t^{normal}$, we provide initial guesses based on the log-linear solution.
+We refine the policy function guesses as follows: For each node in the state space, we solve for the time $t$ variables with either the $c_t^{ZLB}$  or $c_t^{normal}$ according to $i_t$, the interest rate at time $t$.
+With the time $t$ variables, we linearly interpolate both policy functions.
+Next, we calculate the interest rate on each node in the state space, construct an aggregate consumption policy function based on whether the economy is at the ZLB on each node, and calculate time $t+1$ variables acordingly.
+We then update $c_t^{ZLB}$ with an interest rate of 1, and $c_t^{normal}$ with $i_t$.
+
+%It might help to explain in the intro the key difference in the approximation of the policy functions.
+You could show a standard Euler Equation, point out the nominal interest rate, and then explain you would approximate a policy function for consumption that depends on whether the economy is at the ZLB.
+
+In terms of accuracy, both the ART and GHLS yield similar Euler equation errors, with ART being slightly more accurate for the model with capital.
+The ART method converges much more quickly than the GHLS method, particularly when capital is introduced to the model.
+There is not a clear advantage of the regime-indexed policy function approximation when using an evenly spaced grid with linear interpolation.
+All else equal, using regime-indexed policy functions increases the computing time.
+However, introducing Chebyshev polynomials and sparse grid methods as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} may reduce solution time and allow us to solve larger models with more state variables.
+Further research could explore how much accuracy is gained or lost relative to using non regime-indexed policy functions approximated with Chebyshev polynomials.
+
+The remainder of the paper is as follows: \hyperlink{Section 2}{Section 2} outlines our setup for the model with capital.
+\hyperlink{Section 3}{Section 3} describes regime-indexed polynomials and outlines the solution algorithm.
+\hyperlink{Section 4}{Section 4} discusses the results in terms of solution time, curvature of policy functions, and Euler equation errors.
+\hyperlink{Section 5}{Section 5} concludes.
+
+\section[Section 2]{Model \hypertarget{Section 2}{}} 
+This is a widely-employed New Keynesian model which is similar to the model in \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but includes capital accumulation as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}}.
+Thus, it is an appropriate model to benchmark the accuracy and speed of the two solution methods.
+
 \subsection{Firms} The production sector consists of a continuum of monopolistically competitive intermediate goods firms and a final goods firm.
@@
 Dividend maximization determines the demand for intermediate good $f$, $y_t(f) = (p_t(f)/p_t)^{-\theta}y_t$, where $p_t = [\int_{0}^{1} p_t(f)^{1-\theta}df]^{1/(1-\theta)}$ is the price level.
-Following Rotemberg (1982), intermediate firms pay a price adjustment cost, $adj_t^p(f) \equiv \varphi(p_t(f)/(\bar{\pi}p_{t-1}(f))-1)^2)y_t/2$, where $\varphi > 0$ scales the cost and $\bar{\pi}$ is the steady-state gross inflation rate.
+Following \hyperlink{Rotemberg}{\color{black}{Rotemberg (1982)}}, intermediate firms pay a price adjustment cost, $adj_t^p(f) \equiv \varphi(p_t(f)/(\bar{\pi}p_{t-1}(f))-1)^2)y_t/2$, where $\varphi > 0$ scales the cost and $\bar{\pi}$ is the steady-state gross inflation rate.
 Given this cost, firm $f$ chooses $n_t(f)$, $k_{t-1}(f)$, and $p_t(f)$ to maximize the expected discounted present value of future dividends, $E_t\sum_{k=t}^\infty q_{t,k}d_k(f)$, subject to its production function and the demand for its product, where $q_{t,t} \equiv 1$, $q_{t,t+1} \equiv \beta(\lambda_t/\lambda_{t+1})$ is the pricing kernel between periods $t$ and $t+1$, $q_{t,k} \equiv \prod_{j=t+1}^{k>t} q_{j-1,j}$, and $d_t(f) = p_t(f)y_t(f)/p_t - w_tn_t(f) - adj_t^p(f)$.
@@
 \begin{gather*}
-    c_t+x_t+b_t/(i_ts_t)=w_tn_t+r_t^kk_{t-1}+b_{t-1}/\pi_t+d_t
+    c_t+x_t+b_t/(i_ts_t)=w_tn_t+r_t^kk_{t-1}+b_{t-1}/\pi_t+d_t,
   \end{gather*}
@@
     \label{eq:15}
-    i_t=\max\{1,i_t^n\}\\
+    i_t=\max\{1,i_t^n\},\\
       \label{eq:16}
@@
 
-\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters. Parameters are from Atkinson et al. (2019), and were chosen to be characteristic of U.S. data.
-
-\begin{table}
+\begin{table}[H]
   \hypertarget{Table 1}
+\centering
+\captionsetup{justification=centering}
   \small
-    \setlength{\tabcolsep}{10pt}      
+    \setlength{\tabcolsep}{7.5pt}      
   \begin{tabular}{l c c l c c}
@@
 
-\section{Solution Methods}
-\subsection{Richter et al. (2014)}
-The Richter et al.
-(2014) solution method is policy function iteration with time iteration and linear interpolation.
-We first construct an evely-spaced state space by discretizing the endogenous state variables and using the Rouwenhorst (1995) method to approximate the exogenous state variables $s_t$, $g_t$, and $\varepsilon_{i,t}$.
-As in Richter et al.
-(2014), we use the Rouwenhorst method so that we do not have to interpolate along the dimensions of the exogenous state variables, providing a faster and more accurate than quadrature methods.
-To construct the initial policy functions, we solve the log-linear analog of our model with the ZLB not imposed using Sims's (2002) gensys algorithms.
-We update the policy functions using a fixed point iteration scheme on each node in the discretized state space and calculate the maximum distance between the updated policy functions and the previous guess.
-Finally, we update the policy functions with our new guess and iterate until the maximum distance is below a convergence criterion.
-\hyperlink{Appendix B}{Appendix B} provides a more detailed discussion of the solution method.
-The baseline code for this algorithm is provided as a companion to Richter et al (2014).
-%Add Gust et al solution method
-\subsection{Gust et al. (2014)}
-The Gust et al.
-(2014) solution method similarly uses time iteration on a fixed point solution with linear interpolations.
-Following this solution method, instead of directly computing the policy functions, we estimate smoother functions at and away from the ZLB following Gust, L{\o g}pez-Salido, and Smith (2012) which builds on Christiano and Fisher (2000).
-Since the policy functions depend directly on the nominal interetst rate, they have a kink or non-differentiability associated with the ZLB.
-On the other hand, the regime-indexed policy functions do not depend on the current indicator function and are thus more likely to be smooth.
-The smoother functions are approximated by specifying:
+\subsection{Parameter Values} \hyperlink{Table 1}{Table 1} shows the model parameters.
+Parameters are from \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, and are chosen to be characteristic of U.S.
+data.
+The subjective discount factor, $\beta$ is set to $0.9949$, the time average of the values implied by the steady-state consumption Euler equation and the federal funds rate.
+The Frisch labor supply elasticity $1/\eta$ is set to 3 to match the macro estimate in \hyperlink{Peterman}{\color{black}{Peterman (2016)}}.
+The price elasticity of substitution $\theta$ is set to 6, matching GHLS and corresponding to to a 20\% average markup.
+Steady-state labor hours $\bar{n}$ is set to 1/3 of available time.
+The steady-state risk premium, growth rate, and inflation rate are set to the time averages of per capital real DGP growth, the percent GDP implicit price deflator, and the Baa corporate bond yield relative to the yield on the 10-Year Treasury.
+The capital share of income $\alpha$ is equal to the \hyperlink{Fernald}{\color{black}{Fernald (2012)}} utilization-adjusted quarterly-TFP estimates of the capital share of income from 1988-2017Q4.
+The other parameters are set to values consistent with posterior estimates from similar models in the literature.
+For the model without capital, all parameters are the same except $\sigma_i$ which is set to $0.002$.
+(For the model with capital, $\sigma_i$ was originally set to $0.002$ to match \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but the model failed to hit the ZLB during simulation, so we increased the parameter to $0.0035$.)
+
+\section[Section 3]{Solution Methods \hypertarget{Section 3}{}} 
+\subsection{Regime-indexed policy functions} Instead of directly approximating the policy functions, some papers elect to approximate alternative functions to avoid the kink experienced at the ZLB (e.g., \hyperlink{Gust}{\color{black}{Gust et al.,\ 2017}}; \hyperlink{Aruoba}{\color{black}{Aruoba et al.,\ 2018}}).
+\hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} uses policy functions that are indexed by the interest-rate regime.
+Because these functions do not depend on the current indicator function,\hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} claims that they are more likely to be smooth.
+The regime-specific functions still depend on a secondary effect that the non-differentiability in the nominal rate in the following period has on expectations of future variables.
+However, following \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}} this effect should be small due to the presence of the expectations operators which act to smooth out regime-specific functions.
+The idea for regime-indexed policy functions is as follows:
 \begin{gather}
-  \textbf{pf}_t(d) = \textbf{pf}_{t,1}(d)\mathds{I}_t(d) + \textbf{pf}_{t,2}(d)(1-\mathds{I}_t(d))
+    \label{eq:18}
+  \textbf{pf}_t(d) = \textbf{pf}_{t,1}(d)\mathds{I}_t(d) + \textbf{pf}_{t,2}(d)(1-\mathds{I}_t(d)),
 \end{gather}
+
 where $\mathds{I}_t(d)$ is defined by
 \begin{gather}
+    \label{eq:19}
   \mathds{I}_t(d) = 
@@
      1 &\text{ if } i_t > 1\\
-     0 &\text{ otherwise}
+     0 &\text{ otherwise.}
 \end{cases}
@@
 \begin{gather}
-  R_{t,1,1} = 1 - s_ti_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))]\\
-  R_{t,1,2} = 1 - s_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))]\\
-  R_{t,2,j} = q_t - \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})]\\
-  R_{t,3,j} = 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] - \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)]\\
-  R_{t,4,j} = \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t - \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]
+\label{eq:20}
+  R_{t,1,1} = 1 - s_ti_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))],\\
+\label{eq:21}
+  R_{t,1,2} = 1 - s_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))],\\
+\label{eq:22}
+  R_{t,2,j} = q_t - \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})],\\
+\label{eq:23}
+  R_{t,3,j} = 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] - \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)],\\
+\label{eq:24}
+  R_{t,4,j} = \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t - \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
   \end{gather}
+
+\subsection{Solution Algorithm}
+Our solution algorithm is as follows: Construct an evenly-spaced grid by discretizing the endogenous state variables and using \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}} method to approximate the exogenous processes for $s_t$, $g_t$, and $\varepsilon_{i,t}$.
+We use the Rouwenhorst method so that we do not have to interpolate along the dimensions of the exogenous state variables, providing a faster and more accurate than quadrature methods.
+The vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$.
+Denote the vector of states $\textbf{z}_t$.
+\begin{enumerate} 
+\item To construct the initial policy functions $\textbf{pf}_0$, we solve the log-linear analog of our model with the ZLB not impos
+ed using \hyperlink{Sims}{\color{black}{Sims's (2002) \texttt{gensys}}} algorithm. (For GHLS, we initialize the regime-indexed policy functions by setting them to the log-linear solution.)
+\item For each node in the state space $d \in \{1,\dots,D\}:$
+\begin{enumerate}
+\item Solve for the variables dated at time $t$ given $\textbf{pf}_t$ and $\textbf{z}_t$.
+(For GHLS, we calculate time $t$ variables with the non-ZLB policy functions if the interest rate $i_t > 1$, and the ZLB policy functions if the interest rate $i_t \leq 1$).
+\item  Linearly interpolate the policy functions at the updated state variables $\textbf{z}_{t+1}$ to obtain $\textbf{pf}_{t+1}(m)$ on every integration node $m \in \{1,\dots,M\}$.
+(For GHLS, we interpolate the non-ZLB and ZLB policy functions separately.)
+\item Given the interpolated policy functions $\{\textbf{pf}(m)\}_{m=1}^M$, and integration nodes and weights provided by the Rouwenhorst method, approximate the expectation operators for the model.
+(For GHLS, use the interest rate array calculated from the interpolated policy functions to determine whether the model is at the ZLB at each node.
+We construct the aggregate policy functions accordingly, as in (\ref{eq:18}) and (\ref{eq:19}).)
+\item Solve for time $t+1$ variables from the expectation operators.
+Back out the policy functions $\textbf{pf}_{d}$ from the expectation operators and time $t+1$ variables.
+(For GHLS, we solve for the regime-indexed policy functions according to (\ref{eq:20})-(\ref{eq:24})).
+\end{enumerate}
+\item Repeat step 2 until the maximum distance between successive approximations of the policy functions is below $10^{-6}$. 
+\end{enumerate}
 
@@
 We use Euler equation errors to measure the accuracy of our solutions.
-To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method following Richter et al.
-(2014) to allow exogenous variables to have realizations between grid points.
+To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method following ART to allow exogenous variables to have realizations between grid points.
 The Euler equation errors are represented in absolute value of the errors in base 10 logarithms.
-An Euler equation error of -3 means the household makes an error equivalent to one per 1,000 consumption goods.
+An Euler equation error of -3 means the household makes an error equivalent to one per 1,000 consumption goods; i.e., an error of 0.1\% on average.
 
-  Richter et al.
-(2014) use Euler equation errors to measure the accuracy of their solutions.
-To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method to allow exogenous variables to be off the grid.
-The Euler equation errors are reported in absolute value of the errors in base 10 logarithms.
-A consumption Euler equation error of -3 means the household makes an error equal to one out of every 1,000 consumption goods.
+We simulate 10,000 periods of the model using the nonlinear solution with random shocks. For
+each period, we follow one iteration of step 2 of the algorithm outlined in Appendix B and then
+transform the residuals to Euler equation errors.
 
-\section{Results}
+	We considered adding a second measure of accuracy, a statistical measure from \hyperlink{Den}{\color{black}{Den Haan and Marcet (1994)}} based on a transformation of the Euler equation residuals to a chi-square distribution.
+However, it proved uninformative, as several runs of the test statistic were all in the extreme
+tails of the distribution.
 
-\subsection{Solution Times}
-\hyperlink{Table 2}{Table 2} reports the solution times for the Richter et al.
-(2013) and Gust et al.
-(2017) solution methods for the models with and without capital.
-The solution times were computed with multi-core processing using the Parallel Computing Toolbox.
-With MATLAB executable functions (MEX) provided by the companion Toolbox to Richter et al.
-(2013), we integrate Fortran in the interpolation steps of the algorithm.
-The solution times represent one run of each algorithm.
-The machine used to compute the solutions has two CPUs (at 2.30GHz), each with 16 cores.
-%Say something about the solution times%
-\begin{itemize}
-\item Gust et al. method slower, particularly on the model with capital. The differential blows up for the model with capital.
-\item The speed and speed differential is influenced by the parameterization, and appears to take more time on the boundary of convergence for each algorithm.
-\end{itemize}
+\section[Section 4]{Results \hypertarget{Section 4}{}}
+
 \begin{table}[H]
   \centering
+\captionsetup{justification=centering}
   \hypertarget{Table 2}
   \small
-    \setlength{\tabcolsep}{10pt}      
-  \begin{tabular}{l c c c c}
+    \setlength{\tabcolsep}{6pt}      
+  \begin{tabular}{l c c c c c c}
     \hline
-    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
-    & Iterations & Total Time & Iterations & Total time\\
+    & \multicolumn{3}{c}{Model without capital} & \multicolumn{3}{c}{Model with capital} \\
+    & Total nodes & Iterations & Total Time & Total Nodes & Iterations & Total time\\
     \hline
-  Richter et al. (2013) & 67 & 17.9s & 65 & 0h 15m 37.1s\\    
-  Gust et al. (2017) & 66 & 46s & 1170 &  5h 32m 48.6s\\
+  ART & 2401  & 67 & 17.9s & 78125 & 65 & 0h 15m 37.1s\\    
+  GHLS & 2401  & 66 & 46s & 78125 & 1170 &  5h 32m 48.6s\\
   \hline
@@
 
-\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital.
-\hyperlink{Table 3}{Table 3} reports the RMSE and mean \% error from linear policy functions.
-The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.
+\subsection{Solution Times}
+\hyperlink{Table 2}{Table 2} reports the solution times for the ART and
+GHLS solution methods for the models with and without capital. The solution times
+were computed with multi-core processing using the Parallel Computing Toolbox. With MATLAB
+executable functions (MEX) provided by the companion toolbox to \hyperlink{RTW}{\color{black}{Richter et al.
+(2014)}}, we implemented the interpolation steps of the algorithm in Fortran.
+The solution times represent one run
+of each algorithm. The machine used to compute the solutions has 32 total cores (two CPUs at 2.30GHz, each
+with 16 cores).
 
-\begin{itemize}
-\item ART is visually a lot smoother; matched with statistics
-  \item the Gust Et Al combined policy function si very similar to the non-ZLB policy function. All Gust Et Al policy functions have a kink corresponding to the ZLB. 
-  \item Percent error and RMSE error wise though, this is not too big of a difference?
-    \item say something about what the mean \% error and RMSE is
-  \end{itemize}
+The GHLS method is slower for both the model with and without capital. The speed
+differential blows up for the model with capital. The performance is somewhat contingent upon the
+parameterization. The GHLS method was faster with $\sigma_v = 0.002$, but we selected $\sigma_v = 0.0035$
+so that the ZLB constraint was better represented in the simulation. The GHLS solution
+algorithm handles a labor policy (consumption policy for model without capital) at and away from
+the ZLB. As a result, the solution algorithm requires two interpolation steps. In addition, the GHLS solution algorithm must determine at which nodes the state space is at the ZLB, and
+solve for time $t$ and $t + 1$ variables accordingly.
 
@@
     \centering
-    \includegraphics[scale=.6]{pfs3D_CAPITAL-eps-converted-to.pdf}%{pfs3D_CAPITAL.eps}
+\captionsetup{justification=centering}
+    \includegraphics[width=17.25cm,scale=1]{pfs3DCAP.pdf}
   \caption{Labor policy function for model with capital}    
@@
 
+\subsection{Policy Functions} \hyperlink{Figure 1}{Figure 1} shows the cross-section of the labor policy functions with the interest rate and risk premium for the model with capital.
+The black dots on the nodes of the
+graph represent labor values corresponding to the ZLB. The GHLS labor policy function is
+computed at and away from the ZLB, and combined later, so all three are shown in the figure. The
+GHLS combined policy function is very similar to the policy function away from the ZLB.
+
+Visually, the ART labor policy function is smoother. Labor hours smoothly
+increase as the interest rate falls and hits the ZLB. The GHLS labor policy function
+features a kink at the ZLB where labor rises dramatically.
+
 \begin{table}[H]
   \centering
+\captionsetup{justification=centering}
   \hypertarget{Table 3}
@@
     \hline
-    Richter et al. policy & 0.46545\% &0.0020137 consumption units & 0.19585\% & .0029035 labor units \\    
-  Gust et al. policy & 0.45556\% & 0.0019792 consumption units & 0.56142\% & 0.0076665 labor units \\
+    ART policy & 0.46545\% &0.0020137 $c$  units & 0.19585\% & .0029035 $l$ units \\    
+  GHLS policy & 0.45556\% & 0.0019792 $c$ units & 0.56142\% & 0.0076665 $l$ units \\
   \hline
 \end{tabular}
-  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). Gust et al. combined policy functions are reported.}
+  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). GHLS combined policy functions are reported.}
 \end{table}
+
+ \hyperlink{Table 3}{Table 3} reports the RMSE (root mean square error) and mean percent error from linear policy
+functions. The mean percent error is calculated as $1/M\sum_{i=1}^N[\textbf{pf.n}(i)-\hat{\textbf{n}}(i)]/\bar{n}$
+where $N$ is the
+number of periods, $\textbf{pf.n}$ is the labor policy function, $\hat{\textbf{n}}$ is the linear regression model of $\textbf{pf.n}$ fit to
+the state variables, and $\bar{n}$ is steady state labor. The corresponding results for the model without
+capital is reported in \hyperlink{Appendix C}{Appendix C}.
+
+The RMSE and the mean percent error indicate that the ART labor policy function is smoother and better fits a linear plane for the model with capital. For the model without
+capital, both functions are smooth, but the GHLS policy function slightly better fits a linear
+plane than the ART policy function.
+
+\begin{figure}[H]
+\hypertarget{Figure 2}  
+    \centering
+\captionsetup{justification=centering}
+    \includegraphics[width=16cm,scale=.8]{eeerrorsCAP.pdf}%{pfs3D_CAPITAL.eps}
+  \caption{Euler equation errors for model with capital}    
+  \end{figure}
 
@@
 
-\begin{itemize}
-\item Euler equations very comparable between algorithms
-\item Gust et al does slightly worse. Means are similar but max is higher.
-  \end{itemize}
+The Euler equation errors are very similar between solution algorithm, though the ART
+Euler equation errors are slightly more negative, and thus correspond to a smaller household error.
+The mean errors are similar, though the maximum error is considerably higher for the GHLS
+Euler equation error. The shapes of the errors are comparable.
 
-\begin{figure}[H]
-\hypertarget{Figure 2}  
-    \centering
-    \includegraphics[scale=1.5]{eeerrors_C.eps}%{pfs3D_CAPITAL.eps}
-  \caption{Euler equation errors for model with capital}    
-  \end{figure}
+\section[Section 5]{Conclusion \hypertarget{Section 5}{}}
 
-\section{Conclusion}
-% summarize results
-Opportunities for future work
-\begin{itemize}
-\item Chebyshev polynomials
-\item Smolyak grids
-  \item This might make solution method faster, so we could potentially increase the number of grid points and make it better than Richter et al
-  \end{itemize}
+During the Great Recession, the U.S.
+Federal Reserve lowered policy rates to zero, creating a kink in its policy rule, and calling into question traditional solution methods.
+Recent work has explored fully nonlinear models to represent the ZLB, but not much work has compared the performance of different solution methods.
+This paper analyzes the effect that different ways of representing the policy functions can have on a nonlinear solution algorithm.
+We use a method based on \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} to motivate directly approximating the policy functions and a method based on  \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} to motivate regime-indexing the policy functions.
+Although the regime-indexed policy functions were meant to be smoother and easier to compute, the GHLS method was slower and featured more of a non-linearity at the ZLB then the ART representation in the model with caiptal.
+The regime-indexed policy functions also yielded a solution that was less accurate in terms of Euler equation errors in the model with capital.
+
+Future work includes solving the GHLS solution method using Smolyak discretization methods with Chebyshev polynomials.
+We would expect this to speed up the solution algorithm and improve the accuracy of the solution.
+If this addition made the algorithm faster, we could also discretize the grid more finely to improve the accuracy of the solution and compare this to the ART method.
 
@@
   \noindent
-  \textbf{Medium-Scale Model} The detrended system includes (\ref{eq:1}),(\ref{eq:6}),(\ref{eq:15}),(\ref{eq:16}) and 
+  \textbf{Medium-Scale Model} The detrended system includes (\ref{eq:1}), (\ref{eq:6}), (\ref{eq:15}), (\ref{eq:16}) and 
 \begin{gather}
@@
 
-\noindent \textbf{Small-Scale Model} The detrended system includes (\ref{eq:1}),(\ref{eq:6}),(\ref{eq:15}),(\ref{eq:16})(\ref{eq:m1}),(\ref{eq:m2}),(\ref{eq:m3}), and 
+\noindent \textbf{Small-Scale Model} The detrended system includes (\ref{eq:1}), (\ref{eq:6}), (\ref{eq:15}), (\ref{eq:16}), (\ref{eq:m1}), (\ref{eq:m2}), (\ref{eq:m3}), and 
 \begin{gather}
@@
 \section{Nonlinear Solution Method}\hypertarget{Appendix B}
-The following discussion is based on Atkinson et al. (2019) and Richter and Throckmorton (2014). We express the detrended nonlinear system compactly as
+The following discussion is based on \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} and \hyperlink{RT}{\color{black}{Richter and Throckmorton (2014)}}.
+We express the detrended nonlinear system compactly as
 \begin{gather*}
@@
 
-We use the Markov chain method in Rouwenhorst (1995) to discretize the endogenous state variables, $s_t$, $g_t$, and $\varepsilon_{i,t}$ follwing Richter et al (2014).
-The bounds on $\tilde{c}_{t-1}, i^n_{t-1}, \tilde{k}_{t-1},$ and $\tilde{x}_{t-1}$ are set to $\pm 2.5\%, \pm 6\%, \pm 8\%, \pm 15\%$, respectively, following Atkinson et al.
-(2019).
+We use the Markov chain method in \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}} to discretize the endogenous state variables, $s_t$, $g_t$, and $\varepsilon_{i,t}$ following ART.
+The bounds on $\tilde{c}_{t-1}, i^n_{t-1}, \tilde{k}_{t-1},$ and $\tilde{x}_{t-1}$ are set to $\pm 2.5\%$, $\pm 6\%$, $\pm 8\%$, and $\pm 15\%$, respectively, following \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}.
 We discretize the states into 5 evenly-spaced points for the model with capital and 7 evenly-spaced points for the model without capital.
@@
 
-The vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$ ($\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), n_t(\textbf{z}_t), q_t(\textbf{z}_t), mc_t(\textbf{z}_t)]$ for the model with capital and $\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), \tilde{c}_t(\textbf{z}_t)]$.
-The policy functions are selected so that solving fr other variables in the nonlinear system is straightforwards.
+The vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$ ($\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), n_t(\textbf{z}_t), q_t(\textbf{z}_t), mc_t(\textbf{z}_t)]$ for the model with capital and $\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), \tilde{c}_t(\textbf{z}_t)]$ for the model without capital.
+For the GHRT policy functions, any variables directly dependent on the interest rate ($n_t$ for the model with capital and $\tilde{c}_t$ for the model without capital) are the result of computing regime-indexed policy functions using (\ref{eq:18}) and (\ref{eq:19}).
+The policy functions are selected so that solving for other variables in the nonlinear system is straightforward.
 
@@
   \item Use Sims's (2002) \texttt{gensys} algorithm to solve the log-linear model without the ZLB constraint and obtain conjectures for the policy functions $\textbf{pf}_0$.
-  \item On each node $d \in \{1,\dots,D\}$,% use fixed point iteration to find $\textbf{pf}_t(d)$ to satisfy $E[f(\cdot)|\textbf{z}_t(d), \vartheta] \approx 0$.
+(For GHLS, the initial guesses for $n_t^{normal}$ and $n_t^{ZLB}$ are set to the log-linear solution for $n_t$ from \texttt{gensys}).
+  \item On each node $d \in \{1,\dots,D\}$:% use fixed point iteration to find $\textbf{pf}_t(d)$ to satisfy $E[f(\cdot)|\textbf{z}_t(d), \vartheta] \approx 0$.
 Guess $\textbf{pf}_j(d) = \textbf{pf}_{j-1}(d)$ Then:
     \begin{enumerate}
-    \item Solve for all variables dated at time $t$, given $\textbf{pf}_t(d)$ and $\textbf{z}_t(d)$.
-    \item Linearly interpolate the policy functions $\textbf{pf}_{j-1}$, at the updated state variables $\textbf{z}_{t+1}(m)$, to obtain $\textbf{pf}_{t+1}(m)$ on every integration node, $m \in \{1,\dots,M\}$.
-    \item Given $\{\textbf{pf}_{t+1}(m)\}_{m=1}^M$, solve for the other elements of $\textbf{s}_{t+1}(m)$ and approximate the expectation operators %and back out the updated \textbf{pf}$_t(d)$.
+    \item ART: Solve for all variables dated at time $t$, given $\textbf{pf}_t(d)$ and $\textbf{z}_t(d)$. \\
+GHLS: Solve for $i_t$. If $i_t > 1$, solve for all time $t$ variables with $n_t^{normal}$. Otherwise, solve for all time $t$ variables with $n_t^{ZLB}$. 
+    \item ART: Linearly interpolate the policy functions $\textbf{pf}_{j-1}$, at the updated state variables $\textbf{z}_{t+1}(m)$, to obtain $\textbf{pf}_{t+1}(m)$ on every integration node, $m \in \{1,\dots,M\}$.\\
+GHLS: Linearly interpolate $n_t^{normal}$ and $n_t^{ZLB}$ in separate steps with the remainder of the policy functions in $\textbf{pf}_{j-1}$.
+    \item ART: Given $\{\textbf{pf}_{t+1}(m)\}_{m=1}^M$, solve for the other elements of $\textbf{s}_{t+1}(m)$ and approximate the expectation operators
       \begin{gather*}
@@
       \end{gather*}
-      \item Solve for $\textbf{pf}_t(d)$ from the expectation operators and $\textbf{s}_{t+1}(m)$. Set $\textbf{pf}_j(d) = \textbf{pf}_t(d)$.
+GHLS: Solve for $\{i_t(m)\}_{m=1}^M$ using the interpolated policy functions and time $t$ variables.
+If the value of $\{i_t(m)\}_{m=1}^M$ on node $d$ is greater than 1, assign $\{n_t(m)\}_{m=1}^M$ on node $d$ to the corresponding value in $\{n_t^{normal}(m)\}_{m=1}^M$, otherwise assign $\{n_t(m)\}_{m=1}^M$ on node $d$ to the corresponding value in $\{n_t^{ZLB}(m)\}_{m=1}^M$.
+Solve for the other elements in $\textbf{s}_{t+1}$ and approximate the expectation operators.
+      \item ART: Solve for $\textbf{pf}_t(d)$ from the expectation operators and $\textbf{s}_{t+1}(m)$. Set $\textbf{pf}_j(d) = \textbf{pf}_t(d)$.\\
+GHLS: Using the expectation operators, solve for the $n_t(d)$ policy in the style of (\ref{eq:20}) and the $n_t^{ZLB}$ policy in the style of (\ref{eq:21}).
+Solve for the rest of the policy functions in $\textbf{pf}_t(d)$.
     \end{enumerate}
@@
 
+%The GHLS solution is the same as above, except $\textbf{pf}_t(d) \equiv  [\tilde{\pi}^{gap}_t(\textbf{z}_t), n_t(\textbf{z}_t),n_t^{ZLB}(\textbf{z}_t), q_t(\textbf{z}_t), mc_t(\textbf{z}_t)]$ for the model with capital and $\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), \tilde{c}_t(\textbf{z}_t),\tilde{c}_t^{ZLB}(\textbf{z}_t)]$ for the model without capital where the policy functions away and at the ZLB are computed according to (\ref{eq:18}) and (\ref{eq:19}).
+The initial guess for $n_t^{ZLB}$ is set to the log-linear solution for $n_t$ from \texttt{gensys}.
+For step 2, in addition to what is in the ART solution method,
+%\begin{enumerate}
+%\item[(a)] Solve for $i_t$. If $i_t > 1$, solve for all time $t$ variables with $n_t$. Otherwise, solve for all time $t$ variables with $n_t^{ZLB}$. 
+%\item[(b)] Linearly interpolate both $n_t$ and $n_t^{ZLB}$ separately, as well as the other policy functions in $\textbf{pf}_{j-1}$ atF the updated state variables. 
+%\item[(c)] Solve for $\textbf{i}_t$ using the interpolated policy functions and time $t$ variables.
+If the node $\textbf{i}_t(d) > 1$, assign $\textbf{n}_t^{combined}(d)$ to the value in $\textbf{n}_t(d)$, otherwise $\textbf{n}_t^{combined}(d)$ to the value in $\textbf{n}_t^{ZLB}(d)$.
+Solve for the other elements in $\textbf{s}_{t+1}$ and approximate the expectation operators.
+%\item[(d)] Using the expectation operators, solve for the $n_t(d)$ policy in the style of (\ref{eq:20}) and the $n_t^{ZLB}$ policy in the style of (\ref{eq:21}).
+Solve for the rest of the policy functions in $\textbf{pf}_t(d)$.
+%\end{enumerate}
+
 \section{Results for model without capital} \hypertarget{Appendix C}
 The following reports the corresponding results for the model wtihout capital.
-\hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and risk premium.
-\hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the consumption euler Equation and the price Phillips curve.
 
@@
     \centering
-    \includegraphics[scale=.6]{pfs3D.eps}
+\captionsetup{justification=centering}
+    \includegraphics[width=16cm,scale=.9]{pfs3D.pdf}
   \caption{Consumption policy function for model without capital}    
@@
 
-\begin{itemize}
-\item Smoother in general
-\item Very close between ART and GustEtAl
-  \end{itemize}
+\hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and
+risk premium. The policy functions are all fairly smooth and only have a slight nonlinearity at the
+ZLB. The average percent error of the consumption policy functions from a linear plane is slightly
+lower for the GHLS policy functions.
 
@@
     \centering
-    \includegraphics[scale=1.5]{eeerrors.eps}
+\captionsetup{justification=centering}
+    \includegraphics[scale=1]{eeerrors.pdf}
   \caption{Euler equation errors for model without capital}    
@@
 
-\begin{itemize}
-\item Bimodality more distinct in Gust et al policy functions
-\item Very similar with regards to mean and max; Gust et al does slightly better in consumption Euler
-\end{itemize}
+\hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10
+logarithms for the consumption Euler equation and the price Phillips curve. The mean and maximum Euler equations are comparable between algorithms; the GHLS solution does slightly
+better for the consumption Euler equation and the ART solution does slightly better for the
+firm pricing equation.
 
-\begin{comment}
-\subsection{ART Model with capital}
-\noindent Preferences:
-\begin{gather*}
-  E_0\textstyle\sum_{t=0}^\infty\beta^t [\log(c_t-hc^a_{t-1})-\chi n_t^{1+\eta}/(1+\eta)]
-\end{gather*}
+\section*{References}
 
-\noindent Budget Constraint:
-\begin{gather*}
-  c_t+x_t+b_t/(i_ts_t)=w_tn_t+r_t^kk_{t-1}+b_{t-1}/\pi_t+d_t\\
-  k_t = (1-\delta)k_{t-1} + x_t(1 - \nu(x^g_t-1)^2/2)
-\end{gather*}
+\setlength\parindent{0pt}
 
-\setcounter{equation}{0}
-\noindent Equilibrium system:
-\small\begin{gather}
-y_t = k_{t-1}^\alpha(z_t n_t)^{1-\alpha}\\ %%%
-r_t^k = \alpha mc_ty_t/k_{t-1}\\
-w_t = (1-\alpha)mc_ty_t/n_t\\
-%w_t^g = \pi_tw_t(\bar{\pi}gw_{t-1})\\
-y_t^{gdp} = [1 - \varphi(\pi_t^{gap}-1)^2/2]y_t \\
-y^g_t = y^{gdp}_t/(\bar{g}y^{gdp}_{t-1})\\
-i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{g}_{t})^{\phi_y})^{1-\rho_i}\exp(mp_t)\\
-i_t=\max\{1,i_t^n\}\\
-\lambda_t = c_t - hc^a_{t-1} \\
-w_t = \chi n_t^\eta \lambda_t\\
-c_t + x_t = y_t^{gdp}\\
-x_t^g = x_t/(\bar{g}x_{t-1})\\
-k_t = (1-\delta)k_{t-1}+x_t(1-\nu(x_t^g-1)^2/2) \\%%%
-1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}))]\\
-q_t = \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})]\\
-1 = q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] + \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)]\\
-\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
-g_t = \bar{g} + \sigma_g\varepsilon_{g,t}\\
-s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_s\varepsilon_{s,t}\\
-mp_t = \sigma_i\varepsilon_{i,t}\\
-  z_t=g_tz_{t-1}
-\end{gather}\normalsize
-Variables: $\{c,n,x,k,y^{gdp},y,x^g,y^g,w,r^k,\pi,i,i^n,q,mc,\lambda,g,s,mp,z\}$\\
+\hypertarget{Aruoba} \hangindent=0.5cm \textsc{Aruoba, S., P. Cuba-Borda, and F. Schorfheide (2018):}  “Macroeconomic Dynamics
+Near the ZLB: A Tale of Two Countries,”  \textit{The Review of Economic Studies}, 85, 87–118.
 
-\setcounter{equation}{0}
-\noindent De-trended Equilibrium System:
-\small\begin{gather}
-\tilde{y}_t= (\tilde{k}_{t-1}/g_t)^\alpha n_t^{1-\alpha}\\
-r^k_t = \alpha mc_t g_t \tilde{y}_t/\tilde{k}_{t-1}\\
-\tilde{w}_t = (1-\alpha)mc_t\tilde{y}_t/n_t\\
-\tilde{y}^{gdp}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
-y^g_t = g_t\tilde{y}^{gdp}_t/(\bar{g}\tilde{y}^{gdp}_{t-1})\\
-i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi}(y^g_t)^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t})\\
-i_t=\max\{1,i_t^n\}\\
-\tilde{\lambda}_t = \tilde{c}_t\ - h\tilde{c}_{t-1}/g_t\\
-\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
-\tilde{c}_t + \tilde{x}_t = \tilde{y}^{gdp}_t\\
-x^g_t = g_t\tilde{x}_t/(\bar{g}\tilde{x}_{t-1})\\
-\tilde{k}_t = (1-\delta)(\tilde{k}_{t-1}/g_t) + \tilde{x}_t(1-\nu(x^g_t-1)^2/2)\\%%%
-  1 = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
-q_t = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(r^k_{t+1} + (1-\delta)q_{t+1})/g_{t+1}]\\
-1 = q_t[1 - \nu(x^g_t-1)^2/2 - \nu(x^g_t-1)x^g_t] + \nu\beta\bar{g}E_t[q_{t+1}(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)/g_{t+1}]\\
-  \varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1}) (\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
-  g_t= \bar{g} + \sigma_g\varepsilon_{g,t} \\
-  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_s\varepsilon_{s,t}\\
-  mp_t = \sigma_i\varepsilon_{i,t}
-\end{gather}
-Variables:$\{\tilde{c},\tilde{n},\tilde{x},\tilde{k},\tilde{y^{gdp}},\tilde{y},x^g,y^g,\tilde{w},r^k,\pi,i,i^n,q,mc,\tilde{\lambda},g,s,mp\}$\\
+\hypertarget{Atkinson}\hangindent=0.5cm \textsc{Atkinson, T., A. W. Richter, N. A. Throckmorton (2019):} “The Accuracy of Linear and Nonlinear Estimation in the
+Presence of the Zero Lower Bound,” FRB Dallas Working Paper 1705, revised February 2019.
 
-\setcounter{equation}{0}
-\noindent Log-linear Equilibrium System:
-\begin{gather}
-  \hat{y}_t/\bar{y} = \alpha(\hat{k}_{t-1}/\bar{k} - \hat{g}_t/\bar{g}) + (1-\alpha)\hat{n}_t/\bar{n}\\
-\hat{r}^k_t/\bar{r}^k = \hat{mc}_t/\bar{mc} + \hat{g}_t/\bar{g} + \hat{y}_t/\bar{y} - \hat{k}_{t-1}/\bar{k}\\
-\hat{w}_t/\bar{w} = \hat{mc}_t/\bar{mc} + \hat{y}_t/\bar{y} - \hat{n}_t/\bar{n}\\
-\hat{y}_t^{gdp} = \hat{y}_t\\
-\hat{y}^g_t = \hat{g}_t/\bar{g} + \hat{y}^{gdp}_t/\bar{y}^{gdp} - \hat{y}^{gdp}_{t-1}/\bar{y}^{gdp}\\
-  \hat{i}_t/\bar{i} = \rho_i\hat{i}_{t-1}/\bar{i} + (1-\rho_i)(\phi_\pi\hat{\pi}^{gap}_t+ \phi_y\hat{y}^g_t)+\hat{mp}_t \\
-  \hat{\imath}_t = \hat{\imath}_t^n\\
-  \hat{\lambda}_t = \hat{c}_t - (h/\bar{g})\hat{c}_{t-1} + (h\bar{c}/\bar{g}^2)\hat{g}_t\\
-  \hat{c}_t + \hat{x}_t = \hat{y}^{gdp}_t\\
-  \hat{x}^g_t = \hat{g}_t/\bar{g} + \hat{x}_t/\bar{x} - \hat{x}_{t-1}/\bar{x}\\
-  \hat{k}_t = ((1-\delta)/\bar{g})[\hat{k}_{t-1}-(\bar{k}/\bar{g})\hat{g}_t] + \hat{x}_t\\
-  \hat{\lambda}_t/\bar{\lambda} + \hat{\imath}_t/\bar{i} + \hat{s}_t/\bar{s}  = E_t\hat{\lambda}_{t+1}/\bar{\lambda}+E_t\hat{g}_{t+1}/\bar{g}+E_t\hat{\pi}_{t+1}/\bar{\pi} \\
-  \hat{q}_t = \hat{\lambda}_t/\bar{\lambda} - E_t\hat{\lambda}_{t+1}/\bar{\lambda} + (\beta/\bar{g})[E_t\hat{r}^k_{t+1} + (1-\delta)E_t\hat{q}_{t+1}] - E_t\hat{g}_{t+1}/\bar{g}\\
-  \hat{x}^g_t = \hat{q}_t + \beta E_t\hat{x}^g_{t+1}\\
-  \varphi\hat{\pi}^{gap}_t = \theta\hat{mc}_t+\beta\varphi E_t\hat{\pi}^{gap}_{t+1}\\
-  \hat{g}_t = \sigma_g\varepsilon_{g,t}\\
-  \hat{s}_t = \rho_s\hat{s}_{t-1} + \sigma_s\varepsilon_{s,t}\\
-  \hat{mp}_t = \sigma_i\varepsilon_{i,t}
-\end{gather}
-Variables:$\{\hat{c},\hat{n},\hat{x},\hat{k},\hat{y^{gdp}},\hat{y},\hat{x^g},\hat{y^g},\hat{w},\hat{r^k},\hat{\pi},\hat{i},\hat{i^n},\hat{q},\hat{\lambda},\hat{g},\hat{s},\hat{mp}\}$\\
-\begin{comment}
-\pagebreak
+\hypertarget{Christiano}\hangindent=0.5cm \textsc{Christiano, L. J., and J. D. M. Fisher (2000): } “Algorithms for Solving Dynamic Models with Occasionally Binding
+Constraints,” \textit{Journal of Economic Dynamics and Control}, 24 (8), 1179–1232.
 
-\subsection{ART Model pre-capital}
-\noindent Preferences:
-\begin{gather*}
-  E_0\textstyle\sum_{t=0}^\infty\beta^t [\log(c_t-hc^a_{t-1})-\chi n_t^{1+\eta}/(1+\eta)]
-\end{gather*}
+\hypertarget{Fernald}\hangindent=0.5cm \textsc{Fernald, J.
+G.
+(2012):}   “A Quarterly, Utilization-Adjusted Series on Total Factor Productivity,” Federal Reserve Bank of San Francisco Working Paper 2012-19.
 
-\noindent Budget Constraint:
-\begin{gather*}
-  c_t+b_t/(i_ts_t)=w_tn_t+b_{t-1}/\pi_t+d_t
-\end{gather*}
+\hypertarget{Fernandez}\hangindent=0.5cm \textsc{Ferna\'ndez-Villaverde, J., G. Gordon, P. Guerro\'n-Quintana, and J. F.
+Rubio-Rami\'rez (2015):}  “Nonlinear Adventures at the Zero Lower Bound,” \textit{Journal of
+Economic Dynamics and Control}, 57, 182–204.
 
-\setcounter{equation}{0}
-\noindent Equilibrium system (11 equations):
-\small\begin{gather}
-c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
-i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(c_t/(\bar{g}c_{t-1}))^{\phi_c})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
-i_t=\max\{1,i_t^n\}\\
-\lambda_t = c_t - hc^a_{t-1} \\
-w_t = \chi n_t^\eta \lambda_t\\
-1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}))]\\
-\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
-  y_t=z_t n_t\\  
-  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
-  s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t\\
-  z_t=g_tz_{t-1}
-\end{gather}\normalsize
-Variables: $\{c,i^n,i,\lambda,w,\pi^{gap},y,n,g,s,z\}$\\
+\hypertarget{Guerrieri}\hangindent=0.5cm\textsc{Guerrieri, L. and M. Iacoviello (2015):} “OccBin: A toolkit for solving dynamic models with occasionally binding
+constraints easily,”  \textit{Journal of Monetary Economics}, 70, 22–38.
 
-\setcounter{equation}{0}
-\noindent De-trended Equilibrium System (10 equations):
-\small\begin{gather}
-\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
-i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi}(g_t\tilde{c}_t/(\bar{g}\tilde{c}_{t-1})^{\phi_c})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
-i_t=\max\{1,i_t^n\}\\
-\tilde{\lambda}_t = \tilde{c}_t\ - h\tilde{c}_{t-1}/g_t\\
-\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
-  1 = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
-  \varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1-\theta + \theta\tilde{w}_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1}) (\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
-  \tilde{y}_t= n_t\\  
-  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
-  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t
-\end{gather}
-Variables: $\{\tilde{c},i^n,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{y},n,k,g,s\}$\\
+\hypertarget{Gust}\hangindent=0.5cm\textsc{Gust, C., E. Herbst, D. Lo\'pez-Salido, and M. E. Smith (2017):} “The Empirical Implications of the Interest-Rate
+Lower Bound,”  \textit{American Economic Review}, 107, 1971–2006.
 
-\setcounter{equation}{0}
-\noindent Log-linear Equilibrium System:
-\begin{gather}
-  \hat{c}_t = \hat{y}_t\\
-  \hat{\imath}_t^n = \rho_i\hat{\imath}^n_{t-1} + (1-\rho_i)\phi_\pi\hat{\pi}_t+ (1-\rho_i)\phi_c(\hat{g}+\hat{c}-\hat{c}_{t-1})+\sigma_\nu\nu_t \\
-  \hat{\imath}_t = \hat{\imath}_t^n\\
-  (1-h/g)\hat{\lambda}_t = \hat{c}_t + (h/g)(\hat{g} - \hat{c}_{t-1})\\
-  \hat{w}_t =  \eta\hat{n}_t + \hat{\lambda}_t\\
-  \hat{\lambda}_t + \hat{\imath}_t + s_t  = E_t\hat{\lambda}_{t+1}+E_t\hat{\pi}_{t+1} \\
-  \varphi\hat{\pi}_t = (\theta-1)\hat{w}_t+\beta\varphi E_t\hat{\pi}_{t+1}\\
-  \hat{y}_t = \hat{n}_t 
-\end{gather}
-\pagebreak
-\setcounter{equation}{0}
-\subsection{Gust Et Al Model}
-\noindent Equilibrium system (13 equations):
-\small\begin{gather}
-\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
-i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
-i_t=\max\{1,i_t^n\}\\
-1/\lambda_t =  \beta E_t[(1/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
-\lambda_t = c_t \\
-c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
-w_t = \chi n_t^\eta \lambda_t\\
-  y_t=z_t n_t\\  
-  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
-  s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t\\
-  z_t=g_tz_{t-1}
-\end{gather}\normalsize
-Variables: $\{c,i^n,i,\lambda,w,\pi^{gap},V_{\lambda},y,V_{\pi},n,g,s,z\}$\\
+\hypertarget{Judd1} \hangindent=0.5cm \textsc{Judd, K.
+L., Maliar, L.
+and Maliar, S.
+(2010)}   “A Cluster-Grid Projection Method: Solving Problems with High Dimensionality” \textit{Computational Economics}, NBER Working Paper, 15965.
 
-\setcounter{equation}{0}
-\noindent De-trended Equilibrium System (12 equations):
-\small\begin{gather}
-\varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1 - \theta + \theta\tilde{w}_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(\pi^{gap}_{t+1}-1)\pi^{gap}_{t+1}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
-i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
-i_t=\max\{1,i_t^n\}\\
-1/\tilde{\lambda}_t = \beta E_t[(1/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi^{gap}_{t+1}g_{t+1}))]\\%
-\tilde{\lambda}_t = \tilde{c}_t\\
-\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
-\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
-  \tilde{y}_t= n_t\\  
-  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
-  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t
-\end{gather}
-Variables: $\{\tilde{c},i^n,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{V}_{\lambda},\tilde{y},\tilde{V}_{\pi},n,g,s\}$\\
+\hypertarget{Judd2}\hangindent=0.5cm\textsc{Judd, K. L., L. Maliar, S. Maliar, and R. Valero (2014):}  “Smolyak Method for Solving Dynamic Economic Models:
+Lagrange Interpolation, Anisotropic Grid and Adaptive Domain,”  \textit{Journal of Economic Dynamics and Control}, 44, 92–123.
 
-\setcounter{equation}{0}
-\noindent Log-linear Equilibrium System:
-\begin{gather}
-  \varphi\hat{\pi}_t = (\theta-1)\hat{w}_t+\beta\varphi E_t\hat{\pi}_{t+1}\\
-  \hat{\imath}_t^n = \rho_i\hat{\imath}^n_{t-1} + (1-\rho_i)\phi_\pi\hat{\pi}_t+\sigma_\nu\nu_t \\
-  \hat{\imath}_t = \hat{\imath}_t^n\\
-    -\hat{\lambda}_t = \hat{\imath}_t + s_t - E_t\hat{\lambda}_{t+1} - E_t\hat{\pi}_{t+1} \\
-  \hat{\lambda}_t = \hat{c}_t \\
-  \hat{c}_t = \hat{y}_t\\
-  \hat{w}_t =  \eta\hat{n}_t + \hat{\lambda}_t\\
-  \hat{y}_t = \hat{n}_t
-\end{gather}
+\hypertarget{Den}\hangindent=0.5cm\textsc{Den Haan, W. J. and Marcet A. (1994):}  “Accuracy in Simulations,"  \textit{Review of Economic Studies}, 61(1), 3-17.
 
-\setcounter{equation}{0}
-\noindent Gust et al Indicator Functions\\
-\begin{gather}
-  c_{t+1,1} = \beta E_t[\lambda_t(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
-  c_{t+1,2} = \beta E_t[\lambda_t(s_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\  
-\end{gather}
-for $k=1,2$ where $k=1$ corresponds to the non-ZLB regime and $k=2$ corresponds to the ZLB regime.
-\begin{gather}
-c_{t} = c_{t,1}I + c_{t,2}(1-I) 
-\end{gather}
-for $j=1,2$ and where $I$ is defined by:
-$$
-\begin{cases}
-  I = 1 & \text{ if } i > 1\\
-  I = 0 & \text{ otherwise.}
-\end{cases}
-$$
-%We use the functions, $V_l$, to determine the decisions rule though we do not approximate $V_l$ directly, because they inherit a kink associated with the ZLB constraint.
-Instead, we approximate functions, $V_{l,i}$, that are smoother and easier to approximate by specifying:
-%\begin{gather}
-%V_l = V_{l,1}I + V_{l,2}(1-I) 
-%\end{gather}
-%for $l \in \{\lambda, \pi\}$ and $j=1,2$ and where $I$ is defined by:
-%\begin{gather}
-%  I = 1 \text{ if } i > 1\\
-%  \text{  } = 0 \text{ otherwise}
-%\end{gather}
-%In the above, $i = \max(1,i^n)$ where $i^n$ denotes the value of the notional rate derived from evaluating the functions $V_{l,1}$ and using (2).
-(For each variable, we use $j=1$ to denote the function associated with the regime with a positive nominal interest rate and $j=2$ to denote the function associated with the ZLB regime.
-\\
-%Because the functions, $V_l$ depend directly on the nominal interest rate, we expect then to have a kink or non-differentiability.
-By contrast, the counterpart functions, $V_{l,j}$, that are indexed by the interest-rate regime do not depend on the current indicator function and thus are more likely to be smooth.
-\\
-%Specifically, $V_{\pi,1}$ and $V_{\pi,2}$ are both described by (8) because the nominal interest rate does not appear in that equation. $V_{\lambda,1}$ is described by (6), but for the ZLB regime:
-%\begin{gather}
-%V_{\lambda,t,2} =  \beta E_t[(1/\lambda_{t+1})(s_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\  
-%\end{gather}
-%where $i_t$ is replaced by 1.
-\end{comment}
+\hypertarget{Peterman}\hangindent=0.5cm \textsc{Peterman, W. B. (2016):}  “Reconciling Micro and Macro Estimates of the Frisch Labor Supply
+Elasticity,” \textit{Economic Inquiry}, 54, 100–120.
+
+\hypertarget{Plante}\hangindent=0.5cm\textsc{Plante, M., A. W. Richter, and N. A. Throckmorton (2018):}  “The Zero Lower Bound and Endogenous Uncertainty,” \textit{Economic Journal}, forthcoming.
+\hypertarget{RT}\hangindent=0.5cm \textsc{Richter, A. W. and N. A. Throckmorton (2016):}  “Is Rotemberg Pricing Justified by Macro Data?” \textit{Economics Letters}, 149, 44–48.
+
+\hypertarget{RWT}\hangindent=0.5cm\textsc{Richter, A.
+W., N.
+A.
+Throckmorton, and T.
+B.
+Walker (2014):}  “Accuracy, Speed and Robustness of Policy Function Iteration,” \textit{Computational Economics}, 44, 445–476.
+
+\hypertarget{Rotemberg}\hangindent=0.5cm \textsc{Rotemberg, J. J. (1982):} “Sticky Prices in the United States,” \textit{Journal of Political Economy}, 90, 1187–1211.
+
+\hypertarget{Rouwenhorst}\hangindent=0.5cm \textsc{Rouwenhorst, K. G. (1995):}  “Asset Pricing Implications of Equilibrium Business Cycle
+Models,” in \textit{Frontiers of Business Cycle Research}, ed. by T. F. Cooley, Princeton, NJ: Princeton
+University Press, 294–330.
+
+\hypertarget{Sims}\hangindent=0.5cm \textsc{Sims, C. A. (2002):}  “Solving Linear Rational Expectations Models,” \textit{Computational Economics}, 20, 1–20.
+
+\hypertarget{Smolyak}\hangindent=0.5cm\textsc{Smolyak, S.
+(1963):} “Quadrature and interpolation formulas for tensor products of certain classes of functions,” \textit{Dokl.
+Akad.
+Nauk}, 148, 1042-1045.
+
+%\hangindent=0.5cm\textsc{Aruoba, S.
+B., J.
+Fernandez-Villaverde, J.
+F.
+Rubio-Ramirez (2006):} “Comparing solution methods for dynamic equilibrium economies,” \textit{Journal of Economic Dynamics and Control}, 30, 2477-2508.
+%\hangindent=0.5cm
+
 \end{document}
-
-\documentclass[12pt, final]{article}
-\usepackage{color}
-\usepackage{times}
-\usepackage{amssymb,amsmath,amsthm}
-\usepackage{dsfont}
-\usepackage{graphicx}
-\usepackage{enumerate}
-\usepackage{enumitem}
-\usepackage[paperwidth=8.5in,left=1.0in,right=1.0in,top=1.0in,bottom=1.0in,paperheight=11.0in]{geometry}
-\usepackage[labelsep=colon,singlelinecheck=false,footnotesize]{caption}
-\usepackage{fancyhdr}
-\usepackage{float}
-\usepackage{booktabs}
-\usepackage[sort&compress]{natbib}
-\usepackage{subfig}
-\usepackage{titlesec}
-\usepackage[breaklinks]{hyperref}
-\hypersetup{pdfdisplaydoctitle=true,bookmarksnumbered=true,colorlinks=true,citecolor=black,linkcolor=darkblue,urlcolor=darkred,pdfstartview=FitH,pdfpagemode=UseNone}
-\usepackage[hyphenbreaks]{breakurl}
-\usepackage{accents}
-\newcommand{\ubar}[1]{\underaccent{\bar}{#1}}
-
-%Define Color Names
-\definecolor{Gray}{rgb}{0.65,0.65,0.65}
-\definecolor{darkblue}{rgb}{0,0,0.55}
-\definecolor{darkred}{rgb}{0.5,0,0}
-
-%Section Headings
-\newcommand\Bheadfont{\fontsize{14pt}{\baselineskip}\selectfont}
-\titleformat{\section}[hang]{\normalfont\sc\color{darkblue}\Bheadfont}{\thesection\hskip0.618em}{0em}{}
-\titlespacing*{\section}{0pt}{15pt plus 2pt minus 2pt}{9pt plus 2pt minus 2pt}
-\titleformat{\subsection}[runin]{\normalfont\sc\color{darkblue}} {\thesubsection\hskip0.618em}{0em}{}
-\titlespacing*{\subsection}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
-\titleformat{\subsubsection}[runin]{\normalfont\sc\color{darkblue}} {\thesubsubsection\hskip0.618em}{0em}{}
-\titlespacing*{\subsubsection}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
-\titleformat{\paragraph}[runin]{\bfseries}{\theparagraph\hskip0.618em}{0em}{}
-\titlespacing*{\paragraph}{0pt}{13pt plus 2pt minus 2pt}{13pt plus 2pt minus 2pt}
-
-\begin{document}
-
-\section{Equilibrium System}
-
-\noindent Preferences:
-\begin{gather*}
-  E_0\textstyle\sum_{t=0}^\infty\beta^t [\log(c_t)-\chi n_t^{1+\eta}/(1+\eta)]
-\end{gather*}
-
-\noindent Budget Constraint:
-\begin{gather*}
-  c_t+b_t/(i_ts_t)=w_tn_t+b_{t-1}/\pi_t+d_t
-\end{gather*}
-
-\setcounter{equation}{0}
-\subsection{ART Model}
-\noindent Equilibrium system (11 equations):
-\small\begin{gather}
-c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
-i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
-i_t=\max\{1,i_t^*\}\\
-\lambda_t = c_t \\
-w_t = \chi n_t^\eta \lambda_t\\
-1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
-\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
-  y_t=z_t n_t\\  
-  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
-  s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t\\
-  z_t=g_tz_{t-1}
-\end{gather}\normalsize
-Variables: $\{c,i^*,i,\lambda,w,\pi^{gap},y,n,g,s,z\}$\\
-
-\setcounter{equation}{0}
-\noindent De-trended Equilibrium System (10 equations):
-\small\begin{gather}
-\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
-i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
-i_t=\max\{1,i_t^*\}\\
-\tilde{\lambda}_t = \tilde{c}_t\\
-\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
-  1 = \beta E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
-  \varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1-\theta + \theta\tilde{w}_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1}) (\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
-  \tilde{y}_t= n_t\\  
-  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
-  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t
-\end{gather}
-Variables: $\{\tilde{c},i^*,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{y},n,g,s\}$\\
-
-\setcounter{equation}{0}
-\noindent Log-linear Equilibrium System:
-\begin{gather}
-  \hat{c}_t = \hat{y}_t\\
-  \hat{\imath}_t^n = \rho_i\hat{\imath}^n_{t-1} + (1-\rho_i)\phi_\pi\hat{\pi}_t+\sigma_\nu\nu_t \\
-  \hat{\imath}_t = \hat{\imath}_t^n\\
-  \hat{\lambda}_t = \hat{c}_t \\
-  \hat{w}_t =  \eta\hat{n}_t + \hat{\lambda}_t\\
-  \hat{\lambda}_t + \hat{\imath}_t + s_t  = E_t\hat{\lambda}_{t+1}+E_t\hat{\pi}_{t+1} \\
-  \varphi\hat{\pi}_t = (\theta-1)\hat{w}_t+\beta\varphi E_t\hat{\pi}_{t+1}\\
-  \hat{y}_t = \hat{n}_t 
-\end{gather}
-\pagebreak
-\setcounter{equation}{0}
-\subsection{Gust Et Al Model}
-\noindent Equilibrium system (13 equations):
-\small\begin{gather}
-\varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta w_t/z_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)]\\
-i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
-i_t=\max\{1,i_t^*\}\\
-1/\lambda_t =  \beta E_t[(1/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
-\lambda_t = c_t \\
-c_t = [1-\varphi(\pi_t^{gap}-1)^2/2]y_t\\
-w_t = \chi n_t^\eta \lambda_t\\
-  y_t=z_t n_t\\  
-  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
-  s_t=(1-\rho_s)\bar{s}+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t\\
-  z_t=g_tz_{t-1}
-\end{gather}\normalsize
-Variables: $\{c,i^*,i,\lambda,w,\pi^{gap},V_{\lambda},y,V_{\pi},n,g,s,z\}$\\
-
-\setcounter{equation}{0}
-\noindent De-trended Equilibrium System (12 equations):
-\small\begin{gather}
-\varphi(\pi_t^{gap}-1){\pi}_t^{gap} = 1 - \theta + \theta\tilde{w}_t + \beta\varphi E_t[(\tilde{\lambda}_t/\tilde{\lambda}_{t+1})(\pi^{gap}_{t+1}-1)\pi^{gap}_{t+1}(\tilde{y}_{t+1}/\tilde{y}_t)]\\
-i_t^*=(i^*_{t-1})^{\rho_i}(\bar{\imath}(\pi_t^{gap})^{\phi_\pi})^{1-\rho_i}\exp(\sigma_\nu\nu_t)\\
-i_t=\max\{1,i_t^*\}\\
-1/\tilde{\lambda}_t = \beta E_t[(1/\tilde{\lambda}_{t+1})(s_ti_t/(\bar{\pi}\pi^{gap}_{t+1}g_{t+1}))]\\%
-\tilde{\lambda}_t = \tilde{c}_t\\
-\tilde{c}_t = [1-\varphi(\pi_t^{gap} - 1)^2/2]\tilde{y}_t\\
-\tilde{w}_t = \chi n_t^\eta \tilde{\lambda}_t  \\
-  \tilde{y}_t= n_t\\  
-  g_t= (1-\rho_g)\bar{g}+\rho_gg_{t-1} + \sigma_\varepsilon\varepsilon_t \\
-  s_t=(1-\rho_s)s_t+\rho_ss_{t-1} + \sigma_\upsilon\upsilon_t
-\end{gather}
-Variables: $\{\tilde{c},i^*,i,\tilde{\lambda},\tilde{w},\pi^{gap},\tilde{V}_{\lambda},\tilde{y},\tilde{V}_{\pi},n,g,s\}$\\
-
-\setcounter{equation}{0}
-\noindent Log-linear Equilibrium System:
-\begin{gather}
-  \varphi\hat{\pi}_t = (\theta-1)\hat{w}_t+\beta\varphi E_t\hat{\pi}_{t+1}\\
-  \hat{\imath}_t^n = \rho_i\hat{\imath}^n_{t-1} + (1-\rho_i)\phi_\pi\hat{\pi}_t+\sigma_\nu\nu_t \\
-  \hat{\imath}_t = \hat{\imath}_t^n\\
-    -\hat{\lambda}_t = \hat{\imath}_t + s_t - E_t\hat{\lambda}_{t+1} - E_t\hat{\pi}_{t+1} \\
-  \hat{\lambda}_t = \hat{c}_t \\
-  \hat{c}_t = \hat{y}_t\\
-  \hat{w}_t =  \eta\hat{n}_t + \hat{\lambda}_t\\
-  \hat{y}_t = \hat{n}_t
-\end{gather}
-
-\setcounter{equation}{0}
-\noindent Gust et al Indicator Functions\\
-\begin{gather}
-  c_{t+1,1} = \beta E_t[\lambda_t(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\
-  c_{t+1,2} = \beta E_t[\lambda_t(s_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\  
-\end{gather}
-for $k=1,2$ where $k=1$ corresponds to the non-ZLB regime and $k=2$ corresponds to the ZLB regime.
-\begin{gather}
-c_{t} = c_{t,1}I + c_{t,2}(1-I) 
-\end{gather}
-for $j=1,2$ and where $I$ is defined by:
-$$
-\begin{cases}
-  I = 1 & \text{ if } i > 1\\
-  I = 0 & \text{ otherwise.}
-\end{cases}
-$$
-%We use the functions, $V_l$, to determine the decisions rule though we do not approximate $V_l$ directly, because they inherit a kink associated with the ZLB constraint.
-Instead, we approximate functions, $V_{l,i}$, that are smoother and easier to approximate by specifying:
-%\begin{gather}
-%V_l = V_{l,1}I + V_{l,2}(1-I) 
-%\end{gather}
-%for $l \in \{\lambda, \pi\}$ and $j=1,2$ and where $I$ is defined by:
-%\begin{gather}
-%  I = 1 \text{ if } i > 1\\
-%  \text{  } = 0 \text{ otherwise}
-%\end{gather}
-%In the above, $i = \max(1,i^*)$ where $i^*$ denotes the value of the notional rate derived from evaluating the functions $V_{l,1}$ and using (2).
-(For each variable, we use $j=1$ to denote the function associated with the regime with a positive nominal interest rate and $j=2$ to denote the function associated with the ZLB regime.
-\\
-%Because the functions, $V_l$ depend directly on the nominal interest rate, we expect then to have a kink or non-differentiability.
-By contrast, the counterpart functions, $V_{l,j}$, that are indexed by the interest-rate regime do not depend on the current indicator function and thus are more likely to be smooth.
-\\
-%Specifically, $V_{\pi,1}$ and $V_{\pi,2}$ are both described by (8) because the nominal interest rate does not appear in that equation. $V_{\lambda,1}$ is described by (6), but for the ZLB regime:
-%\begin{gather}
-%V_{\lambda,t,2} =  \beta E_t[(1/\lambda_{t+1})(s_t/(\bar{\pi}\pi_{t+1}^{gap}g_{t+1}))]\\  
-%\end{gather}
-%where $i_t$ is replaced by 1.
-\end{comment}
-\end{document}

### 2019-04-20 Paper/Paper.tex
Finish and turn in paper

@@
 \title{Comparison of Global Solution Methods to a Zero Lower Bound Model}
-\date{\small First Draft: \today}
+\date{\small\today}
 \author{Emily Martell\thanks{Thank you to Professor Throckmorton for advising and providing materials for this project.
@@
 {\small \forceindent During the Great Recession, the U.S.
-Federal Reserve lowered policy rates to zero, creating a kink in its policy rule, and calling into question traditional solution methods.
-Recent work has explored fully nonlinear models to represent the ZLB, but not much work has compared the performance of different solution methods.
-Two suggested solution methods are linear interpolation This paper examines the effect of making the policy functions conditional on whether the ZLB binds.
-We consider a fully nonlinear New Keynesian model with capital, and a solution algorithm with policy function iteration and linear interpolation.
-We find no evidence that the regime-indexed policy functions are smoother.
-In addition, the solution algorithms perform similarly with respect to accuracy, but the solution containing the regime-indexed policy functions is much slower, all else equal.}
+Federal Reserve lowered policy rates to zero, introducing a kink in its policy rule and calling into question traditional solution methods.
+Recent papers have solved fully nonlinear models that treats the zero lower bound (ZLB) as an occasionally binding constraint, but there is little work analyzing the relative performance of these nonlinear solution methods.
+Two proposed solution methods are policy function iteration with linear interpolation and regime-indexed policy function iteration with Chebyshev polynomial approximation.
+We examine the impact of making the policy functions conditional on whether the ZLB binds.
+Our solution algorithm uses evenly-spaced grid points, linear interpolation, and Rouwenhorst integration.
+This paper shows that the regime-indexed policy functions are quite nonlinear in a New Keynesian model with capital and are costly to approximate in terms of solution time.}
+
 \end{changemargin}
@@
 unprecedented lowering of policy rates, the ZLB holds for a considerable portion of historic data
-for three major economies --- the US, Japan, and the Euro Area. The ZLB creates a kink in the policy
+for three major economies --- the US, Japan, and the Euro Area. The ZLB introduces a kink in the policy
 rule and calls into question linear estimation methods.
@@
 The \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} solution method is policy function iteration with linear interpolation to approximate future variables.
-The state space features evenly-spaced nodes and exogenous state variables  approximated with the Markov chain from \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}}.
+The state space features evenly-spaced nodes and exogenous state variables  approximated with the Markov chain from \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}}, which \hyperlink{Kopecky}{\color{black}{Kopecky and Suen (2010)}} show outperforms other methods for approximating autoregressive processes.
 The Rouwenhorst approximation is useful because it only requires interpolation along the dimensions of the endogenous state variables.
-This yields a faster and more accurate solution than quadrature methods.They update the policy functions with linear interpolation to accurately capture the kink experienced at the ZLB.
+They update the policy functions with linear interpolation to accurately capture the kink experienced at the ZLB.
 
 The \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method approximates policy functions underlying the model's decision rule using an antistropic Smolyak method with Chebyshev polynomials.
-(See \hyperlink{Judd2}{\color{black}{Judd et al.\ (2014)}} for a discussion of antistropic Smolyak methods).
+(See \hyperlink{Judd2}{\color{black}{Judd et al.\, 2014}} for a discussion of antistropic Smolyak methods).
 They approximate the exogenous state variables using Gauss-Hermite quadrature.
@@
 The idea is that the policy functions feature a kink or non-differentiability at the ZLB and regime-indexing the policy functions will yield smoother functions.
+This is appropriate for the choice of Chebyshev polynomial approximation, which performs better on smoother functions.
 
@@
 %In a NK model instead???
-The standard representation of the Euler equation is
+The interest rate enters directly in the consumption Euler equation, which for our small-scale model without habit formation is as follows:
 \begin{gather*}
-u'(c_t)  = \beta u'(c_{t+1})[f'(k_{t+1}) + 1 - \delta],
+    1 = \beta E_t[(c_t/c_{t+1})(s_ti_t/\pi_{t})],
 \end{gather*}
-where $u(\cdot)$ is the instantaneuous utility function, $0<\beta<1$ is the discount factor, $c_t$ is consumption at period $t$, $k_t$ is the capital stock at the beginning of the period, $0 < \delta \leq 1$ is the rate of depreciation, and $f(\cdot)$ is the production function.
-$u(\cdot)$ and $f(\cdot)$ are differentated according to the choice variables.
-The Euler equation is the fundamental dynamic equation in intertemporal optimization problems that include dynamic constraints.
-It states that the marginal cost of forgoing consumption today must equal the discounted marginal benefit of investing in capital for one period.
-%Cite Dr Richter's notes?
+where $E_t$ is the expectation operator, $0<\beta<1$ is the discount factor, and $c_t$, $s_t$, $i_t$, and $\pi_t$ are consumption, the risk premium, the interest rate, and inflation at time $t$.
+The interest rate appears because the household has the choice of owning a nominal bond, and must choose a combination of consumption, labor, and bond holdings to maximize expected lifetime utility.
+For this reason, consumption $c_t$ depends on the interest rate.
+At the ZLB, the presence of the interest rate creates a nonlinearity in the consumption Euler equation and motivates the use of regime-indexed policy functions.
 
-%Here make a better segway
-The interest rate appears in the household's budget constraint in models where the household has the choice of owning a nomimal bond.
-The household must choose a combination of consumption, labor, and bond holdings to maximize expected lifetime utility.
-Thus, the household's choice of consumption depends on the interest rate and whether the economy is at the ZLB.
 To approximate regime-indexed consumption policy functions $c_t^{ZLB}$ and $c_t^{normal}$, we provide initial guesses based on the log-linear solution.
-We refine the policy function guesses as follows: For each node in the state space, we solve for the time $t$ variables with either the $c_t^{ZLB}$  or $c_t^{normal}$ according to $i_t$, the interest rate at time $t$.
+We refine the policy function guesses as follows: For each node in the state space, we solve for the time $t$ variables with either $c_t^{ZLB}$  or $c_t^{normal}$ according to $i_t$, the interest rate at time $t$.
 With the time $t$ variables, we linearly interpolate both policy functions.
-Next, we calculate the interest rate on each node in the state space, construct an aggregate consumption policy function based on whether the economy is at the ZLB on each node, and calculate time $t+1$ variables acordingly.
+Next, we calculate the interest rate on each node in the state space, construct an aggregate consumption policy function based on whether the economy is at the ZLB on each node, and calculate time $t+1$ variables accordingly.
 We then update $c_t^{ZLB}$ with an interest rate of 1, and $c_t^{normal}$ with $i_t$.
@@
 
-In terms of accuracy, both the ART and GHLS yield similar Euler equation errors, with ART being slightly more accurate for the model with capital.
+In terms of accuracy, both ART and GHLS yield similar Euler equation errors, with ART being slightly more accurate for the model with capital.
 The ART method converges much more quickly than the GHLS method, particularly when capital is introduced to the model.
@@
 \section[Section 2]{Model \hypertarget{Section 2}{}} 
-This is a widely-employed New Keynesian model which is similar to the model in \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but includes capital accumulation as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}}.
+Our model is a widely-employed New Keynesian model which is similar to the model in \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but includes capital accumulation as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}}.
 Thus, it is an appropriate model to benchmark the accuracy and speed of the two solution methods.
@@
 The other parameters are set to values consistent with posterior estimates from similar models in the literature.
-For the model without capital, all parameters are the same except $\sigma_i$ which is set to $0.002$.
-(For the model with capital, $\sigma_i$ was originally set to $0.002$ to match \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}, but the model failed to hit the ZLB during simulation, so we increased the parameter to $0.0035$.)
+For the model without capital, all parameters are equivalent to those above except we set $\sigma_s=0.006$ and $\sigma_i=0.002$ allow the GHLS algorithm to converge.
 
@@
 \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} uses policy functions that are indexed by the interest-rate regime.
-Because these functions do not depend on the current indicator function,\hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} claims that they are more likely to be smooth.
+Because these functions do not depend on the current indicator function, \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} claims that they are more likely to be smooth.
 The regime-specific functions still depend on a secondary effect that the non-differentiability in the nominal rate in the following period has on expectations of future variables.
 However, following \hyperlink{Christiano}{\color{black}{Christiano and Fisher (2000)}} this effect should be small due to the presence of the expectations operators which act to smooth out regime-specific functions.
+Let the vector of policy functions at time $t$ be denoted $\textbf{pf}_t$ and the realization on node $d$ be denoted $\textbf{pf}_t(d)$.
 The idea for regime-indexed policy functions is as follows:
@@
 (For each variable, $j=1$ denotes the function associated with the regime with a positive nominal rate and $j=2$ denotes the function associated with the ZLB regime.) %In calculating the fixed point, we use $i=1$ when the model is in the ZLB regime.
-The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for and $l \in \{1,2,3,4\}$ which correspond to the household FOC bond, FOC capital, FOC investment, and the price Phillips curve, respectively, and $j = 1,2$.
+The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for and $l \in \{1,2,3,4\}$ which correspond to the household FOC bond, FOC capital, FOC investment, and the price Phillips curve, respectively, and $j \in \{1,2\}$.
 \begin{gather}
@@
  \label{eq:23} 
-  R_{t,3,j} = 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] - \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)],\\
+  \begin{split}
+    R_{t,3,j} &= 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] \\&- \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)], 
+  \end{split}
+  \\
    \label{eq:24}
-  R_{t,4,j} = \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t - \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
+  \begin{split}
+    R_{t,4,j} &= \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t \\&- \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
+    \end{split}
   \end{gather}
@@
 Our solution algorithm is as follows: Construct an evenly-spaced grid by discretizing the endogenous state variables and using \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}} method to approximate the exogenous processes for $s_t$, $g_t$, and $\varepsilon_{i,t}$.
-We use the Rouwenhorst method so that we do not have to interpolate along the dimensions of the exogenous state variables, providing a faster and more accurate than quadrature methods.
-The vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$.
+We use the Rouwenhorst method so that we do not have to interpolate along the dimensions of the exogenous state variables, which is faster and more accurate than quadrature methods.
+As above, the vector of policy functions is denoted $\textbf{pf}_t$ and the realization on node $d$ is denoted $\textbf{pf}_t(d)$.
 Denote the vector of states $\textbf{z}_t$.
 \begin{enumerate} 
-\item To construct the initial policy functions $\textbf{pf}_0$, we solve the log-linear analog of our model with the ZLB not impos
-ed using \hyperlink{Sims}{\color{black}{Sims's (2002) \texttt{gensys}}} algorithm. (For GHLS, we initialize the regime-indexed policy functions by setting them to the log-linear solution.)
+\item To construct the initial policy functions $\textbf{pf}_0$, we solve the log-linear analog of our model with the ZLB not imposed using \hyperlink{Sims}{\color{black}{Sims's (2002) \texttt{gensys}}} algorithm.
+(For GHLS, we initialize the regime-indexed policy functions by setting them to the log-linear solution.)
 \item For each node in the state space $d \in \{1,\dots,D\}:$
@@
 \item Solve for time $t+1$ variables from the expectation operators.
-Back out the policy functions $\textbf{pf}_{d}$ from the expectation operators and time $t+1$ variables.
+Back out the policy functions $\textbf{pf}_t(d)$ from the expectation operators and time $t+1$ variables.
 (For GHLS, we solve for the regime-indexed policy functions according to (\ref{eq:20})-(\ref{eq:24})).
@@
 We use Euler equation errors to measure the accuracy of our solutions.
-To measure errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method following ART to allow exogenous variables to have realizations between grid points.
+To approximate errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method following ART to allow exogenous variables to have realizations between grid points.
 The Euler equation errors are represented in absolute value of the errors in base 10 logarithms.
@@
     \hline
-  ART & 2401  & 67 & 17.9s & 78125 & 65 & 0h 15m 37.1s\\    
-  GHLS & 2401  & 66 & 46s & 78125 & 1170 &  5h 32m 48.6s\\
+  ART & 2401  & 76 & 21.6s & 78125 & 65 & 0h 15m 37.1s\\    
+  GHLS & 2401  & 62 & 18.5s & 78125 & 1170 &  5h 32m 48.6s\\
   \hline
@@
 
-The GHLS method is slower for both the model with and without capital. The speed
-differential blows up for the model with capital. The performance is somewhat contingent upon the
-parameterization. The GHLS method was faster with $\sigma_v = 0.002$, but we selected $\sigma_v = 0.0035$
-so that the ZLB constraint was better represented in the simulation. The GHLS solution
-algorithm handles a labor policy (consumption policy for model without capital) at and away from
-the ZLB. As a result, the solution algorithm requires two interpolation steps. In addition, the GHLS solution algorithm must determine at which nodes the state space is at the ZLB, and
+The GHLS method is slightly faster for the model without capital, but much slower for the model with capital. The performance is somewhat contingent upon the
+parameterization, but the results indicate that the speed differential blows up for the model with capital. This may be due to the following: The GHLS solution
+algorithm has a labor policy (consumption policy for model without capital) both at and away from
+the ZLB. As a result, the solution algorithm requires an additional interpolation step. In addition, the GHLS solution algorithm must determine at which nodes the state space is at the ZLB, and
 solve for time $t$ and $t + 1$ variables accordingly.
@@
 graph represent labor values corresponding to the ZLB. The GHLS labor policy function is
-computed at and away from the ZLB, and combined later, so all three are shown in the figure. The
-GHLS combined policy function is very similar to the policy function away from the ZLB.
+computed at and away from the ZLB and combined later, and all three are shown in the figure. The
+GHLS combined policy function is very similar to the policy function away from the ZLB, as only a fraction of the nodes experience the ZLB binding.
 
-Visually, the ART labor policy function is smoother. Labor hours smoothly
+Visually, the ART labor policy function cross-section is quite a bit smoother. Labor hours smoothly
 increase as the interest rate falls and hits the ZLB. The GHLS labor policy function
 features a kink at the ZLB where labor rises dramatically.
+
+For the model without capital, the GHLS policy functions do not experience as pronounced a nonlinearity.
+
+\begin{figure}[H]
+\hypertarget{Figure 2}  
+    \centering
+\captionsetup{justification=centering}
+    \includegraphics[width=16cm,scale=.9]{pfs3D.pdf}
+  \caption{Consumption policy function for model without capital}    
+  \end{figure}
+
+\hyperlink{Figure 2}{Figure 2} shows the cross-section of the consumption policy functions with the interest rate and
+risk premium. The policy functions are all fairly smooth and only have a slight nonlinearity at the
+ZLB. The GHLS policy functions are smoother than the ART policy function with respect to both the average percent error from a linear plane and the RMSE.
 
@@
     \hline
-    ART policy & 0.46545\% &0.0020137 $c$  units & 0.19585\% & .0029035 $l$ units \\    
-  GHLS policy & 0.45556\% & 0.0019792 $c$ units & 0.56142\% & 0.0076665 $l$ units \\
+    ART policy & 0.64407\% &0.0027327 $c$  units & 0.201367\% & 0.0029924 $l$ units \\    
+  GHLS policy & 0.62694\% & 0.0026704 $c$ units & 0.732262\% & 0.010799 $l$ units \\
   \hline
@@
  \hyperlink{Table 3}{Table 3} reports the RMSE (root mean square error) and mean percent error from linear policy
-functions. The mean percent error is calculated as $1/M\sum_{i=1}^N[\textbf{pf.n}(i)-\hat{\textbf{n}}(i)]/\bar{n}$
+functions. The mean percent error is calculated as $1/M\sum_{i=1}^N[\tilde{\textbf{n}}(i)-\hat{\textbf{n}}(i)]/\bar{n}$
 where $N$ is the
-number of periods, $\textbf{pf.n}$ is the labor policy function, $\hat{\textbf{n}}$ is the linear regression model of $\textbf{pf.n}$ fit to
-the state variables, and $\bar{n}$ is steady state labor. The corresponding results for the model without
-capital is reported in \hyperlink{Appendix C}{Appendix C}.
+number of periods, $\tilde{\textbf{n}}$ is the nonlinear approximation of the labor policy function, $\hat{\textbf{n}}$ is the linear regression model of $\tilde{\textbf{n}}$ fit to
+the state variables, and $\bar{n}$ is steady state labor. The linear regression model $Y = XB$ is as follows:
+\small
+\begin{gather*}
+  Y = \tilde{\textbf{n}},
+  X = \begin{bmatrix}
+    1 & g_t \\ 
+    1 & s_t \\   
+    1 & mp_t \\
+    1 & in_t \\
+    1 & c_t\\
+    1 & k_t\\
+    1 & x_t    
+  \end{bmatrix},
+  B = \begin{bmatrix}
+    \beta_0 \\
+    \beta_1
+    \end{bmatrix}.
+\end{gather*}
+\normalsize
+
+%The corresponding results for the model without
+%capital is reported in \hyperlink{Appendix C}{Appendix C}.
 
 The RMSE and the mean percent error indicate that the ART labor policy function is smoother and better fits a linear plane for the model with capital. For the model without
-capital, both functions are smooth, but the GHLS policy function slightly better fits a linear
-plane than the ART policy function.
+capital, both functions are smooth, but the GHLS policy function is slightly smoother according to the mean percent error and the RMSE.
 
 \begin{figure}[H]
-\hypertarget{Figure 2}  
+\hypertarget{Figure 3}  
     \centering
@@
 
-\subsection{Euler Equation Errors} \hyperlink{Figure 2}{Figure 2} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the household FOC bond, FOC capital, FOC investment, and price Phillips curve in the model with capital.
+\subsection{Euler Equation Errors} \hyperlink{Figure 3}{Figure 3} shows the distribution of the absolute value of the Euler equation errors in base 10 logarithms for the household FOC bond, FOC capital, FOC investment, and price Phillips curve in the model with capital.
 We also report the mean and maximum error.
-The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.
+%The corresponding results for the model without capital is reported in \hyperlink{Appendix C}{Appendix C}.
 
@@
 Euler equation errors are slightly more negative, and thus correspond to a smaller household error.
-The mean errors are similar, though the maximum error is considerably higher for the GHLS
-Euler equation error. The shapes of the errors are comparable.
+The mean errors are similar, though the GHLS maximum errors are larger. The shapes of the errors are comparable.
+
+For the model without capital, GHLS performs slightly better.
+
+\begin{figure}[H]
+\hypertarget{Figure 4}  
+    \centering
+\captionsetup{justification=centering}
+    \includegraphics[scale=1]{eeerrors.pdf}
+  \caption{Euler equation errors for model without capital}    
+  \end{figure}
+
+\hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10
+logarithms for the consumption Euler equation and the price Phillips curve. The mean and maximum Euler equations are comparable between algorithms, although GHLS has slightly smaller errors.
 
@@
 Federal Reserve lowered policy rates to zero, creating a kink in its policy rule, and calling into question traditional solution methods.
-Recent work has explored fully nonlinear models to represent the ZLB, but not much work has compared the performance of different solution methods.
-This paper analyzes the effect that different ways of representing the policy functions can have on a nonlinear solution algorithm.
+Recent work has explored solving fully nonlinear models to represent the ZLB, but not much work has compared the performance of different nonlinear solution methods.
+This paper analyzes the impact of regime-indexing the policy functions on a nonlinear solution algorithm.
 We use a method based on \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} to motivate directly approximating the policy functions and a method based on  \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} to motivate regime-indexing the policy functions.
-Although the regime-indexed policy functions were meant to be smoother and easier to compute, the GHLS method was slower and featured more of a non-linearity at the ZLB then the ART representation in the model with caiptal.
+Although the regime-indexed policy functions were meant to be smoother and easier to compute, the GHLS method yielded more nonlinear policy functions and was slower than the ART method in our model with capital.
 The regime-indexed policy functions also yielded a solution that was less accurate in terms of Euler equation errors in the model with capital.
@@
 Future work includes solving the GHLS solution method using Smolyak discretization methods with Chebyshev polynomials.
-We would expect this to speed up the solution algorithm and improve the accuracy of the solution.
-If this addition made the algorithm faster, we could also discretize the grid more finely to improve the accuracy of the solution and compare this to the ART method.
+We would expect this to speed up the solution algorithm, but it might lead to a less accurate solution.
+This paper shows that the policy functions conditional on the ZLB binding are quite nonlinear in the model with capital, which means low-order Chebyshev polynomials as in \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} will have a difficult time approximating them.
+The ultimate question is whether the speed gain outweighs any loss in accuracy.
 
@@
 
-%The GHLS solution is the same as above, except $\textbf{pf}_t(d) \equiv  [\tilde{\pi}^{gap}_t(\textbf{z}_t), n_t(\textbf{z}_t),n_t^{ZLB}(\textbf{z}_t), q_t(\textbf{z}_t), mc_t(\textbf{z}_t)]$ for the model with capital and $\textbf{pf}_t(d) \equiv [\tilde{\pi}^{gap}_t(\textbf{z}_t), \tilde{c}_t(\textbf{z}_t),\tilde{c}_t^{ZLB}(\textbf{z}_t)]$ for the model without capital where the policy functions away and at the ZLB are computed according to (\ref{eq:18}) and (\ref{eq:19}).
-The initial guess for $n_t^{ZLB}$ is set to the log-linear solution for $n_t$ from \texttt{gensys}.
-For step 2, in addition to what is in the ART solution method,
-%\begin{enumerate}
-%\item[(a)] Solve for $i_t$. If $i_t > 1$, solve for all time $t$ variables with $n_t$. Otherwise, solve for all time $t$ variables with $n_t^{ZLB}$. 
-%\item[(b)] Linearly interpolate both $n_t$ and $n_t^{ZLB}$ separately, as well as the other policy functions in $\textbf{pf}_{j-1}$ atF the updated state variables. 
-%\item[(c)] Solve for $\textbf{i}_t$ using the interpolated policy functions and time $t$ variables.
-If the node $\textbf{i}_t(d) > 1$, assign $\textbf{n}_t^{combined}(d)$ to the value in $\textbf{n}_t(d)$, otherwise $\textbf{n}_t^{combined}(d)$ to the value in $\textbf{n}_t^{ZLB}(d)$.
-Solve for the other elements in $\textbf{s}_{t+1}$ and approximate the expectation operators.
-%\item[(d)] Using the expectation operators, solve for the $n_t(d)$ policy in the style of (\ref{eq:20}) and the $n_t^{ZLB}$ policy in the style of (\ref{eq:21}).
-Solve for the rest of the policy functions in $\textbf{pf}_t(d)$.
-%\end{enumerate}
-
-\section{Results for model without capital} \hypertarget{Appendix C}
-The following reports the corresponding results for the model wtihout capital.
-
-\begin{figure}[H]
-\hypertarget{Figure 3}  
-    \centering
-\captionsetup{justification=centering}
-    \includegraphics[width=16cm,scale=.9]{pfs3D.pdf}
-  \caption{Consumption policy function for model without capital}    
-  \end{figure}
-
-\hyperlink{Figure 3}{Figure 3} shows the cross-section of the consumption policy functions with the interest rate and
-risk premium. The policy functions are all fairly smooth and only have a slight nonlinearity at the
-ZLB. The average percent error of the consumption policy functions from a linear plane is slightly
-lower for the GHLS policy functions.
-
-\begin{figure}[H]
-\hypertarget{Figure 4}  
-    \centering
-\captionsetup{justification=centering}
-    \includegraphics[scale=1]{eeerrors.pdf}
-  \caption{Euler equation errors for model without capital}    
-  \end{figure}
-
-\hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10
-logarithms for the consumption Euler equation and the price Phillips curve. The mean and maximum Euler equations are comparable between algorithms; the GHLS solution does slightly
-better for the consumption Euler equation and the ART solution does slightly better for the
-firm pricing equation.
-
+%\section{Results for model without capital} \hypertarget{Appendix C}
 \section*{References}
@@
 \hypertarget{Aruoba} \hangindent=0.5cm \textsc{Aruoba, S., P. Cuba-Borda, and F. Schorfheide (2018):}  “Macroeconomic Dynamics
-Near the ZLB: A Tale of Two Countries,”  \textit{The Review of Economic Studies}, 85, 87–118.
+Near the ZLB: A Tale of Two Countries,”  \textit{The Review of Economic Studies}, 85, 87-118.
 
@@
 \hypertarget{Christiano}\hangindent=0.5cm \textsc{Christiano, L. J., and J. D. M. Fisher (2000): } “Algorithms for Solving Dynamic Models with Occasionally Binding
-Constraints,” \textit{Journal of Economic Dynamics and Control}, 24 (8), 1179–1232.
+Constraints,” \textit{Journal of Economic Dynamics and Control}, 24 (8), 1179-1232.
 
@@
 Rubio-Rami\'rez (2015):}  “Nonlinear Adventures at the Zero Lower Bound,” \textit{Journal of
-Economic Dynamics and Control}, 57, 182–204.
+Economic Dynamics and Control}, 57, 182-204.
 
 \hypertarget{Guerrieri}\hangindent=0.5cm\textsc{Guerrieri, L. and M. Iacoviello (2015):} “OccBin: A toolkit for solving dynamic models with occasionally binding
-constraints easily,”  \textit{Journal of Monetary Economics}, 70, 22–38.
+constraints easily,”  \textit{Journal of Monetary Economics}, 70, 22-38.
 
 \hypertarget{Gust}\hangindent=0.5cm\textsc{Gust, C., E. Herbst, D. Lo\'pez-Salido, and M. E. Smith (2017):} “The Empirical Implications of the Interest-Rate
-Lower Bound,”  \textit{American Economic Review}, 107, 1971–2006.
+Lower Bound,”  \textit{American Economic Review}, 107, 1971-2006.
 
@@
 \hypertarget{Judd2}\hangindent=0.5cm\textsc{Judd, K. L., L. Maliar, S. Maliar, and R. Valero (2014):}  “Smolyak Method for Solving Dynamic Economic Models:
-Lagrange Interpolation, Anisotropic Grid and Adaptive Domain,”  \textit{Journal of Economic Dynamics and Control}, 44, 92–123.
+Lagrange Interpolation, Anisotropic Grid and Adaptive Domain,”  \textit{Journal of Economic Dynamics and Control}, 44, 92-123.
 
@@
 
+\hypertarget{Kopecky}\hangindent=0.5cm\textsc{Kopecky, K. and R. Suen (2010):} “Finite State Markov-chain Approximations to Highly
+Persistent Processes,” \textit{Review of Economic Dynamics}, 13, 701-714.
+
 \hypertarget{Peterman}\hangindent=0.5cm \textsc{Peterman, W. B. (2016):}  “Reconciling Micro and Macro Estimates of the Frisch Labor Supply
-Elasticity,” \textit{Economic Inquiry}, 54, 100–120.
+Elasticity,” \textit{Economic Inquiry}, 54, 100-120.
 
 \hypertarget{Plante}\hangindent=0.5cm\textsc{Plante, M., A. W. Richter, and N. A. Throckmorton (2018):}  “The Zero Lower Bound and Endogenous Uncertainty,” \textit{Economic Journal}, forthcoming.
-\hypertarget{RT}\hangindent=0.5cm \textsc{Richter, A. W. and N. A. Throckmorton (2016):}  “Is Rotemberg Pricing Justified by Macro Data?” \textit{Economics Letters}, 149, 44–48.
+\hypertarget{RT}\hangindent=0.5cm \textsc{Richter, A. W. and N. A. Throckmorton (2016):}  “Is Rotemberg Pricing Justified by Macro Data?” \textit{Economics Letters}, 149, 44-48.
 
@@
 B.
-Walker (2014):}  “Accuracy, Speed and Robustness of Policy Function Iteration,” \textit{Computational Economics}, 44, 445–476.
+Walker (2014):}  “Accuracy, Speed and Robustness of Policy Function Iteration,” \textit{Computational Economics}, 44, 445-476.
 
-\hypertarget{Rotemberg}\hangindent=0.5cm \textsc{Rotemberg, J. J. (1982):} “Sticky Prices in the United States,” \textit{Journal of Political Economy}, 90, 1187–1211.
+\hypertarget{Rotemberg}\hangindent=0.5cm \textsc{Rotemberg, J. J. (1982):} “Sticky Prices in the United States,” \textit{Journal of Political Economy}, 90, 1187-1211.
 
@@
 Models,” in \textit{Frontiers of Business Cycle Research}, ed. by T. F. Cooley, Princeton, NJ: Princeton
-University Press, 294–330.
+University Press, 294-330.
 
-\hypertarget{Sims}\hangindent=0.5cm \textsc{Sims, C. A. (2002):}  “Solving Linear Rational Expectations Models,” \textit{Computational Economics}, 20, 1–20.
+\hypertarget{Sims}\hangindent=0.5cm \textsc{Sims, C. A. (2002):}  “Solving Linear Rational Expectations Models,” \textit{Computational Economics}, 20, 1-20.
 

### 2019-04-20 src/general/EEerrors_sim.m

@@ -8,7 +8,7 @@ clc
 saving = 'on';
 
 O.it = 'fp';
-O.alg = 'Gust';
+O.alg = 'ART';
 
 if strcmp(O.it,'fp') && strcmp(O.alg, 'ART')
     load('solutions/solutionfpART_5.mat')
@@ -17,7 +17,7 @@ elseif strcmp(O.it,'fp') && strcmp(O.alg, 'Gust')
 end
 
 O.it = 'fp';
-O.alg = 'Gust';
+O.alg = 'ART';
 V = variables;
 % Numerical pdf of state variables
 %   Simulation parameters

### 2019-04-20 src/general/solutions/smoothness_test.m

@@ -4,7 +4,7 @@ clc
 close all
 
 % Load solutions
-load('solutionfpART.mat')
+load('solutionfpART_5.mat')
 y_ART = pf.n(:);
 n_ART = pf.n;
 % Production function (2)
@@ -18,7 +18,7 @@ rgdpg = G.g_gr.*rgdpp./(P.g.*rgdp);
 inp_ART = G.in_gr.^P.rhoi.*(S.i*pf.pigap.^P.phipi.*rgdpg.^P.phiy).^(1-P.rhoi).*exp(G.mp_gr);   
 %inp_ART = G.in_gr.^P.rhoi.*(S.i*pf.pigap.^P.phipi).^(1-P.rhoi).*exp(G.mp_gr);
 
-load('solutionfpGust.mat')
+load('solutionfpGust_5.mat')
 y_Gust = pf.n(:);
 n_Gust = pf.n;
 %inp_Gust = G.in_gr.^P.rhoi.*(S.i*pf.pigap.^P.phipi).^(1-P.rhoi).*exp(G.mp_gr);
@@ -113,8 +113,16 @@ disp(['Gust, n: ',num2str(meanperc_err{2}), '%'])
 disp(['Gust, n_zlb: ', num2str(meanperc_err{3}), '%'])
 disp(['Gust, n_agg: ', num2str(meanperc_err{4}), '%'])
 
-figbox = [1,1,7,3.5];
-figure;%('Renderer', 'painters', 'Position', [100 100 825 525])
+set(0,'DefaultAxesFontSize',8)
+figbox = [200,200,850,400];
+subpad.bot = .175; % Increase if xaxis lables are cut off
+subpad.top = .15; % Increase if subplot title is cut off
+subpad.left = -.2; % Increase if ylabel is cut off
+subpad.right = -.2; % Decrease if white-space on RHS
+subpad.legend = 0; % Increase if legend overlaps subplot titles
+fontsize = 8;
+
+figure
 set(gcf,'position',figbox);
 
 in_vec = squeeze(G.in_gr(2,:,2,:,3,3,3));
@@ -133,9 +141,9 @@ subplot(2,2,i)
 %     end
 %hold on
 surf(squeeze(G.in_gr(2,:,2,:,3,3,3)),squeeze(G.s_gr(2,:,2,:,3,3,3)), z{i})
-zlim([.32,.37])
+zlim([.32,.39])
 colormap winter
-freezeColors %from MATLAB file exchange
[…]

### 2019-04-20 src/simple/solutions/smoothness_test.m

@@ -87,8 +87,16 @@ disp(['Gust, c: ',num2str(meanperc_err{2}), '%'])
 disp(['Gust, c_zlb: ', num2str(meanperc_err{3}), '%'])
 disp(['Gust, c_agg: ', num2str(meanperc_err{4}), '%'])
 
-figbox = [1,1,7,4.5];
-figure;%('Renderer', 'painters', 'Position', [100 100 825 525])
+set(0,'DefaultAxesFontSize',8)
+figbox = [200,200,800,400];
+subpad.bot = .25; % Increase if xaxis lables are cut off
+subpad.top = .2; % Increase if subplot title is cut off
+subpad.left = .1; % Increase if ylabel is cut off
+subpad.right = .1; % Decrease if white-space on RHS
+subpad.legend = 0; % Increase if legend overlaps subplot titles
+fontsize = 9;
+
+figure;
 set(gcf,'position',figbox);
 
 in_vec = squeeze(G.in_gr(4,:,4,:));
@@ -105,7 +113,6 @@ subplot(2,2,i)
 %hold on
 surf(squeeze(G.in_gr(4,:,4,:)),squeeze(G.s_gr(4,:,4,:)), z{i})
 colormap winter
-freezeColors %from MATLAB file exchange
 %xlim([.98, 1.04])
 %ylim([.98, 1.04])
 %zlim([.28, .39])
@@ -119,8 +126,8 @@ zlabel('Consumption','FontSize',9)
 title(label{i},'FontSize',10)
 [az, el] = view;
 view(az-90,el-10)
-text(1.013,1.04,.37,['avg \% err: ',num2str(meanperc_err{i})],'FontSize',9)
-text(1.013,1.04,.36,'Black dots: ZLB','FontSize',9)
+text(1.035,1.04,.39,['avg % err: ',num2str(meanperc_err{i})],'FontSize',9)
+text(1.035,1.04,.37,'Black dots: ZLB','FontSize',9)
 end
 
 % % Linear regressions using regress

### 2019-04-25 Paper/Paper.tex
Presentation done; just need to add featured bullet pts

@@
 To isolate the effect of splitting the policy functions, we use policy function iteration on a fixed point with linear interpolation following \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}}.
-This solution method also provides the motivation for a single policy function, and the \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution provides the motivation for a regime-indexed policy function.
+This solution method directly computes the policy functions, while the \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method indirectly computes the policy functions through regime-indexed policy functions.
 Henceforth, the solution method based on the \hyperlink{Atkinson}{\color{black}{Atkinson et al.\ (2019)}} solution algorithm will be denoted ART and the solution algorithm that estimates smoother functions based on \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} will be denoted GHLS.
@@
 Next, we calculate the interest rate on each node in the state space, construct an aggregate consumption policy function based on whether the economy is at the ZLB on each node, and calculate time $t+1$ variables accordingly.
-We then update $c_t^{ZLB}$ with an interest rate of 1, and $c_t^{normal}$ with $i_t$.
+We then update $c_t^{ZLB}$ with the interest rate constrained at the ZLB, and $c_t^{normal}$ with a positive interest rate.
 
@@
       \label{eq:16}
-  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{g}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}), 0 \leq \rho_i < 1, \varepsilon_i \sim \mathds{N}(0,1),
+  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{gdp}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}), 0 \leq \rho_i < 1, \varepsilon_i \sim \mathds{N}(0,1),
   \end{gather}
-where $y^{gdp}$ is real GDP (i.e., output, $y$, minus the resources lost due to adjustment costs, $adj^p$), $i^n$ is the gross notional interest rate, $\bar i$ and $\bar{\pi}$ are the target values of the inflation and nominal interest rates, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps.
+where $y^{gdp}$ is real GDP (i.e., output, $y$, minus the resources lost due to adjustment costs, $adj^p$), $i^n$ is the gross notional interest rate, $\bar i$ is the target values of the nominal interest rate, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps.
 A more negative net notional rate indicates that the central bank is more constrained.\\
@@
   Steady-State Inflation Rate & $\bar{\pi}$ & $1.0053$ & Technology Growth Shock SD & $\sigma_g$ & $0.005$ \\
-  Capital Share of Income & $\alpha$ & $0.35$ & Risk Premium Shock SD & $\sigma_s$ & $0.005$ \\
-  Capital Depreciation Rate & $\delta$ & $0.025$ & Notional Interest Rate Shock SD & $\sigma_i$ & $0.0035$ \\
+  Capital Share of Income & $\alpha$ & $0.35$ & Risk Premium Shock SD & $\sigma_s$ & $0.0085$ \\
+  Capital Depreciation Rate & $\delta$ & $0.025$ & Notional Interest Rate Shock SD & $\sigma_i$ & $0.002$ \\
   Investment Adjustment Cost & $\nu$ & $4$ & & &\\
@@
 The other parameters are set to values consistent with posterior estimates from similar models in the literature.
-For the model without capital, all parameters are equivalent to those above except we set $\sigma_s=0.006$ and $\sigma_i=0.002$ allow the GHLS algorithm to converge.
+For the model without capital, all parameters are equivalent to those above except we set $\sigma_s=0.006$ to allow the GHLS algorithm to converge.
 
@@
 (For each variable, $j=1$ denotes the function associated with the regime with a positive nominal rate and $j=2$ denotes the function associated with the ZLB regime.) %In calculating the fixed point, we use $i=1$ when the model is in the ZLB regime.
-The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for and $l \in \{1,2,3,4\}$ which correspond to the household FOC bond, FOC capital, FOC investment, and the price Phillips curve, respectively, and $j \in \{1,2\}$.
+The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for $l \in \{1,2,3,4\}$ which correspond to the household FOC bond, FOC capital, FOC investment, and the price Phillips curve, respectively, and $j \in \{1,2\}$.
 \begin{gather}
@@
     \hline
-  ART & 2401  & 76 & 21.6s & 78125 & 65 & 0h 15m 37.1s\\    
-  GHLS & 2401  & 62 & 18.5s & 78125 & 1170 &  5h 32m 48.6s\\
+  ART & 2401  & 76 & 23.01s (avg. 30 runs) & 78125 & 56 & 0h 9m 16.1s\\    
+  GHLS & 2401  & 62 & 19.34s (avg. 30 runs) & 78125 & 1231 &  3h 28m 28.8s\\
   \hline
@@
 
-For the model without capital, the GHLS policy functions do not experience as pronounced a nonlinearity.
-
 \begin{figure}[H]
@@
 risk premium. The policy functions are all fairly smooth and only have a slight nonlinearity at the
-ZLB. The GHLS policy functions are smoother than the ART policy function with respect to both the average percent error from a linear plane and the RMSE.
+ZLB.
+The GHLS policy functions do not experience a profound nonlinearity as they do in the model with capital.
+The GHLS policy functions are smoother than the ART policy function with respect to both the average percent error from a linear plane and the RMSE.
 
@@
     \hline
-    ART policy & 0.64407\% &0.0027327 $c$  units & 0.201367\% & 0.0029924 $l$ units \\    
-  GHLS policy & 0.62694\% & 0.0026704 $c$ units & 0.732262\% & 0.010799 $l$ units \\
+    ART policy & 0.64407\% &0.0027327 $c$  units & 0.271154\% & 0.0039806 $l$ units \\    
+  GHLS policy & 0.62694\% & 0.0026704 $c$ units & 0.578098\% & 0.0080785 $l$ units \\
   \hline
@@
 \captionsetup{justification=centering}
-    \includegraphics[width=16cm,scale=.8]{eeerrorsCAP.pdf}%{pfs3D_CAPITAL.eps}
+    \includegraphics[width=16cm,scale=.8]{eeerrorsCAP.pdf}%{pfs3D_CAPITAL.pdf}
   \caption{Euler equation errors for model with capital}    
@@
 
-The Euler equation errors are very similar between solution algorithm, though the ART
-Euler equation errors are slightly more negative, and thus correspond to a smaller household error.
-The mean errors are similar, though the GHLS maximum errors are larger. The shapes of the errors are comparable.
-
-For the model without capital, GHLS performs slightly better.
+The Euler equation errors are comparable between solution algorithms.
+The household FOC bond and the price Phillips curve are slightly more negative thought the Euler equation errors are slightly more negative in general, and thus correspond to a smaller household error.
+The shapes of the errors are similar.
+%though the ART
+%Euler equation errors are slightly more negative, and thus correspond to a smaller household error.
+%The mean errors are similar, though the GHLS maximum errors are larger.
 
@@
 \hyperlink{Figure 4}{Figure 4} shows the distribution of the absolute value of the Euler equation errors in base 10
-logarithms for the consumption Euler equation and the price Phillips curve. The mean and maximum Euler equations are comparable between algorithms, although GHLS has slightly smaller errors.
+logarithms for the consumption Euler equation and the price Phillips curve.
+The mean and maximum Euler equations are comparable between algorithms, although GHLS has slightly smaller errors.
+Unlike the model with capital, GHLS performs better.
 

### 2019-04-25 Presentation/Presentation.tex
Presentation done; just need to add featured bullet pts

%\documentclass[handout, bigger]{beamer} %For Handouts
\documentclass[11pt]{beamer}
\usetheme{Singapore}
\usefonttheme[header]{structuresmallcapsserif}
\usefonttheme{professionalfonts}

\usepackage{color,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{multirow}
\usepackage{times}
\usepackage{float}
\usepackage{etoolbox}
\usepackage{dsfont}

\makeatletter
\patchcmd{\Ginclude@eps}{"#1"}{#1}{}{}
\makeatother
\usepackage{tikz}
\usetikzlibrary{positioning}
\usepackage{siunitx}
\sisetup{group-separator={,},group-four-digits=true}
\usepackage[labelformat=empty,scriptsize,singlelinecheck=off]{caption}
\captionsetup[subfigure]{font=scriptsize,labelfont=scriptsize}
\usepackage[font+=scriptsize]{subcaption}
\usepackage{xcolor}
\usepackage{comment}
\usepackage{tabularx}

\usepackage{accents}
\newcommand{\ubar}[1]{\underaccent{\bar}{#1}}
\newcommand{\overbar}[1]{\mkern 1.5mu\overline{\mkern-1.5mu#1\mkern-1.5mu}\mkern 1.5mu}
\setbeamertemplate{itemize subitem}[triangle]

% Set footline
\makeatletter
\setbeamertemplate{footline}
{%
\begin{beamercolorbox}[wd=\paperwidth,ht=0.5ex,dp=0ex,center]{footlinerule}
\end{beamercolorbox}%
\begin{beamercolorbox}[wd=\paperwidth,ht=0.6ex,dp=0ex,center]{empty}
\end{beamercolorbox}%
\leavevmode%
  \hbox{%
  \begin{beamercolorbox}[wd=\paperwidth,ht=2.25ex,dp=2ex,center]{author in head/foot}%
    \usebeamerfont{author in head/foot}%
    \insertshortauthor
  \end{beamercolorbox}}%
  \vskip0pt%
}
\makeatother

%Set Margins
\beamersetleftmargin{0.5cm}
\beamersetrightmargin{0.5cm}

%Imported File Type
\DeclareGraphicsExtensions{.eps}

%Remove Navigation Symbols
\setbeamertemplate{navigation symbols}{}

%Sets the transparency of uncovered text
\beamertemplatetransparentcoveredmedium

%Define New Font Sizes
\def\Tiny{\fontsize{5pt}{5pt}\selectfont}
\def\Scriptsize{\fontsize{8pt}{8pt}\selectfont}

%Table mid rule width
\newcommand{\otoprule}{\midrule[\heavyrulewidth]}

%Define Color Names
\definecolor{Gray}{rgb}{0.65,0.65,0.65}
\definecolor{darkblue}{rgb}{0,0,0.55}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{red}{rgb}{1,0,0}

% Counter for resuming enumeration across slides
\newcounter{savedenumi}

\newcommand{\scs}{\Tiny}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

    \title[]{Comparison of Global Solution Methods to a Zero Lower Bound Model}
    \author[]{\color{Gray} Emily Martell\thanks{\scriptsize{Thank you to Professor Throckmorton for advising and providing materials for this project. Thank you to Professor Campbell, Professor Han, Professor Rolek, and Professor Throckmorton for serving on my committee.}}}
    \date[]{College of William \& Mary \\ \today}

\begin{document}

%===============================================================================================================

{
\setbeamertemplate{footline}{}
    \frame{\titlepage}
}

%===============================================================================================================

\begin{frame}\frametitle{Introduction}

\begin{itemize}\setlength{\itemsep}{7pt}
  \item  As a result of the global financial crisis of 2007-9 and the subsequent recession, central banks lowered their policy rate to its zero lower bound (ZLB)
  \item  The ZLB now holds for a significant portion of historic data for the US, Japan, and the Euro Area
  \item  The ZLB introduces a kink in the central bank's policy rule and calls into question linear estimation methods
  \item  Responses in the literature to this nonlinearity include:
  %\item This paper:
  \begin{enumerate}\setlength{\itemsep}{4pt}
	\item  Failing to incorporate ZLB period data
	\item  Estimating linear models on the entire data set
	\item  Estimating a piecewise linear version of the nonlinear model (e.g., Guerrieri and Iacoviello, 2017)
	\item  Estimating fully nonlinear models that treats the ZLB as an occasionally binding constraint (e.g., Gust et al., 2017; Plante et al., 2018; Richter and Throckmorton, 2016).
  \end{enumerate}
\end{itemize}
\end{frame}

%===============================================================================================================

\begin{frame}\frametitle{Nonlinear Solution Methods}
\begin{itemize}\setlength{\itemsep}{10pt}
	\item  As it is important to incorporate all historical data and yield acurate parameter values and predictions, the path forward seems to be in fully nonlinear models
	\item Solving nonlinear models with projection methods (e.g. Aruoba et al., 2018; Ferna\'ndez-Villaverde et al., 2015).
	\item  Researchers have used different methods for solving fully nonlinear models:
	\begin{enumerate} \setlength{\itemsep}{4pt}
		\item  Policy function iteration with linear interpolation (e.g., Plante et al., 2018; Richter and Throckmorton, 2016).
		\item  Alternate approximating functions: regime-indexed policy functions (Gust et al., 2017), piecewise smooth policy functions (Aruoba et al. 2018)
		\item  Alternate grid construction: Smolyak method with Chebyshev polynomials (e.g., Gust et al., 2017; Ferna\'ndez-Villaverde et al. 2015; Aruoba et al., 2018)
	\end{enumerate}
\end{itemize}
\end{frame}

%=========================================================================
\begin{frame}\frametitle{Two Solution Methods}
\begin{table}\scriptsize
    \renewcommand*{\arraystretch}{1.4}
    \setlength{\tabcolsep}{6pt}      
  \begin{tabularx}{\textwidth}{l | X | X}
    \hline
    & \textbf{Atkinson et al.\ (2019)} & \textbf{Gust et al.\ (2017)} \\ \hline
    	Discretization Method & Evenly-spaced grid points & Smolyak Method\\
	Policy Function Evaluation & Linear Interpolation & Chebyshev Polynomials \\
	Integration Method & Rouwenhorst & Gauss-Hermite quadrature  \\ \hline
\end{tabularx}
\end{table}\normalsize
\begin{itemize}\setlength{\itemsep}{10pt}
\item  Evenly-spaced grid points work well with linear interpolation
\item  The Smolyak method is optimal for Chebyshev polynomials
\item  The Rouwenhorst (1995) method improves approximation on exogenous dimensions when the driving processes are autoregressive
\end{itemize}

\end{frame}
%=========================================================================
\begin{frame}\frametitle{Atkinson et al.\ (2019)}
\begin{itemize}\setlength{\itemsep}{10pt}
\item  Time iteration with linear interpolation
\item Directly approximates policy functions
\item  State space features evenly-spaced nodes
\item  Exogenous variables are approximated with the Markov chain from Rouwenhorst (1995)
  \begin{itemize}\setlength{\itemsep}{4pt}
\item Only requires interpolation along the dimensions of the endogenous state variables
\end{itemize}
\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{Gust et al.\ (2017)}
\begin{itemize}\setlength{\itemsep}{6pt}
\item  Approximates policy functions using an antistropic Smolyak method with Chebyshev polynomials
\item  Approximates exogenous state variables using Gauss-Hermite quadrature%why if we know Rouwenhorst is better?
\item  Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, building on Christiano and Fisher (2000)
  \begin{itemize}\setlength{\itemsep}{4pt}
\item  Policy functions feature a kink or non-differentiability at the ZLB and regime-indexing the policy functions will yield smoother functions
\item  Low-order Chebyshev polynomials perform better on smoother functions and are inexpensive to compute
\end{itemize}
\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{This Project}
\begin{itemize}\setlength{\itemsep}{8pt}
\item  In this project, we consider how splitting up the policy functions conditional on the ZLB impacts the speed and accuracy of the solution of a nonlinear model
\item  We use policy function iteration on a fixed point with linear interpolation
\item  Atkinson et al.\ (2019) provides the motivation for a single policy function;  Gust et al.\ (2017) provides the motivation for a regime-indexed policy function
\item  Solution algorithm based on Atkinson et al.\ (2019) denoted henceforth as ART; solution algorithm based on Gust et al.\ (2017) denoted henceforth as GHLS
\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{Our Solution Algorithm} %NEED TO PUT SOME ABOUT GHLS?
\begin{itemize}\setlength{\itemsep}{8pt}
\item   Construct the state space with evenly-spaced nodes and approximate exogenous state variables with Rouwenhorst (1995)
\item  Obtain initial conjectures for a set of policy functions from the log-linear solution
\item  Using a fixed point iteration scheme, linearly interpolate and numerically integrate the policy functions each step
\begin{itemize}
\item  For ART portion, we update a single policy function, and for the GHLS portion we update regime-indexed policy functions
\end{itemize}
\item  The algorithm converges once the maximum distance between successive guesses of policy functions falls below a convergence criterion

\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{Motivation for Regime-Indexed Policy Functions}
\begin{itemize}\setlength{\itemsep}{6pt}
\item  The interest rate enters directly in the consumption Euler equation
\begin{gather*}
1 =  E_t[\beta(c_t/c_{t+1})(s_ti_t/\pi_t)],
\end{gather*}
where $E_t$ is the expectation operator, $0 < \beta < 1$ is the discount factor, and $c_t$, $s_t$, $i_t$, and $\pi_t$ are consumption, the risk premium, the interest rate, and inflation at time $t$. 
\begin{itemize} \small
\item $\beta(c_t/c_{t+1})$ is a stochastic discount factor used to value future real income
\item $s_ti_t/\pi_t$ is a real interest rate on a one-period bond
\end{itemize}\normalfont
\item  At the ZLB, the presence of the interest rate creates a nonlinearity in the consumption Euler equation 
\item  $c_t$ depends directly on the interest rate
\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{The Model (With Capital)}
\begin{itemize}\setlength{\itemsep}{6pt}
\item The households choose $\{c_t, n_t, b_t, x_t, k_t\}_{t=0}^\infty$ to maximize expected lifetime utility given by
\begin{gather*}
E_0\sum_{t=0}^\infty\beta[\log(c_t-hc^a_{t-1}) - \chi n_t^{1+\eta}/(1+\eta)],
\end{gather*} 
subject to their budget constraint
\begin{gather*}
    c_t+x_t+b_t/(i_ts_t)=w_tn_t+r_t^kk_{t-1}+b_{t-1}/\pi_t+d_t.
  \end{gather*} 
\item The nominal bond, $b$, is subject to a risk premium, $s$, that follows
\begin{gather*}
  s_t = (1-\rho_s)\bar{s} + \rho_ss_{t-1} + \sigma_s\varepsilon_{s,t},
\end{gather*}
where $\bar{s}$ is the steady-state value. %An increase in $s_t$ boosts saving, which lowers period-$t$ demand.
\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{Households}
\begin{itemize}\setlength{\itemsep}{8pt}
\item Households also face an investment adjustment cost, so the law of motion for capital is given by
\begin{gather*}
  k_t = (1-\delta)k_{t-1} + x_t(1-\nu(x^g_t - 1)^2/2),\; 0 \leq \delta \leq 1.
  \end{gather*} %$x_t^g$ is investment growth relative to its steady-state and $\nu \geq 0$ scales the cost.
\item The FOCs to each household's constrained optimization problem are
\scriptsize
\begin{gather*}
  \lambda_t = c_t - hc^a_{t-1}, \\
  w_t = \chi n_t^\eta \lambda_t,\\
  1 =  \beta E_t[(\lambda_t/\lambda_{t+1})(s_ti_t/(\bar{\pi}\pi_{t+1}^{gap}))],\\
  q_t = \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})],\\
  1 = q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] + \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)],\\
  \varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
\end{gather*} %where $1/\lambda$ is the marginal utility of consumption and $q$ is Tobin's q 
\normalsize
\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{Firms}
\begin{itemize}\setlength{\itemsep}{8pt}
\item The production sector consists of a continuum of monopolistically competitive intermediate goods firms and a final goods firm 
\item Technology is $z_t = g_tz_{t-1}$, which is common across firms
\item Deviations from the steady-state growth rate, $\bar{g}$, follow
\begin{gather*}
  g_t = \bar{g} + \sigma_g\varepsilon_{g,t}.
\end{gather*}
\item In symmetric equilibrium, the optimality conditions reduce to
\scriptsize
\begin{gather*}
  y_t = (k_{t-1})^\alpha(z_tn_t)^{1-\alpha},\\
  w_t = (1-\alpha)mc_ty_t/n_t,\\
  r_t^k = \alpha mc_t y_t/k_{t-1},\\
  \varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
\end{gather*}
\normalfont
\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{Monetary Policy}
\begin{itemize} \setlength{\itemsep}{14pt}
\item
The central bank sets the gross nominal interest rate, $i$, according to
\begin{gather*}
    i_t=\max\{1,i_t^n\},\\
  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{gdp}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}). 
\end{gather*}
%where $y^{gdp}$ is real GDP (i.e., output, $y$, minus the resources lost due to adjustment costs, $adj^p$), $i^n$ is the gross notional interest rate, $\bar i$ and $\bar{\pi}$ are the target values of the inflation and nominal interest rates, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps. 
\item A more negative net notional rate indicates that the central bank is more constrained
\end{itemize}
\end{frame}

%=========================================================================
\begin{frame}\frametitle{Competitive Equilibrium}\setlength{\itemindent}{-1.2em}
\begin{itemize} \setlength{\itemsep}{8pt}
\item The aggregate resource constraint and real GDP definition are given by:
\begin{gather*}
  c_t + x_t = y_t^{gdp}\\
  y_t^{gdp} = [1 - \varphi(\pi_t^{gap}-1)^2/2]y_t
\end{gather*}
\item The model does not have a steady-state due to the unit root in technology, $z_t$. Therefore, we define the variables with a trend in terms of technology (i.e., $\tilde{x}_t \equiv x_t/z_t$)
\end{itemize}
\end{frame}
%=========================================================================
\begin{frame}\frametitle{Competitive Equilibrium}
\begin{itemize} \setlength{\itemsep}{10pt}
\item A competitive equilibrium consists of sequences of 
\begin{enumerate} \setlength{\itemsep}{5pt}
\item quantities, $\{\tilde{c}_t, \tilde{y}_t, \tilde{y}_t^{gdp}, x^g_t, y^g_t, n_t, \tilde{k}_t, \tilde{x}_t\}_{t=0}^\infty$ \item prices, $\{\tilde{w}_t, i_t, i^n_t, \pi_t, \tilde{\lambda}_t, q_t, r^k_t, mc_t\}_{t=0}^\infty$
\item exogenous variables, $\{s_t,g_t\}_{t=0}^\infty$
\end{enumerate}
\item that satisfy the detrended equilibrium system, given 
\begin{enumerate}\setlength{\itemsep}{5pt}
\item the initial conditions, $\{\tilde{c}_{-1}, i^n_{-1}, \tilde{k}_{-1}, \tilde{x}_{-1}, \tilde{w}_{-1}, s_0, g_0, \varepsilon_{i,0}\}$
\item three sequences of shocks, $\{\varepsilon_{g,t}, \varepsilon_{s,t}, \varepsilon_{i,t}\}_{t=1}^\infty$
\end{enumerate}
\end{itemize}
\end{frame}
%===============================================================================================================
\begin{frame}\frametitle{Parameter Values}
\begin{table}[H]
\centering
\captionsetup{justification=centering}
  \scriptsize
    \setlength{\tabcolsep}{3pt}      
  \begin{tabular}{l c c |l  c c}
    \hline
  Subjective Discount Factor & $\beta$ & $0.9949$ & Rotemberg Price Adjustment Cost & $\varphi$ & $100$ \\
   Frisch Labor Supply Elasticity & $1/\eta$ & $3$ & Inflation Gap Response & $\phi_\pi$ & $2.0$ \\
  Price Elasticity of Substitution & $\theta$ & $6$ & Output Growth Gap Response & $\phi_y$ & $0.5$ \\
  Steady-State Labor Hours & $\bar{n}$ & $1/3$ & Habit Persistence & $h$ & $0.80$ \\
  Steady-State Risk Premium & $\bar{s}$ & $1.0058$ & Risk Premium Persistence & $\rho_s$ & $0.80$ \\
  Steady-State Growth Rate & $\bar{g}$ & $1.0034$ & Notional Rate Persistence & $\rho_i$ & $0.80$ \\
  Steady-State Inflation Rate & $\bar{\pi}$ & $1.0053$ & Technology Growth Shock SD & $\sigma_g$ & $0.005$ \\
  Capital Share of Income & $\alpha$ & $0.35$ & Risk Premium Shock SD & $\sigma_s$ & $0.0085$ \\
  Capital Depreciation Rate & $\delta$ & $0.025$ & Notional Interest Rate Shock SD & $\sigma_i$ & $0.002$ \\
  Investment Adjustment Cost & $\nu$ & $4$ & & &\\
  \hline
  \end{tabular}
\normalfont
\end{table}
\begin{itemize}\setlength{\itemsep}{8pt}
\item Parameters are from Atkinson et al.\ (2019), and are chosen to be characteristic of U.S. data
\item For the model without capital, $\rho_s = 0.006$ %To allow the GHLS algorithm to converge
\end{itemize}
\end{frame}
%===================================================================================
\begin{frame}\frametitle{Discretized State Space (No Capital)}

\begin{itemize}\setlength{\itemsep}{10pt}
  \item State variables: $g_t$, $s_t$, $mp_t$, $i^n_{t-1}$
  \item Number of grid points: $N_g$, $N_{s}$, $N_{mp}$, $N_{i^n}$
  \item Grid boundaries: 
\begin{center}
$[g_{\min},g_{\max}]$, $[s_{\min},s_{\max}]$, $[mp_{\min},mp_{\max}]$, $[i^n_{\min},i^n_{\max}]$
\end{center}
  \item Create evenly spaced grids:
  \begin{center}
    $x_{grid} = \texttt{linspace}(x_{\min},x_{\max},N_x), \quad x\in\{g,s,mp,i^n\}$
  \end{center}
  \item State space contains $N=N_g\times N_s\times N_{mp}\times N_{i^n}$ nodes
  \item Create an array for each state variable, where every position is a unique permutation of the state space:
  \begin{center}
    $[g_{gr},s_{gr},mp_{gr},i^n_{gr}] = \texttt{ndgrid}(g_{grid},s_{grid},mp_{grid},i^n_{grid})$
  \end{center}
\end{itemize}

\end{frame}
%===================================================================================

\begin{frame}\frametitle{Functional Approximation}

\begin{itemize}\setlength{\itemsep}{12pt}
  \item True RE solution only exists in special cases %(e.g., $\delta=1$)
  \item Goal: Find an approximating function that maps the state space to the optimal decision rule for consumption:
  \begin{gather*}
    \underbrace{c(g,s,mp,i^n)}_{\textrm{True RE Solution}} \approx \underbrace{{\cal{P}}_c(g,s,mp,i^n)}_{\textrm{Approximating Function}}
  \end{gather*}
  \item Basic elements of the algorithm:
  \begin{enumerate}\setlength{\itemsep}{6pt}
    \item Interpolation: Linear, Chebyshev polynomials %Leasst Squares
    \item Integration: Rouwenhorst, Gauss-Hermite %Trapezoid, 
    \item Iteration: Time, Fixed-point 
  \end{enumerate}
\end{itemize}

\end{frame}

%===============================================================================================================

\begin{frame}\frametitle{Local Approximation}

\begin{itemize}\setlength{\itemsep}{8pt}
  \item Piecewise Linear Interpolation: 4 state variables $(g,s,mp,i^n)$
  \item Goal: Find the policy function value ${\cal{P}}_c(g',s',mp',{i^n}')$
  \item We have policy function values on nearest 24 nodes
  \begin{gather*}
   [{\cal{P}}_c(g_i,s_j,mp_k,i^n_l), {\cal{P}}_c(g_i,s_j,mp_k,i^n_{l+1}), {\cal{P}}_c(g_i,s_j,mp_{k+1},i^n_l), \\ \dots, {\cal{P}}_c(g_{i+1},s_{j+1},mp_{k+1},i^n_{l+1})]
  \end{gather*}
  once we determine the grid indices, $i,j,k,l$
  \item Locate the grid point left of $x'$, $x \in \{g,s,mp,i^n\}$ %nearest point to the left
   \begin{gather*}
    \textrm{step} = x_2 - x_1, \qquad \textrm{dist} = x' - x_1\\
    \textrm{loc} = \min(N_x-1,\max(1,\operatorname{floor}(\textrm{dist}/\textrm{step}) + 1))
    \end{gather*}
\end{itemize}

\end{frame}

%===============================================================================================================

\begin{frame}\frametitle{Global Approximation}

\begin{itemize}\setlength{\itemsep}{10pt}
  \item A general class of polynomials can be written as:
  \begin{gather*}
  {\cal{P}}(x;\eta) = \sum_{i=0}^n\eta_i\varphi_i(x).
  \end{gather*}
  \item Linear interpolation is a special case of this general class (i.e., $n=1$, $\varphi_i(x)=x^i$, and weights chosen appropriately)
  \item Can also use bases consisting of orthogonal polynomials (e.g., Chebyshev Polynomials)
\end{itemize}

\end{frame}

%===============================================================================================================
\begin{frame}\frametitle{Solving the Model}

\begin{enumerate}\setlength{\itemsep}{10pt}
  \item Calculate $z(s')$ for each realization of the state
  \item Find the updated policy function, $n(s')$, for each state
  \item Numerical Integration:
  \begin{itemize}\setlength{\itemsep}{5pt}
    \item First integrate across the continuous random variable, $z$, conditional on the future realizations of the discrete stochastic variable, $s'$.%, to obtain:
        %\begin{gather*}
         % E[\Phi(z')|s'=1], \quad E[\Phi(z')|s'=2]
        %\end{gather*}
    \item Then weight the conditional expectations by their corresponding likelihood. %The conditional expectations are:
  %  \begin{gather*}
    %  E\left[\Phi(z')|s = i\right] = p_{i1}E[\Phi(z')|s'=1] + p_{i2}E[\Phi(z')|s'=2]
   % \end{gather*}
  \end{itemize}
\end{enumerate}

\end{frame}

%===============================================================================================================

\begin{frame}\frametitle{Rouwenhorst Method}

\begin{itemize}\setlength{\itemsep}{8pt}
  \item Used to approximate an exogenous $AR(1)$ process
  \item Kopecky and Suen (2010) show the Rouwenhorst method outperforms other approximations of an $AR(1)$ process
  \item The approximation is a Markov switching process like the time-varying intercept example, but with $n$ states
  \item The method determines the bounds of the exogenous state variables, the nodes, and the transition probabilities
  \item Let $z\sim AR(1)$ with persistence $\rho$, mean $\mu_z$, and variance %Idea for approximation of an AR(1) process
  \begin{gather*}
    \sigma_z^2 = \sigma_\varepsilon^2/(1-\rho^2).
  \end{gather*}
  \item The $n$ states for the discretized process $z$ are evenly spaced on $[\mu_z-\sigma_z\sqrt{n-1},\mu_z+\sigma_z\sqrt{n-1}]$
\end{itemize}

\end{frame}

%===============================================================================================================

\begin{frame}\frametitle{Regime-Indexed Policy Functions}
\begin{itemize}\setlength{\itemsep}{10pt}
\item Let the vector of policy functions at time $t$ be denoted $\textbf{pf}_t$ and the realization on node $d$ be denoted $\textbf{pf}_t(d)$
\item The regime-indexed policy functions are as follows: 
\begin{gather*}
  \textbf{pf}_t(d) = \textbf{pf}_{t,1}(d)\mathds{I}_t(d) + \textbf{pf}_{t,2}(d)(1-\mathds{I}_t(d)),
\end{gather*}
where $\mathds{I}_t(d)$ is defined by 
\begin{gather*}
  \mathds{I}_t(d) = 
\begin{cases}
     1 &\text{ if } i_t > 1\\
     0 &\text{ otherwise.}
\end{cases}
\end{gather*}
\end{itemize}
%he variable $i_t=\max\{1,i_t^n\}$ represents the value of the notional rate derived from evaluating the functions $\textbf{pf}_{t,j}(d)$ for $j \in \{1,2\}$ and using equation (\ref{eq:16}). (For each variable, $j=1$ denotes the function associated with the regime with a positive nominal rate and $j=2$ denotes the function associated with the ZLB regime.)
\end{frame}
%===================================================================================
\begin{frame}\frametitle{Regime-Indexed Policy Functions}
The functions $\textbf{pf}_{t,j}$ satisfy the residual functions $R_{t,l,j}$ for $j \in\{1,2\}$ and $l \in \{1,2,3,4\}$: %which correspond to the household FOC bond, FOC capital, FOC investment, and the price phillips curve 
\scriptsize
\begin{gather*}
  R_{t,1,1} = 1 - s_ti_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))],\\
  R_{t,1,2} = 1 - s_t\beta E_t[(\lambda_t/\lambda_{t+1})(1/(\bar{\pi}\pi_{t+1}^{gap}))],\\
R_{t,2,j} = q_t - \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})],\\
    R_{t,3,j} = 1 - q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] - \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)], \\
    R_{t,4,j} = \varphi(\pi_t^{gap}-1)\pi_t^{gap} - (1-\theta) - \theta mc_t - \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
  \end{gather*}
\normalfont
\end{frame}
%===================================================================================
\begin{frame}\frametitle{Solution Algorithm} %NEED TO PUT SOME ABOUT GHLS?
 Construct an evenly-spaced grid using the Rouwenhorst method. Denote the vector of states $\textbf{z}_t$. % by discretizing the endogenous state variables and using \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}} method to approximate the exogenous processes for $s_t$, $g_t$, and $\varepsilon_{i,t}$.
\begin{itemize}\setlength{\itemsep}{8pt}

\item Solve the linear model using Sims's (2002) \texttt{gensys} algorithm. 
\item Solve the nonlinear model using fixed point iteration. For each node in the state space $d \in \{1,\dots,D\}:$
\begin{enumerate}\setlength{\itemsep}{2pt}
\item Solve for the variables dated at time $t$ given $\textbf{pf}_t$ and $\textbf{z}_t$. %For GHLS, if $i_t > 1$, update time $t$ variables with non-ZLB policy functions; if $i_t \leq 1$, update time $t$ variables with ZLB policy functions.
\item  Linearly interpolate the policy functions at the updated state variables $\textbf{z}_{t+1}$ to obtain $\textbf{pf}_{t+1}(m)$ on every integration node $m \in \{1,\dots,M\}$.% For GHLS, interpolate both non-ZLB and ZLB policy functions.
\item Given the interpolated policy functions $\{\textbf{pf}(m)\}_{m=1}^M$, and integration nodes and weights provided by the Rouwenhorst method, approximate the expectation operators for the model. %For GHLS, determine whether the model is at the ZLB at each node, and construct the policy function grids according to .
\item Back out the policy functions $\textbf{pf}_t(d)$ from the expectation operators and time $t+1$ variables. %For GHLS, solve for regime-indexed polynomials based on 
\end{enumerate}
\item Repeat step 2 until the maximum distance between successive approximations of the policy functions is below $10^{-6}$. 
\end{itemize}
\end{frame}

%===================================================================================
\begin{frame}\frametitle{Euler Equation Errors}
\begin{itemize}\setlength{\itemsep}{8pt}
%We use Euler equation errors to measure the accuracy of our solutions.
\item Measure of solution accuracy
\item To approximate errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method %to allow exogenous variables to have realizations between grid points. 
\item The Euler equation errors are represented in absolute value of the errors in base 10 logarithms
\begin{itemize}\setlength{\itemsep}{2pt}
\item An Euler equation error of -3 means the household makes an error equivalent to one per 1,000 consumption goods
\end{itemize}
\item Obtaining Euler equation errors:
\begin{itemize}\setlength{\itemsep}{2pt}
\item Simulate 10,000 periods of the model using the nonlinear solution with random shocks 
\item Follow one iteration of step 2 of our solution algorithm and transform the residuals to Euler equation errors
\end{itemize}
\end{itemize}
\end{frame}

%===============================================================================================================

\begin{frame}\frametitle{Parallel Processing in Matlab}

\begin{itemize}\setlength{\itemsep}{14pt}
  \item Any calculations that are not dependent on the results of other calculations can be performed in parallel (e.g., solving for policy values at each node in the state space)
  \item We replace \texttt{for} loops with \texttt{parfor} loops where applicable. This tells MATLAB to distribute each step in the loop across the specified number of processors
\end{itemize}

\end{frame}

%===================================================================================
\begin{frame}\frametitle{Solution Times}
\begin{table}[H]
  \centering
\captionsetup{justification=centering}
  \hypertarget{Table 2}
  \scriptsize
    \setlength{\tabcolsep}{3pt}      
  \begin{tabular}{l | c c c c c c}
    \hline
    & \multicolumn{3}{c}{Model without capital} & \multicolumn{3}{c}{Model with capital} \\
    & Total nodes & Iterations & Total Time & Total Nodes & Iterations & Total time\\
    \hline
  ART & 2401  & 76 & 23.01s (avg. 30 runs) & 78125 & 56 & 0h 9m 16.1s\\    
  GHLS & 2401  & 62 & 19.34s (avg. 30 runs) & 78125 & 1231 &  3h 28m 28.8s\\
  \hline
\end{tabular}
  \caption{Solution times}
\end{table}
\begin{itemize}\setlength{\itemsep}{10pt}
\item The solution times
were computed with multi-core processing using the Parallel Computing Toolbox
\item We implemented the interpolation steps of the algorithm in Fortran with MATLAB
executable functions (MEX) provided in the companion toolbox to \hyperlink{RTW}{\color{black}{Richter et al. (2014)}} %This may be due to the following: The GHLS solution algorithm has a labor policy (consumption policy for model without capital) both at and away from the ZLB. As a result, the solution algorithm requires an additional interpolation step. In addition, the GHLS solution algorithm must determine at which nodes the state space is at the ZLB, and solve for time $t$ and $t + 1$ variables accordingly.
\end{itemize}
\end{frame}
%===================================================================================

\begin{frame}\frametitle{Policy Functions: Model Without Capital}
\begin{figure}[H]
\hypertarget{Figure 1}  
    \centering
\captionsetup{justification=centering}
    \includegraphics[width=10cm,scale=.3]{../Paper/pfs3D.pdf}
  \caption{Consumption policy function for model without capital}    
  \label{Fig:1}
  \end{figure}
\end{frame}

%===================================================================================
\begin{frame}\frametitle{Smoothness Measures}
\begin{table}[H]
  \centering
\captionsetup{justification=centering}
  \hypertarget{Table 3}
  \scriptsize
    \setlength{\tabcolsep}{4pt}      
  \begin{tabular}{l c c c c}
    \hline
    & \multicolumn{2}{c}{Model without capital} & \multicolumn{2}{c}{Model with capital} \\
    & Mean \% Error & RMSE & Mean \% Error & RMSE\\
    \hline
    ART policy & 0.64407\% &0.0027327 $c$  units & 0.271154\% & 0.0039806 $l$ units \\    
  GHLS policy & 0.62694\% & 0.0026704 $c$ units & 0.578098\% & 0.0080785 $l$ units \\
  \hline
\end{tabular}
  \caption{Smoothness measures for labor policy functions ($c$ for model with capital and $n$ for model with capital). GHLS combined policy functions are reported.}
\end{table} 
 \begin{itemize}\setlength{\itemsep}{8pt}
\item RMSE (root mean square error)
\item Mean percent error from linear policy functions
\item  GHLS smoother for model without capital; ART smoother for model with capital
\end{itemize}
\end{frame}
%===================================================================================

\begin{frame}\frametitle{Euler Equation Errors: Model Without Capital}
% Distribution of the absolute value of the Euler equation errors in base 10 logarithms:
\begin{figure}[H]
    \centering
\captionsetup{justification=centering}
    \includegraphics[width=9cm,scale=.74]{../Paper/eeerrors.pdf}
  \caption{Euler equation errors for model without capital}    
  \end{figure}
\end{frame}

%===================================================================================
\begin{frame}\frametitle{Policy Functions: Model with Capital} %black dots: ZLB, GHLS labor policy function is computed at and away from the ZLB and conmied later
\begin{figure}[H]
\hypertarget{Figure 1}  
    \centering
\captionsetup{justification=centering}
    \includegraphics[width=10cm,scale=.3]{../Paper/pfs3DCAP.pdf}
  \caption{Labor policy function for model with capital}    
  \label{Fig:1}
  \end{figure}
\end{frame}
%===================================================================================

\begin{frame}\frametitle{Euler Equation Errors: Model With Capital}
 %Distribution of the absolute value of the Euler equation errors in base 10 logarithms:
\begin{figure}[H]
    \centering
\captionsetup{justification=centering}
    \includegraphics[width=10cm,scale=.8]{../Paper/eeerrorsCAP.pdf}
  \caption{Euler equation errors for model with capital}    
  \end{figure}
\end{frame}%Unlike the model with capital, GHLS performs better. 
%===================================================================================
\begin{frame}\frametitle{Conclusion}
\begin{itemize}\setlength{\itemsep}{8pt}
\item During the Great Recession, policy rates hit zero, calling into question traditional solution methods
\item There is a literature in solving nonlinear models, but not much work comparing nonlinear solution methods
\item This paper discusses the impact of regime-indexing the policy functions on a nonlinear solution algorithm
\begin{enumerate}\setlength{\itemsep}{4pt}
\item Motivation for directly approximating the policy functions from Atkinson et al.\ (2019)
\item Motivation for regime-indexing the policy functions from Gust et al.\ (2017). They claim that regime-indexed policy functions are smoother and easier to approximate
\end{enumerate}

\end{itemize}
\end{frame}

%===============================================================================================================
\begin{frame}\frametitle{Conclusion}
\begin{itemize}\setlength{\itemsep}{10pt}
\item Key takeaways:
\begin{itemize}\setlength{\itemsep}{4pt}
\item In the model without capital, regime-indexed policy functions were smoother and solution algorithm was faster
\item In model with capital,  the regime-indexed policy functions were more nonlinear and solution algorithm was slower
\end{itemize}
\item Extensions:
\begin{itemize}\setlength{\itemsep}{4pt}
\item Solve the GHLS solution method using Smolyak discretization methods and Chebyshev polynomials 
\item This would be expected to speed up the solution algorithm, but may lead to a less accurate solution
\end{itemize}
\end{itemize}
\end{frame}

\end{document}

### 2019-04-25 Presentation/Presentation.tex
Add in clicking bullets

@@
 \begin{itemize}\setlength{\itemsep}{7pt}
-  \item  As a result of the global financial crisis of 2007-9 and the subsequent recession, central banks lowered their policy rate to its zero lower bound (ZLB)
-  \item  The ZLB now holds for a significant portion of historic data for the US, Japan, and the Euro Area
-  \item  The ZLB introduces a kink in the central bank's policy rule and calls into question linear estimation methods
-  \item  Responses in the literature to this nonlinearity include:
+  \item <1-|handout:1>As a result of the global financial crisis of 2007-9 and the subsequent recession, central banks lowered their policy rate to its zero lower bound (ZLB)
+  \item  <2-|handout:1>The ZLB now holds for a significant portion of historic data for the US, Japan, and the Euro Area
+  \item  <3-|handout:1>The ZLB introduces a kink in the central bank's policy rule and calls into question linear estimation methods
+  \item <4-|handout:1> Responses in the literature to this nonlinearity include:
   %\item This paper:
@@
 \begin{itemize}\setlength{\itemsep}{10pt}
-	\item  As it is important to incorporate all historical data and yield acurate parameter values and predictions, the path forward seems to be in fully nonlinear models
-	\item Solving nonlinear models with projection methods (e.g. Aruoba et al., 2018; Ferna\'ndez-Villaverde et al., 2015).
-	\item  Researchers have used different methods for solving fully nonlinear models:
+	\item  <1-|handout:1>As it is important to incorporate all historical data and yield acurate parameter values and predictions, the path forward seems to be in fully nonlinear models
+	\item <2-|handout:1>Solving nonlinear models with projection methods (e.g. Aruoba et al., 2018; Ferna\'ndez-Villaverde et al., 2015).
+	\item  <3-|handout:1>Researchers have used different methods for solving fully nonlinear models:
 	\begin{enumerate} \setlength{\itemsep}{4pt}
@@
 \begin{itemize}\setlength{\itemsep}{10pt}
-\item  Evenly-spaced grid points work well with linear interpolation
-\item  The Smolyak method is optimal for Chebyshev polynomials
-\item  The Rouwenhorst (1995) method improves approximation on exogenous dimensions when the driving processes are autoregressive
+\item  <2-|handout:1>Evenly-spaced grid points work well with linear interpolation
+\item  <3-|handout:1>The Smolyak method is optimal for Chebyshev polynomials
+\item  <4-|handout:1>The Rouwenhorst (1995) method improves approximation on exogenous dimensions when the driving processes are autoregressive
 \end{itemize}
@@
 \begin{itemize}\setlength{\itemsep}{10pt}
-\item  Time iteration with linear interpolation
-\item Directly approximates policy functions
-\item  State space features evenly-spaced nodes
-\item  Exogenous variables are approximated with the Markov chain from Rouwenhorst (1995)
+\item <1-|handout:1> Time iteration with linear interpolation
+\item <2-|handout:1>Directly approximates policy functions
+\item <3-|handout:1> State space features evenly-spaced nodes
+\item<4-|handout:1>  Exogenous variables are approximated with the Markov chain from Rouwenhorst (1995)
   \begin{itemize}\setlength{\itemsep}{4pt}
@@
 \begin{itemize}\setlength{\itemsep}{6pt}
-\item  Approximates policy functions using an antistropic Smolyak method with Chebyshev polynomials
-\item  Approximates exogenous state variables using Gauss-Hermite quadrature%why if we know Rouwenhorst is better?
-\item  Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, building on Christiano and Fisher (2000)
+\item  <1-|handout:1>Approximates policy functions using an antistropic Smolyak method with Chebyshev polynomials
+\item  <2-|handout:1>Approximates exogenous state variables using Gauss-Hermite quadrature%why if we know Rouwenhorst is better?
+\item  <3-|handout:1>Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, building on Christiano and Fisher (2000)
   \begin{itemize}\setlength{\itemsep}{4pt}
@@
 \begin{itemize}\setlength{\itemsep}{8pt}
-\item  In this project, we consider how splitting up the policy functions conditional on the ZLB impacts the speed and accuracy of the solution of a nonlinear model
-\item  We use policy function iteration on a fixed point with linear interpolation
-\item  Atkinson et al.\ (2019) provides the motivation for a single policy function;  Gust et al.\ (2017) provides the motivation for a regime-indexed policy function
-\item  Solution algorithm based on Atkinson et al.\ (2019) denoted henceforth as ART; solution algorithm based on Gust et al.\ (2017) denoted henceforth as GHLS
+\item  <1-|handout:1>In this project, we consider how splitting up the policy functions conditional on the ZLB impacts the speed and accuracy of the solution of a nonlinear model
+\item  <2-|handout:1>We use policy function iteration on a fixed point with linear interpolation
+\item  <3-|handout:1>Atkinson et al.\ (2019) provides the motivation for a single policy function;  Gust et al.\ (2017) provides the motivation for a regime-indexed policy function
+\item <4-|handout:1> Solution algorithm based on Atkinson et al.\ (2019) denoted henceforth as ART; solution algorithm based on Gust et al.\ (2017) denoted henceforth as GHLS
 \end{itemize}
@@
 \begin{itemize}\setlength{\itemsep}{8pt}
-\item   Construct the state space with evenly-spaced nodes and approximate exogenous state variables with Rouwenhorst (1995)
-\item  Obtain initial conjectures for a set of policy functions from the log-linear solution
-\item  Using a fixed point iteration scheme, linearly interpolate and numerically integrate the policy functions each step
+\item   <1-|handout:1>Construct the state space with evenly-spaced nodes and approximate exogenous state variables with Rouwenhorst (1995)
+\item  <2-|handout:1>Obtain initial conjectures for a set of policy functions from the log-linear solution
+\item  <3-|handout:1>Using a fixed point iteration scheme, linearly interpolate and numerically integrate the policy functions each step
 \begin{itemize}
@@
 \end{itemize}
-\item  The algorithm converges once the maximum distance between successive guesses of policy functions falls below a convergence criterion
+\item <5-|handout:1> The algorithm converges once the maximum distance between successive guesses of policy functions falls below a convergence criterion
 
@@
 \begin{itemize}\setlength{\itemsep}{6pt}
-\item  The interest rate enters directly in the consumption Euler equation
+\item  <1-|handout:1>The interest rate enters directly in the consumption Euler equation
 \begin{gather*}
@@
 \end{itemize}\normalfont
-\item  At the ZLB, the presence of the interest rate creates a nonlinearity in the consumption Euler equation 
-\item  $c_t$ depends directly on the interest rate
+\item <2-|handout:1> At the ZLB, the presence of the interest rate creates a nonlinearity in the consumption Euler equation 
+\item <3-|handout:1> $c_t$ depends directly on the interest rate
 \end{itemize}
@@
 \begin{itemize}\setlength{\itemsep}{6pt}
-\item The households choose $\{c_t, n_t, b_t, x_t, k_t\}_{t=0}^\infty$ to maximize expected lifetime utility given by
+\item <1-|handout:1>The households choose $\{c_t, n_t, b_t, x_t, k_t\}_{t=0}^\infty$ to maximize expected lifetime utility given by
 \begin{gather*}
@@
   \end{gather*} 
-\item The nominal bond, $b$, is subject to a risk premium, $s$, that follows
+\item <2-|handout:1>The nominal bond, $b$, is subject to a risk premium, $s$, that follows
 \begin{gather*}
@@
 \begin{itemize}\setlength{\itemsep}{8pt}
-\item Households also face an investment adjustment cost, so the law of motion for capital is given by
+\item <1-|handout:1>Households also face an investment adjustment cost, so the law of motion for capital is given by
 \begin{gather*}
@@
   \end{gather*} %$x_t^g$ is investment growth relative to its steady-state and $\nu \geq 0$ scales the cost.
-\item The FOCs to each household's constrained optimization problem are
+\item <2-|handout:1>The FOCs to each household's constrained optimization problem are
 \scriptsize
@@
 \begin{itemize}\setlength{\itemsep}{8pt}
-\item The production sector consists of a continuum of monopolistically competitive intermediate goods firms and a final goods firm 
-\item Technology is $z_t = g_tz_{t-1}$, which is common across firms
-\item Deviations from the steady-state growth rate, $\bar{g}$, follow
+\item <1-|handout:1>The production sector consists of a continuum of monopolistically competitive intermediate goods firms and a final goods firm 
+\item <2-|handout:1>Technology is $z_t = g_tz_{t-1}$, which is common across firms
+\item <3-|handout:1>Deviations from the steady-state growth rate, $\bar{g}$, follow
 \begin{gather*}
@@
 \end{gather*}
-\item In symmetric equilibrium, the optimality conditions reduce to
+\item <4-|handout:1>In symmetric equilibrium, the optimality conditions reduce to
 \scriptsize
@@
 \begin{itemize} \setlength{\itemsep}{14pt}
-\item
+\item <1-|handout:1>\ 
 The central bank sets the gross nominal interest rate, $i$, according to
@@
 %where $y^{gdp}$ is real GDP (i.e., output, $y$, minus the resources lost due to adjustment costs, $adj^p$), $i^n$ is the gross notional interest rate, $\bar i$ and $\bar{\pi}$ are the target values of the inflation and nominal interest rates, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps.
-\item A more negative net notional rate indicates that the central bank is more constrained
+\item <2-|handout:1>A more negative net notional rate indicates that the central bank is more constrained
 \end{itemize}
@@
 \begin{itemize} \setlength{\itemsep}{8pt}
-\item The aggregate resource constraint and real GDP definition are given by:
+\item <1-|handout:1>The aggregate resource constraint and real GDP definition are given by:
 \begin{gather*}
@@
 \end{gather*}
-\item The model does not have a steady-state due to the unit root in technology, $z_t$. Therefore, we define the variables with a trend in terms of technology (i.e., $\tilde{x}_t \equiv x_t/z_t$)
+\item <2-|handout:1>The model does not have a steady-state due to the unit root in technology, $z_t$.
+Therefore, we define the variables with a trend in terms of technology (i.e., $\tilde{x}_t \equiv x_t/z_t$)
 \end{itemize}
@@
 \begin{itemize} \setlength{\itemsep}{10pt}
-\item A competitive equilibrium consists of sequences of 
+\item <1-|handout:1>A competitive equilibrium consists of sequences of 
 \begin{enumerate} \setlength{\itemsep}{5pt}
@@
 \end{enumerate}
-\item that satisfy the detrended equilibrium system, given 
+\item <2-|handout:1>that satisfy the detrended equilibrium system, given 
 \begin{enumerate}\setlength{\itemsep}{5pt}
@@
 \begin{itemize}\setlength{\itemsep}{8pt}
-\item Parameters are from Atkinson et al.\ (2019), and are chosen to be characteristic of U.S. data
-\item For the model without capital, $\rho_s = 0.006$ %To allow the GHLS algorithm to converge
+\item <2-|handout:1>Parameters are from Atkinson et al.\ (2019), and are chosen to be characteristic of U.S. data
+\item <3-|handout:1>For the model without capital, $\rho_s = 0.006$ %To allow the GHLS algorithm to converge
 \end{itemize}
@@
 \begin{itemize}\setlength{\itemsep}{10pt}
-  \item State variables: $g_t$, $s_t$, $mp_t$, $i^n_{t-1}$
-  \item Number of grid points: $N_g$, $N_{s}$, $N_{mp}$, $N_{i^n}$
-  \item Grid boundaries: 
+  \item <1-|handout:1>State variables: $g_t$, $s_t$, $mp_t$, $i^n_{t-1}$
+  \item <2-|handout:1>Number of grid points: $N_g$, $N_{s}$, $N_{mp}$, $N_{i^n}$
+  \item <3-|handout:1>Grid boundaries: 
 \begin{center}
@@
 \end{center}
-  \item Create evenly spaced grids:
+  \item <4-|handout:1>Create evenly spaced grids:
   \begin{center}
@@
   \end{center}
-  \item State space contains $N=N_g\times N_s\times N_{mp}\times N_{i^n}$ nodes
-  \item Create an array for each state variable, where every position is a unique permutation of the state space:
+  \item <5-|handout:1>State space contains $N=N_g\times N_s\times N_{mp}\times N_{i^n}$ nodes
+  \item <6-|handout:1>Create an array for each state variable, where every position is a unique permutation of the state space:
   \begin{center}
@@
 \begin{itemize}\setlength{\itemsep}{12pt}
-  \item True RE solution only exists in special cases %(e.g., $\delta=1$)
-  \item Goal: Find an approximating function that maps the state space to the optimal decision rule for consumption:
+  \item <1-|handout:1>True RE solution only exists in special cases %(e.g., $\delta=1$)
+  \item <2-|handout:1>Goal: Find an approximating function that maps the state space to the optimal decision rule for consumption:
   \begin{gather*}
@@
   \end{gather*}
-  \item Basic elements of the algorithm:
+  \item <3-|handout:1>Basic elements of the algorithm:
   \begin{enumerate}\setlength{\itemsep}{6pt}
@@
 \begin{itemize}\setlength{\itemsep}{8pt}
-  \item Piecewise Linear Interpolation: 4 state variables $(g,s,mp,i^n)$
-  \item Goal: Find the policy function value ${\cal{P}}_c(g',s',mp',{i^n}')$
-  \item We have policy function values on nearest 24 nodes
+  \item <1-|handout:1>Piecewise Linear Interpolation: 4 state variables $(g,s,mp,i^n)$
+  \item <2-|handout:1>Goal: Find the policy function value ${\cal{P}}_c(g',s',mp',{i^n}')$
+  \item <3-|handout:1>We have policy function values on nearest 24 nodes
   \begin{gather*}
@@
   once we determine the grid indices, $i,j,k,l$
-  \item Locate the grid point left of $x'$, $x \in \{g,s,mp,i^n\}$ %nearest point to the left
+\item   <4-|handout:1>Locate the grid point left of $x'$, $x \in \{g,s,mp,i^n\}$ %nearest point to the left
    \begin{gather*}
@@
 \begin{itemize}\setlength{\itemsep}{10pt}
-  \item A general class of polynomials can be written as:
+  \item <1-|handout:1>A general class of polynomials can be written as:
   \begin{gather*}
@@
   \end{gather*}
-  \item Linear interpolation is a special case of this general class (i.e., $n=1$, $\varphi_i(x)=x^i$, and weights chosen appropriately)
-  \item Can also use bases consisting of orthogonal polynomials (e.g., Chebyshev Polynomials)
+  \item <2-|handout:1>Linear interpolation is a special case of this general class (i.e., $n=1$, $\varphi_i(x)=x^i$, and weights chosen appropriately)
+  \item <3-|handout:1>Can also use bases consisting of orthogonal polynomials (e.g., Chebyshev Polynomials)
 \end{itemize}
@@
 \begin{enumerate}\setlength{\itemsep}{10pt}
-  \item Calculate $z(s')$ for each realization of the state
-  \item Find the updated policy function, $n(s')$, for each state
-  \item Numerical Integration:
+  \item <1-|handout:1>Calculate $z(s')$ for each realization of the state
+  \item <2-|handout:1>Find the updated policy function, $n(s')$, for each state
+  \item <3-|handout:1>Numerical Integration:
   \begin{itemize}\setlength{\itemsep}{5pt}
@@
 \begin{itemize}\setlength{\itemsep}{8pt}
-  \item Used to approximate an exogenous $AR(1)$ process
-  \item Kopecky and Suen (2010) show the Rouwenhorst method outperforms other approximations of an $AR(1)$ process
-  \item The approximation is a Markov switching process like the time-varying intercept example, but with $n$ states
-  \item The method determines the bounds of the exogenous state variables, the nodes, and the transition probabilities
-  \item Let $z\sim AR(1)$ with persistence $\rho$, mean $\mu_z$, and variance %Idea for approximation of an AR(1) process
+  \item<1-|handout:1> Used to approximate an exogenous $AR(1)$ process
+  \item <2-|handout:1>Kopecky and Suen (2010) show the Rouwenhorst method outperforms other approximations of an $AR(1)$ process
+  \item <3-|handout:1>The approximation is a Markov switching process like the time-varying intercept example, but with $n$ states
+  \item <4-|handout:1>The method determines the bounds of the exogenous state variables, the nodes, and the transition probabilities
+  \item <5-|handout:1>Let $z\sim AR(1)$ with persistence $\rho$, mean $\mu_z$, and variance %Idea for approximation of an AR(1) process
   \begin{gather*}
@@
   \end{gather*}
-  \item The $n$ states for the discretized process $z$ are evenly spaced on $[\mu_z-\sigma_z\sqrt{n-1},\mu_z+\sigma_z\sqrt{n-1}]$
+  \item   <6-|handout:1>The $n$ states for the discretized process $z$ are evenly spaced on $[\mu_z-\sigma_z\sqrt{n-1},\mu_z+\sigma_z\sqrt{n-1}]$
 \end{itemize}
@@
 \begin{itemize}\setlength{\itemsep}{10pt}
-\item Let the vector of policy functions at time $t$ be denoted $\textbf{pf}_t$ and the realization on node $d$ be denoted $\textbf{pf}_t(d)$
-\item The regime-indexed policy functions are as follows: 
+\item <1-|handout:1>Let the vector of policy functions at time $t$ be denoted $\textbf{pf}_t$ and the realization on node $d$ be denoted $\textbf{pf}_t(d)$
+\item <2-|handout:1>The regime-indexed policy functions are as follows: 
 \begin{gather*}
@@
 
-\item Solve the linear model using Sims's (2002) \texttt{gensys} algorithm. 
-\item Solve the nonlinear model using fixed point iteration. For each node in the state space $d \in \{1,\dots,D\}:$
+\item <2-|handout:1>Solve the linear model using Sims's (2002) \texttt{gensys} algorithm. 
+\item <3-|handout:1>Solve the nonlinear model using fixed point iteration. For each node in the state space $d \in \{1,\dots,D\}:$
 \begin{enumerate}\setlength{\itemsep}{2pt}
-\item Solve for the variables dated at time $t$ given $\textbf{pf}_t$ and $\textbf{z}_t$.
+\item <4-|handout:1>Solve for the variables dated at time $t$ given $\textbf{pf}_t$ and $\textbf{z}_t$.
 %For GHLS, if $i_t > 1$, update time $t$ variables with non-ZLB policy functions; if $i_t \leq 1$, update time $t$ variables with ZLB policy functions.
-\item  Linearly interpolate the policy functions at the updated state variables $\textbf{z}_{t+1}$ to obtain $\textbf{pf}_{t+1}(m)$ on every integration node $m \in \{1,\dots,M\}$.% For GHLS, interpolate both non-ZLB and ZLB policy functions.
-\item Given the interpolated policy functions $\{\textbf{pf}(m)\}_{m=1}^M$, and integration nodes and weights provided by the Rouwenhorst method, approximate the expectation operators for the model.
+\item  <5-|handout:1>Linearly interpolate the policy functions at the updated state variables $\textbf{z}_{t+1}$ to obtain $\textbf{pf}_{t+1}(m)$ on every integration node $m \in \{1,\dots,M\}$.% For GHLS, interpolate both non-ZLB and ZLB policy functions.
+\item <6-|handout:1>Given the interpolated policy functions $\{\textbf{pf}(m)\}_{m=1}^M$, and integration nodes and weights provided by the Rouwenhorst method, approximate the expectation operators for the model.
 %For GHLS, determine whether the model is at the ZLB at each node, and construct the policy function grids according to .
-\item Back out the policy functions $\textbf{pf}_t(d)$ from the expectation operators and time $t+1$ variables. %For GHLS, solve for regime-indexed polynomials based on 
+\item <7-|handout:1>Back out the policy functions $\textbf{pf}_t(d)$ from the expectation operators and time $t+1$ variables. %For GHLS, solve for regime-indexed polynomials based on 
 \end{enumerate}
-\item Repeat step 2 until the maximum distance between successive approximations of the policy functions is below $10^{-6}$. 
+\item <8-|handout:1>Repeat step 2 until the maximum distance between successive approximations of the policy functions is below $10^{-6}$. 
 \end{itemize}
@@
 %We use Euler equation errors to measure the accuracy of our solutions.
-\item Measure of solution accuracy
-\item To approximate errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method %to allow exogenous variables to have realizations between grid points. 
-\item The Euler equation errors are represented in absolute value of the errors in base 10 logarithms
+\item <1-|handout:1>Measure of solution accuracy
+\item <2-|handout:1>To approximate errors between nodes, we use Gauss-Hermite quadrature instead of the Rouwenhorst method %to allow exogenous variables to have realizations between grid points. 
+\item <3-|handout:1>The Euler equation errors are represented in absolute value of the errors in base 10 logarithms
 \begin{itemize}\setlength{\itemsep}{2pt}
@@
 \end{itemize}
-\item Obtaining Euler equation errors:
+\item <4-|handout:1>Obtaining Euler equation errors:
 \begin{itemize}\setlength{\itemsep}{2pt}
@@
 \begin{itemize}\setlength{\itemsep}{14pt}
-  \item Any calculations that are not dependent on the results of other calculations can be performed in parallel (e.g., solving for policy values at each node in the state space)
-  \item We replace \texttt{for} loops with \texttt{parfor} loops where applicable. This tells MATLAB to distribute each step in the loop across the specified number of processors
+  \item <1-|handout:1>Any calculations that are not dependent on the results of other calculations can be performed in parallel (e.g., solving for policy values at each node in the state space)
+  \item <2-|handout:1>We replace \texttt{for} loops with \texttt{parfor} loops where applicable. This tells MATLAB to distribute each step in the loop across the specified number of processors
 \end{itemize}
@@
 \begin{itemize}\setlength{\itemsep}{10pt}
-\item The solution times
+\item <1-|handout:1>The solution times
 were computed with multi-core processing using the Parallel Computing Toolbox
-\item We implemented the interpolation steps of the algorithm in Fortran with MATLAB
+\item<2-|handout:1> We implemented the interpolation steps of the algorithm in Fortran with MATLAB
 executable functions (MEX) provided in the companion toolbox to \hyperlink{RTW}{\color{black}{Richter et al.
@@
  \begin{itemize}\setlength{\itemsep}{8pt}
-\item RMSE (root mean square error)
-\item Mean percent error from linear policy functions
-\item  GHLS smoother for model without capital; ART smoother for model with capital
+\item <1-|handout:1>RMSE (root mean square error)
+\item <2-|handout:1>Mean percent error from linear policy functions
+\item  <3-|handout:1>GHLS smoother for model without capital; ART smoother for model with capital
 \end{itemize}
@@
 \begin{itemize}\setlength{\itemsep}{8pt}
-\item During the Great Recession, policy rates hit zero, calling into question traditional solution methods
-\item There is a literature in solving nonlinear models, but not much work comparing nonlinear solution methods
-\item This paper discusses the impact of regime-indexing the policy functions on a nonlinear solution algorithm
+\item <1-|handout:1>During the Great Recession, policy rates hit zero, calling into question traditional solution methods
+\item <2-|handout:1>There is a literature in solving nonlinear models, but not much work comparing nonlinear solution methods
+\item <3-|handout:1>This paper discusses the impact of regime-indexing the policy functions on a nonlinear solution algorithm
 \begin{enumerate}\setlength{\itemsep}{4pt}
-\item Motivation for directly approximating the policy functions from Atkinson et al.\ (2019)
-\item Motivation for regime-indexing the policy functions from Gust et al.\ (2017). They claim that regime-indexed policy functions are smoother and easier to approximate
+\item Example of directly approximating the policy functions from Atkinson et al.\ (2019)
+\item Example of for regime-indexing the policy functions from Gust et al.\ (2017). They claim that regime-indexed policy functions are smoother and easier to approximate
 \end{enumerate}
@@
 \begin{itemize}\setlength{\itemsep}{10pt}
-\item Key takeaways:
+\item <1-|handout:1>Key takeaways:
 \begin{itemize}\setlength{\itemsep}{4pt}
@@
 \end{itemize}
-\item Extensions:
+\item <2-|handout:1>Extensions:
 \begin{itemize}\setlength{\itemsep}{4pt}

### 2019-05-29 Paper/Paper.tex
Final edits

@@
 
-The \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method approximates policy functions underlying the model's decision rule using an antistropic Smolyak method with Chebyshev polynomials.
-(See \hyperlink{Judd2}{\color{black}{Judd et al.\, 2014}} for a discussion of antistropic Smolyak methods).
+The \hyperlink{Gust}{\color{black}{Gust et al.\ (2017)}} solution method approximates policy functions underlying the model's decision rule using an anisotropic Smolyak method with Chebyshev polynomials.
+(See \hyperlink{Judd2}{\color{black}{Judd et al.\, 2014}} for a discussion of anisotropic Smolyak methods).
 They approximate the exogenous state variables using Gauss-Hermite quadrature.
@@
       \label{eq:16}
-  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{gdp}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}), 0 \leq \rho_i < 1, \varepsilon_i \sim \mathds{N}(0,1),
+  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{g}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}), 0 \leq \rho_i < 1, \varepsilon_i \sim \mathds{N}(0,1),
   \end{gather}
-where $y^{gdp}$ is real GDP (i.e., output, $y$, minus the resources lost due to adjustment costs, $adj^p$), $i^n$ is the gross notional interest rate, $\bar i$ is the target values of the nominal interest rate, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps.
+where $y^{g}$ is output growth, $i^n$ is the gross notional interest rate, $\bar{\imath}$ is the target values of the nominal interest rate, and $\phi_\pi$ and $\phi_y$ are the responses to the inflation and output growth gaps.
 A more negative net notional rate indicates that the central bank is more constrained.\\
@@
 The Frisch labor supply elasticity $1/\eta$ is set to 3 to match the macro estimate in \hyperlink{Peterman}{\color{black}{Peterman (2016)}}.
-The price elasticity of substitution $\theta$ is set to 6, matching GHLS and corresponding to to a 20\% average markup.
+The price elasticity of substitution $\theta$ is set to 6, matching GHLS and corresponding to a 20\% average markup.
 Steady-state labor hours $\bar{n}$ is set to 1/3 of available time.

### 2019-05-29 Presentation/Presentation.tex
Final edits

@@
-%\documentclass[handout, bigger]{beamer} %For Handouts
+%\documentclass[handout, 11pt]{beamer} %For Handouts
 \documentclass[11pt]{beamer}
@@
 
-%===============================================================================================================
-
-\begin{frame}\frametitle{Nonlinear Solution Methods}
-\begin{itemize}\setlength{\itemsep}{10pt}
-	\item  <1-|handout:1>As it is important to incorporate all historical data and yield acurate parameter values and predictions, the path forward seems to be in fully nonlinear models
-	\item <2-|handout:1>Solving nonlinear models with projection methods (e.g. Aruoba et al., 2018; Ferna\'ndez-Villaverde et al., 2015).
-	\item  <3-|handout:1>Researchers have used different methods for solving fully nonlinear models:
-	\begin{enumerate} \setlength{\itemsep}{4pt}
-		\item  Policy function iteration with linear interpolation (e.g., Plante et al., 2018; Richter and Throckmorton, 2016).
-		\item  Alternate approximating functions: regime-indexed policy functions (Gust et al., 2017), piecewise smooth policy functions (Aruoba et al. 2018)
-		\item  Alternate grid construction: Smolyak method with Chebyshev polynomials (e.g., Gust et al., 2017; Ferna\'ndez-Villaverde et al. 2015; Aruoba et al., 2018)
-	\end{enumerate}
-\end{itemize}
-\end{frame}
-
-%=========================================================================
-\begin{frame}\frametitle{Two Solution Methods}
-\begin{table}\scriptsize
-    \renewcommand*{\arraystretch}{1.4}
-    \setlength{\tabcolsep}{6pt}      
-  \begin{tabularx}{\textwidth}{l | X | X}
-    \hline
-    & \textbf{Atkinson et al.\ (2019)} & \textbf{Gust et al.\ (2017)} \\ \hline
-    	Discretization Method & Evenly-spaced grid points & Smolyak Method\\
-	Policy Function Evaluation & Linear Interpolation & Chebyshev Polynomials \\
-	Integration Method & Rouwenhorst & Gauss-Hermite quadrature  \\ \hline
-\end{tabularx}
-\end{table}\normalsize
-\begin{itemize}\setlength{\itemsep}{10pt}
-\item  <2-|handout:1>Evenly-spaced grid points work well with linear interpolation
-\item  <3-|handout:1>The Smolyak method is optimal for Chebyshev polynomials
-\item  <4-|handout:1>The Rouwenhorst (1995) method improves approximation on exogenous dimensions when the driving processes are autoregressive
-\end{itemize}
-
-\end{frame}
-%=========================================================================
-\begin{frame}\frametitle{Atkinson et al.\ (2019)}
-\begin{itemize}\setlength{\itemsep}{10pt}
-\item <1-|handout:1> Time iteration with linear interpolation
-\item <2-|handout:1>Directly approximates policy functions
-\item <3-|handout:1> State space features evenly-spaced nodes
-\item<4-|handout:1>  Exogenous variables are approximated with the Markov chain from Rouwenhorst (1995)
-  \begin{itemize}\setlength{\itemsep}{4pt}
-\item Only requires interpolation along the dimensions of the endogenous state variables
-\end{itemize}
-\end{itemize}
-\end{frame}
-%=========================================================================
-\begin{frame}\frametitle{Gust et al.\ (2017)}
-\begin{itemize}\setlength{\itemsep}{6pt}
-\item  <1-|handout:1>Approximates policy functions using an antistropic Smolyak method with Chebyshev polynomials
-\item  <2-|handout:1>Approximates exogenous state variables using Gauss-Hermite quadrature%why if we know Rouwenhorst is better?
-\item  <3-|handout:1>Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, building on Christiano and Fisher (2000)
-  \begin{itemize}\setlength{\itemsep}{4pt}
-\item  Policy functions feature a kink or non-differentiability at the ZLB and regime-indexing the policy functions will yield smoother functions
-\item Low-order Chebyshev polynomials perform better on smoother functions and are inexpensive to compute
-\end{itemize}
-\end{itemize}
-\end{frame}
-%=========================================================================
-\begin{frame}\frametitle{This Project}
-\begin{itemize}\setlength{\itemsep}{8pt}
-\item  <1-|handout:1>In this project, we consider how splitting up the policy functions conditional on the ZLB impacts the speed and accuracy of the solution of a nonlinear model
-\item  <2-|handout:1>We use policy function iteration on a fixed point with linear interpolation
-\item  <3-|handout:1>Atkinson et al.\ (2019) provides the motivation for a single policy function;  Gust et al.\ (2017) provides the motivation for a regime-indexed policy function
-\item <4-|handout:1> Solution algorithm based on Atkinson et al.\ (2019) denoted henceforth as ART; solution algorithm based on Gust et al.\ (2017) denoted henceforth as GHLS
-\end{itemize}
-\end{frame}
-%=========================================================================
-\begin{frame}\frametitle{Our Solution Algorithm} %NEED TO PUT SOME ABOUT GHLS?
-\begin{itemize}\setlength{\itemsep}{8pt}
-\item   <1-|handout:1>Construct the state space with evenly-spaced nodes and approximate exogenous state variables with Rouwenhorst (1995)
-\item  <2-|handout:1>Obtain initial conjectures for a set of policy functions from the log-linear solution
-\item  <3-|handout:1>Using a fixed point iteration scheme, linearly interpolate and numerically integrate the policy functions each step
-\begin{itemize}
-\item For ART portion, we update a single policy function, and for the GHLS portion we update regime-indexed policy functions
-\end{itemize}
-\item <5-|handout:1> The algorithm converges once the maximum distance between successive guesses of policy functions falls below a convergence criterion
-
-\end{itemize}
-\end{frame}
-%=========================================================================
-\begin{frame}\frametitle{Motivation for Regime-Indexed Policy Functions}
-\begin{itemize}\setlength{\itemsep}{6pt}
-\item  <1-|handout:1>The interest rate enters directly in the consumption Euler equation
-\begin{gather*}
-1 =  E_t[\beta(c_t/c_{t+1})(s_ti_t/\pi_t)],
-\end{gather*}
-where $E_t$ is the expectation operator, $0 < \beta < 1$ is the discount factor, and $c_t$, $s_t$, $i_t$, and $\pi_t$ are consumption, the risk premium, the interest rate, and inflation at time $t$. 
-\begin{itemize} \small
-\item $\beta(c_t/c_{t+1})$ is a stochastic discount factor used to value future real income
-\item $s_ti_t/\pi_t$ is a real interest rate on a one-period bond
-\end{itemize}\normalfont
-\item <2-|handout:1> At the ZLB, the presence of the interest rate creates a nonlinearity in the consumption Euler equation 
-\item <3-|handout:1> $c_t$ depends directly on the interest rate
-\end{itemize}
-\end{frame}
 %=========================================================================
@@
   \end{gather*} %$x_t^g$ is investment growth relative to its steady-state and $\nu \geq 0$ scales the cost.
-\item <2-|handout:1>The FOCs to each household's constrained optimization problem are
+\item <2-|handout:1>The FOCs to the representative household's constrained optimization problem are
 \scriptsize
@@
   q_t = \beta E_t[(\lambda_t/\lambda_{t+1})(r^k_{t+1}+(1-\delta)q_{t+1})],\\
-  1 = q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] + \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)],\\
-  \varphi(\pi_t^{gap}-1)\pi_t^{gap} = 1-\theta + \theta mc_t + \beta\varphi E_t[(\lambda_t/\lambda_{t+1})(\pi_{t+1}^{gap}-1)\pi_{t+1}^{gap}(y_{t+1}/y_t)].
+  1 = q_t[1-\nu(x^g_t-1)^2/2 - \nu(x_t^g-1)x_t^g] + \nu\beta\bar{g}E_t[q_{t+1}(\lambda_t/\lambda_{t+1})(x^g_{t+1})^2(x^g_{t+1}-1)].\\
 \end{gather*} %where $1/\lambda$ is the marginal utility of consumption and $q$ is Tobin's q 
@@
     i_t=\max\{1,i_t^n\},\\
-  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{gdp}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}). 
+  i_t^n=(i^n_{t-1})^{\rho_i}(\bar{\imath}(\pi^{gap}_t)^{\phi_\pi}(y^{g}_{t})^{\phi_y})^{1-\rho_i}\exp(\sigma_i\varepsilon_{i,t}). 
 \end{gather*}
@@
 \item <2-|handout:1>Parameters are from Atkinson et al.\ (2019), and are chosen to be characteristic of U.S. data
-\item <3-|handout:1>For the model without capital, $\rho_s = 0.006$ %To allow the GHLS algorithm to converge
+\item <3-|handout:1>For the model without capital, $\sigma_s = 0.006$ %To allow the GHLS algorithm to converge
 \end{itemize}
 \end{frame}
+%===============================================================================================================
+
+\begin{frame}\frametitle{Nonlinear Solution Methods}
+\begin{itemize}\setlength{\itemsep}{10pt}
+	\item  <1-|handout:1>As it is important to incorporate all historic data and yield accurate parameter values and predictions, the path forward seems to be in fully nonlinear models
+	\item <2-|handout:1>Solving nonlinear models with projection methods:
+\begin{enumerate}
+		\item  <3-|handout:1>Policy function iteration with linear interpolation on an evenly spaced grid (e.g., Plante et al., 2018; Richter and Throckmorton, 2016).
+		\item  <3-|handout:1>Alternate approximating functions: regime-indexed policy functions (Gust et al., 2017), piecewise smooth policy functions (Aruoba et al. 2018)
+		\item  <3-|handout:1>Alternate grid construction and policy function evaluation method: Smolyak method with Chebyshev polynomials (e.g., Gust et al., 2017; Ferna\'ndez-Villaverde et al.
+2015; Aruoba et al., 2018)
+	\end{enumerate}
+\end{itemize}
+\end{frame}
+
+%=========================================================================
+\begin{frame}\frametitle{Two Solution Methods}
+\begin{table}\scriptsize
+    \renewcommand*{\arraystretch}{1.4}
+    \setlength{\tabcolsep}{6pt}      
+  \begin{tabularx}{\textwidth}{l | X | X}
+    \hline
+    & \textbf{Atkinson et al.\ (2019)} & \textbf{Gust et al.\ (2017)} \\ \hline
+    	Discretization Method & Evenly-spaced grid points & Smolyak Method\\
+	Policy Function Evaluation & Linear Interpolation & Chebyshev Polynomials \\
+	Integration Method & Rouwenhorst & Gauss-Hermite quadrature  \\ \hline
+\end{tabularx}
+\end{table}\normalsize
+\begin{itemize}\setlength{\itemsep}{10pt}
+\item  <2-|handout:1>Evenly-spaced grid points work well with linear interpolation
+\item  <3-|handout:1>The Smolyak method is optimal for Chebyshev polynomials
+\item  <4-|handout:1>The Rouwenhorst (1995) method improves approximation on exogenous dimensions when the driving processes are autoregressive
+\end{itemize}
+
+\end{frame}
+%=========================================================================
+\begin{frame}\frametitle{Atkinson et al.\ (2019)}
+\begin{itemize}\setlength{\itemsep}{10pt}
+\item <1-|handout:1> Time iteration with linear interpolation
+\item <2-|handout:1>Directly approximates policy functions
+\item <3-|handout:1> State space features evenly-spaced nodes
+\item<4-|handout:1>  Exogenous variables are approximated with the Markov chain from Rouwenhorst (1995)
+  \begin{itemize}\setlength{\itemsep}{4pt}
+\item Only requires interpolation along the dimensions of the endogenous state variables
+\end{itemize}
+\end{itemize}
+\end{frame}
+%=========================================================================
+\begin{frame}\frametitle{Gust et al.\ (2017)}
+\begin{itemize}\setlength{\itemsep}{6pt}
+\item  <1-|handout:1>Approximates policy functions using an anisotropic Smolyak method with Chebyshev polynomials
+\item  <2-|handout:1>Approximates exogenous state variables using Gauss-Hermite quadrature%why if we know Rouwenhorst is better?
+\item  <3-|handout:1>Instead of directly computing the policy functions, they estimate functions at and away from the ZLB, building on Christiano and Fisher (2000)
+  \begin{itemize}\setlength{\itemsep}{4pt}
+\item  Policy functions feature a kink or non-differentiability at the ZLB and regime-indexing the policy functions will yield smoother functions
+\item Low-order Chebyshev polynomials perform better on smoother functions and are inexpensive to compute
+\end{itemize}
+\end{itemize}
+\end{frame}
+%=========================================================================
+\begin{frame}\frametitle{This Project}
+\begin{itemize}\setlength{\itemsep}{8pt}
+\item  <1-|handout:1>In this project, we consider how splitting up the policy functions conditional on the ZLB impacts the speed and accuracy of the solution of a nonlinear model
+\item  <2-|handout:1>We use policy function iteration on a fixed point with linear interpolation
+\item  <3-|handout:1>Atkinson et al.\ (2019) directly computes the policy functions;  Gust et al.\ (2017) indirectly computes the policy functions through regime-indexed policy functions
+\item <4-|handout:1> Solution algorithm based on Atkinson et al.\ (2019) denoted henceforth as ART; solution algorithm based on Gust et al.\ (2017) denoted henceforth as GHLS
+\end{itemize}
+\end{frame}
+%=========================================================================
+\begin{frame}\frametitle{Motivation for Regime-Indexed Policy Functions}
+\begin{itemize}\setlength{\itemsep}{6pt}
+\item  <1-|handout:1>The interest rate enters directly in the consumption Euler equation
+\begin{gather*}
+1 =  E_t[\beta(c_t/c_{t+1})(s_ti_t/\pi_t)],
+\end{gather*}
+where $E_t$ is the expectation operator, $0 < \beta < 1$ is the discount factor, and $c_t$, $s_t$, $i_t$, and $\pi_t$ are consumption, the risk premium, the interest rate, and inflation at time $t$. 
+\begin{itemize} \small
+\item $\beta(c_t/c_{t+1})$ is a stochastic discount factor used to value future real income
+\item $s_ti_t/\pi_t$ is a real interest rate on a one-period bond
+\end{itemize}\normalfont
+\item <2-|handout:1> At the ZLB, the presence of the interest rate creates a nonlinearity in the consumption Euler equation 
+\item <3-|handout:1> $c_t$ depends directly on the interest rate
+\end{itemize}
+\end{frame}%=========================================================================
+\begin{frame}\frametitle{Our Solution Algorithm} %NEED TO PUT SOME ABOUT GHLS?
+\begin{itemize}\setlength{\itemsep}{8pt}
+\item   <1-|handout:1>Construct the state space with evenly-spaced nodes and approximate exogenous state variables with Rouwenhorst (1995)
+\item  <2-|handout:1>Obtain initial conjectures for a set of policy functions from the log-linear solution
+\item  <3-|handout:1>Using a fixed point iteration scheme, linearly interpolate and numerically integrate the policy functions each step
+\begin{itemize}
+\item For ART portion, we update a single policy function, and for the GHLS portion we update regime-indexed policy functions
+\end{itemize}
+\item <5-|handout:1> The algorithm converges once the maximum distance between successive guesses of policy functions falls below a convergence criterion
+
+\end{itemize}
+\end{frame}
+
 %===================================================================================
@@
 %===============================================================================================================
-\begin{frame}\frametitle{Solving the Model}
 
-\begin{enumerate}\setlength{\itemsep}{10pt}
-  \item <1-|handout:1>Calculate $z(s')$ for each realization of the state
-  \item <2-|handout:1>Find the updated policy function, $n(s')$, for each state
-  \item <3-|handout:1>Numerical Integration:
-  \begin{itemize}\setlength{\itemsep}{5pt}
-    \item First integrate across the continuous random variable, $z$, conditional on the future realizations of the discrete stochastic variable, $s'$.%, to obtain:
+\begin{frame}\frametitle{Rouwenhorst Method}
+
+\begin{itemize}\setlength{\itemsep}{12pt}
+  \item<1-|handout:1> Used to approximate an exogenous $AR(p)$ process
+  \item <2-|handout:1>Kopecky and Suen (2010) show the Rouwenhorst method outperforms other approximations of an $AR(1)$ process
+  \item <3-|handout:1>The method determines the bounds of the exogenous state variables, the nodes, and the transition probabilities
+\end{itemize}
+\end{frame}
+
+%===============================================================================================================
+%===============================================================================================================
+
+\begin{frame}\frametitle{Example: Time Iteration}
+
+On iteration $q$, solve for the ${\cal P}_c^q(g,s,mp,i^n)$ that \textit{satisfies} equilibrium
+\begin{enumerate}\setlength{\itemsep}{12pt}
+  \item<1-|handout:1> Use log-linear solution on each node to obtain ${\cal P}_c^0$
+  \begin{itemize}
+    \item Local: ${\cal P}_c^1={\cal P}_c^0$
+    \item Global: set initial basis $\hat{\eta}^0$%$\hat{\eta}^0 = ({X^T}X)^{-1}{X^T}\operatorname{vec}({\cal P}_c^0)$ so ${\cal P}_c^1=X\hat{\eta}^0$
+  \end{itemize}
+  \item<2-|handout:1> Solve for $g'$, $s'$, $mp'$, ${i^n}'$, given $\varepsilon_g'$, $\varepsilon_s'$, $\varepsilon_i'$ \label{updated vars}
+  \item<3-|handout:1> Find ${\cal P}_c^q(g',s',mp',{i^n}')$ given the updated state
+  \begin{itemize}
+    \item Local: use piecewise linear interpolation
+    \item Global: update the basis %so ${\cal P}_c^q(g',s',mp',{i^n}') = X'\hat{\eta}^{q-1}$
+  \end{itemize}
+  \item<4-|handout:1> Evaluate expectations (Rouwenhorst or Gauss Hermite) \label{expectation}
     %\begin{gather*}
-         % E[\Phi(z')|s'=1], \quad E[\Phi(z')|s'=2]
+      %E[\Phi(z')] = \beta E[{\cal P}_c^q(k',z')^{-\sigma}(\alpha z'k'^{\alpha-1}+1-\delta)]
     %\end{gather*}
-    \item Then weight the conditional expectations by their corresponding likelihood. %The conditional expectations are:
-  %  \begin{gather*}
-    %  E\left[\Phi(z')|s = i\right] = p_{i1}E[\Phi(z')|s'=1] + p_{i2}E[\Phi(z')|s'=2]
-   % \end{gather*}
-  \end{itemize}
 \end{enumerate}
 
+\end{frame}
+\setcounter{savedenumi}{\value{enumi}}
+
+%===============================================================================================================
+
+\begin{frame}\frametitle{Example: Time Iteration}
+
+\begin{enumerate}
+  \setcounter{enumi}{\value{savedenumi}}
+  \item<1-|handout:1> Use nonlinear solver to find a ${\cal P}_c^q(g,s,mp,i^n)$ that satisfies the consumption Euler equation%, ${\cal P}_c^q(g,s,mp,i^n)^{-\sigma}=E[\Phi(z')]$.
+  \item<2-|handout:1> Update policy function \label{update}
+  \begin{itemize}
+    \item Local: ${\cal P}_c^{q+1}={\cal P}_c^q$
+    \item Global: update basis $\hat{\eta}^q$  %$\hat{\eta}^q = ({X^T}X)^{-1}{X^T}\operatorname{vec}({\cal P}_c^q(g,s,mp,i^n))$, ${\cal P}_c^{q+1}(g,s,mp,i^n) = X\hat{\eta}^{q}$
+  \end{itemize}
+  \item<3-|handout:1> Calculate distance between updates
+  \begin{itemize}
+    \item Local: $\textrm{dist} = {\cal P}_c^q(g,s,mp,i^n) - {\cal P}_c^{q-1}(g,s,mp,i^n)$
+    \item Global: $\textrm{dist} = \hat{\eta}^q - \hat{\eta}^{q-1}$
+  \end{itemize}
+  \item<4-|handout:1> If $|\textrm{dist}| < \textrm{tol}$, then stop. If not, then set $q=q+1$ and repeat steps 2-7 using ${\cal P}_c^{q+1}$ as the new initial conjecture. \label{tol criterion}
+\end{enumerate}
+\onslide<5-|handout:1>{\underline{Advantage}: Satisfies the equilibrium system on each node and nodes can be run in parallel.\\[6pt]
+\underline{Disadvantage}: Nonlinear solver must execute on each node.}
 \end{frame}
@@
 
-\begin{frame}\frametitle{Rouwenhorst Method}
+\begin{frame}\frametitle{Example: Fixed-Point Iteration}
 
-\begin{itemize}\setlength{\itemsep}{8pt}
-  \item<1-|handout:1> Used to approximate an exogenous $AR(1)$ process
-  \item <2-|handout:1>Kopecky and Suen (2010) show the Rouwenhorst method outperforms other approximations of an $AR(1)$ process
-  \item <3-|handout:1>The approximation is a Markov switching process like the time-varying intercept example, but with $n$ states
-  \item <4-|handout:1>The method determines the bounds of the exogenous state variables, the nodes, and the transition probabilities
-  \item <5-|handout:1>Let $z\sim AR(1)$ with persistence $\rho$, mean $\mu_z$, and variance %Idea for approximation of an AR(1) process
-  \begin{gather*}
-    \sigma_z^2 = \sigma_\varepsilon^2/(1-\rho^2).
-  \end{gather*}
-  \item   <6-|handout:1>The $n$ states for the discretized process $z$ are evenly spaced on $[\mu_z-\sigma_z\sqrt{n-1},\mu_z+\sigma_z\sqrt{n-1}]$
-\end{itemize}
-
+Solve for the ${\cal P}_c^q(g,s,mp,i^n)$ \textit{implied} by the equilibrium system
+\begin{enumerate}
+  \item<1-|handout:1> Obtain an initial conjecture\\(step 1 in the time iteration algorithm)
+  \item<2-|handout:1> Calculate updated variables and expectations\\(steps \ref{updated vars}-\ref{expectation} in the time iteration algorithm)
+  \item<3-|handout:1> Calculate ${\cal P}_c^q(g,s,mp,i^n)$ on each node %=(E[\Phi(z')])^{-1/\sigma}$ on each node
+  \item<4-|handout:1> Execute steps \ref{update}-\ref{tol criterion} in the time iteration algorithm
+\end{enumerate}
+\onslide<5-|handout:1>{\underline{Advantage}: Does not require a loop, since all of the nodes are evaluated simultaneously.\\[6pt]
+\underline{Disadvantage}: Algorithm is less stable because it does not solve for the optimal policy function on each node.\\[6pt]}
 \end{frame}
@@
 % by discretizing the endogenous state variables and using \hyperlink{Rouwenhorst}{\color{black}{Rouwenhorst (1995)}} method to approximate the exogenous processes for $s_t$, $g_t$, and $\varepsilon_{i,t}$.
-\begin{itemize}\setlength{\itemsep}{8pt}
+\begin{enumerate}\setlength{\itemsep}{8pt}
 
@@
 \begin{enumerate}\setlength{\itemsep}{2pt}
-\item <4-|handout:1>Solve for the variables dated at time $t$ given $\textbf{pf}_t$ and $\textbf{z}_t$.
+\item[a.] <4-|handout:1>Solve for the variables dated at time $t$ given $\textbf{pf}_t$ and $\textbf{z}_t$.
 %For GHLS, if $i_t > 1$, update time $t$ variables with non-ZLB policy functions; if $i_t \leq 1$, update time $t$ variables with ZLB policy functions.
-\item  <5-|handout:1>Linearly interpolate the policy functions at the updated state variables $\textbf{z}_{t+1}$ to obtain $\textbf{pf}_{t+1}(m)$ on every integration node $m \in \{1,\dots,M\}$.% For GHLS, interpolate both non-ZLB and ZLB policy functions.
-\item <6-|handout:1>Given the interpolated policy functions $\{\textbf{pf}(m)\}_{m=1}^M$, and integration nodes and weights provided by the Rouwenhorst method, approximate the expectation operators for the model.
+\item[b.]  <5-|handout:1>Linearly interpolate the policy functions at the updated state variables $\textbf{z}_{t+1}$ to obtain $\textbf{pf}_{t+1}(m)$ on every integration node $m \in \{1,\dots,M\}$.% For GHLS, interpolate both non-ZLB and ZLB policy functions.
+\item[c.] <6-|handout:1>Given the interpolated policy functions $\{\textbf{pf}(m)\}_{m=1}^M$, and integration nodes and weights provided by the Rouwenhorst method, approximate the expectation operators for the model.
 %For GHLS, determine whether the model is at the ZLB at each node, and construct the policy function grids according to .
-\item <7-|handout:1>Back out the policy functions $\textbf{pf}_t(d)$ from the expectation operators and time $t+1$ variables. %For GHLS, solve for regime-indexed polynomials based on 
+\item[d.] <7-|handout:1>Back out the policy functions $\textbf{pf}_t(d)$ from the expectation operators and time $t+1$ variables. %For GHLS, solve for regime-indexed polynomials based on 
 \end{enumerate}
 \item <8-|handout:1>Repeat step 2 until the maximum distance between successive approximations of the policy functions is below $10^{-6}$. 
-\end{itemize}
+\end{enumerate}
 \end{frame}
